---
title: "Cox Interaction Models for a Cross-Protocol V2 Ab Correlates Study"
output:
  html_document:
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
---


```{r, include = F, warning = F, message = F}

library(tidyverse)
library(data.table)
library(survey)
library(kyotil)
library(vaccine)
library(WeightedROC)


knitr::opts_chunk$set(echo = FALSE, warning = F, message = F)


analysis_data_files <- c(
  # HVTN702 = "controlledVEdata702.csv",
  HVTN705 = "/trials/vaccine/p705/analysis/lab/cc/copcor/HVTN705_secondcasecontrolprocesseddata_v14.csv",
  # HVTN505 = "controlledVEdata505_lab.csv",
  RV144 = "/trials/vaccine/thai_trial_rv144/adhoc/Moodie_Correlates_May2024/adata/controlledVEdataRV144_v2.csv"
)

# df_hvtn702 <- read.csv(analysis_data_files[["HVTN702"]])
df_hvtn705 <- read.csv(analysis_data_files[["HVTN705"]])
# df_hvtn505 <- read.csv(analysis_data_files[["HVTN505"]])
df_rv144 <- read.csv(analysis_data_files[["RV144"]])

# data processing 
df_hvtn705 <- df_hvtn705 %>% 
  mutate(RSA = factor(RSA), 
         Delta.D210.is.169K = ifelse(hxb169.is.k == 1 & Delta.D210 == 1, 1, 0),
         Delta.D210.not.169K = ifelse(hxb169.is.not.k == 1 & Delta.D210 == 1, 1, 0)) %>% 
  filter(!is.na(Ttilde.D210)) %>% 
  
  # change 11/19 
  mutate(
    Day210IgGgp70.B.CaseA.V1.V250delta = Day210IgGgp70.B.CaseA.V1.V250delta -log10(2),
    Day210IgGAE.A244.V1V2.Tags_293F50delta = Day210IgGAE.A244.V1V2.Tags_293F50delta -log10(2),
    Day210IgGC.1086C.V1.V2.Tags50delta = Day210IgGC.1086C.V1.V2.Tags50delta -log10(2),
    Day210IgGgp70_Ce1086.B2.V1V250delta = Day210IgGgp70_Ce1086.B2.V1V250delta -log10(2))


# df_hvtn702 <- df_hvtn702 %>% 
#   mutate(AGELE25 = factor(AGELE25))

df_rv144 <- df_rv144 %>% 
  mutate(trt = ifelse(trt == "VACCINE", 1, 0), 
         HIVm42.is.169K = ifelse(hxb169.is.k == 1 & HIVm42 == 1, 1, 0), 
         HIVm42.not.169K = ifelse(hxb169.is.not.k == 1 & HIVm42 == 1, 1, 0), 
         HIVwk26.is.169K = ifelse(hxb169.is.k == 1 & HIVwk26 == 1, 1, 0), 
         HIVwk26.not.169K = ifelse(hxb169.is.not.k == 1 & HIVwk26 == 1, 1, 0)
         )
df_rv144$age_ge_26 = ifelse(df_rv144$agecat == "Age >=26", ">=26", "<26")

# process HVTN 705 dataframe to look like RV 144 dataframe
df_hvtn705_new <- df_hvtn705 %>%
  filter(!is.na(Ttilde.D210)) %>% 
  rename(pub_id = Subjectid, 
         trt = Trt,
         HIVwk26fu = Ttilde.D210, 
         HIVwk26 = Delta.D210,
         HIVwk26.is.169K = Delta.D210.is.169K, 
         HIVwk26.not.169K = Delta.D210.not.169K,
         sample_weight = wt.D210,
         IgG_gp70_B.CaseA_V1V2 = Day210IgGgp70.B.CaseA.V1.V250delta, 
         IgG_AE.A244_V1V2_Tags_293F = Day210IgGAE.A244.V1V2.Tags_293F50delta,
         IgG_C.1086C_V1V2_Tags = Day210IgGC.1086C.V1.V2.Tags50delta,
         IgG_gp70_C.1086C_V1V2_293F = Day210IgGgp70_Ce1086.B2.V1V250delta,
         IgG3_gp70_B.CaseA_V1V2 = Day210IgG3gp70.B.CaseA.V1.V240delta,
         IgG3_AE.A244_V1V2_Tags_293F = Day210IgG3AE.A244.V1V2.Tags_293F40delta,
         IgG3_C.1086C_V1V2_Tags = Day210IgG3C.1086C.V1.V2.Tags40delta, 
         IgG3_gp70_C.1086C_V1V2_293F = Day210IgG3gp70.Ce1086.B2.V1V240delta) %>% 
  mutate(study_region = ifelse(RSA == "1", "HVTN705_SA", "HVTN705_Not_SA"),
         age_ge_26 = ifelse(Age >= 26, ">=26", "<26")) %>% 
  select(pub_id, trt, study_region, age_ge_26, HIVwk26fu, HIVwk26, HIVwk26.is.169K, 
         HIVwk26.not.169K, 
         sample_weight, IgG_gp70_B.CaseA_V1V2,
         IgG_AE.A244_V1V2_Tags_293F, IgG_C.1086C_V1V2_Tags, IgG_gp70_C.1086C_V1V2_293F, 
         IgG3_gp70_B.CaseA_V1V2, IgG3_AE.A244_V1V2_Tags_293F, IgG3_C.1086C_V1V2_Tags,
         IgG3_gp70_C.1086C_V1V2_293F)

df_combined <- df_rv144 %>% 
  mutate(study_region = "RV144", 
         age_ge_26 = ifelse(agecat == "Age >=26", ">=26", "<26")) %>% 
  select(pub_id, trt, study_region, age_ge_26, HIVwk26fu, HIVwk26, HIVwk26.is.169K, 
         HIVwk26.not.169K, sample_weight, IgG_gp70_B.CaseA_V1V2,
         IgG_AE.A244_V1V2_Tags_293F, IgG_C.1086C_V1V2_Tags, IgG_gp70_C.1086C_V1V2_293F, 
         IgG3_gp70_B.CaseA_V1V2, IgG3_AE.A244_V1V2_Tags_293F, IgG3_C.1086C_V1V2_Tags,
         IgG3_gp70_C.1086C_V1V2_293F) %>% 
  rbind(df_hvtn705_new)

```




# Combined HVTN 705 + RV144 analyses (24 months)

* **Adjustment covariates**: Region (RV144, South Africa, Outside South Africa), 
age above or below 26
* **Event time variable**: HIVwk26fu (RV144) and Ttilde.D210 (HVTN 705)
* **Event type variable**: HIVwk26 (RV144) and Delta.D210 (HVTN 705)
* **Weight variable**: sample_weight (RV144) and wt.D210 (HVTN 705)
* **Filter for HVTN 705**: !is.na(Ttilde.D210)



```{r, results = "asis", cache=T, fig.align='center'}
fit_svycoxph <- function(df, 
                                  covariates, 
                                  trt_var,
                                  time_var, 
                                  event_var, 
                                  marker_var,
                                  weight_var, 
                                  tf, 
                                  filter = NULL, 
                                  itxn = NULL, 
                                  ylim_cutoffs  = c(-1, 1, 0.2)){
  
  # filter for vaccine 
  df_vaccine <- df %>% 
    filter(!!sym(trt_var) == 1 & !is.na(!!sym(marker_var)))
  
  des <- svydesign(ids = ~1, weights = as.formula(paste0("~", weight_var)), data = df_vaccine)
  
  if (itxn==0) {
    # no interaction
    f <- as.formula(paste("Surv(", time_var, ",", event_var, ") ~", paste(c(marker_var%.%"+study_region", covariates), collapse = " + ")))
    
  } else if (itxn==1) {
    # interaction
    f <- as.formula(paste("Surv(", time_var, ",", event_var, ") ~", paste(c(marker_var%.%"*I(study_region=='RV144')", covariates), collapse = " + ")))
    
  } else if (itxn==2) {
    # rv144 only
    f <- as.formula(paste("Surv(", time_var, ",", event_var, ") ~", paste(c(marker_var, covariates), collapse = " + ")))
    
  } else if (itxn==3) {
    # 705 only
    f <- as.formula(paste("Surv(", time_var, ",", event_var, ") ~", paste(c(marker_var%.%"+study_region", covariates), collapse = " + ")))
    
  }
  
  fit <- svycoxph(f, design = des)
  return(fit)

}

covariates <- c("age_ge_26") # , "study_region"
tf <- 459 
time_var <- "HIVwk26fu"
event_var <- "HIVwk26"
trt_var <- "trt"
named_markers <- c(
  "IgG_gp70_B.CaseA_V1V2" = "IgG V1V2 B.CaseA-gp70",
  "IgG_AE.A244_V1V2_Tags_293F" = "IgG V1V2 AE.A244-Tags",
  "IgG_C.1086C_V1V2_Tags" = "IgG V1V2 C.1086-Tags",
  "IgG_gp70_C.1086C_V1V2_293F" = "IgG V1V2 C.1086-gp70",
  "IgG3_gp70_B.CaseA_V1V2" = "IgG3 V1V2 B.CaseA-gp70",
  "IgG3_AE.A244_V1V2_Tags_293F" = "IgG3 V1V2 AE.A244-Tags",
  "IgG3_C.1086C_V1V2_Tags" = "IgG3 V1V2 C.1086-Tags",
  "IgG3_gp70_C.1086C_V1V2_293F" = "IgG3 V1V2 C.1086-gp70"
)

weight_var <- "sample_weight"


# RV144
cat("RV144\n")
fits=list()
for (marker_var in names(named_markers)){
  readable_name <- named_markers[[marker_var]]
  # cat(sprintf("\n\n### %s {.tabset .tabset-fade} \n", readable_name))
  
  fits[[marker_var]]=fit_svycoxph(subset(df_combined, study_region=='RV144'), 
                        covariates = covariates, 
                        trt_var = trt_var, 
                        time_var = time_var,
                        event_var = event_var,
                        marker_var = marker_var, 
                        weight_var = weight_var, 
                        tf = tf, 
                        itxn = 2)
}
tab=getFormattedSummary(fits, robust=T)
knitr::kable(tab)


# 705
cat("705\n")
fits=list()
for (marker_var in names(named_markers)){
  readable_name <- named_markers[[marker_var]]
  # cat(sprintf("\n\n### %s {.tabset .tabset-fade} \n", readable_name))
  
  fits[[marker_var]]=fit_svycoxph(subset(df_combined, study_region!='RV144'), 
                        covariates = covariates, 
                        trt_var = trt_var, 
                        time_var = time_var,
                        event_var = event_var,
                        marker_var = marker_var, 
                        weight_var = weight_var, 
                        tf = tf, 
                        itxn = 3)
}
tab=getFormattedSummary(fits, robust=T)
knitr::kable(tab)


# no interaction
cat("Pooled, no interaction\n")
fits=list()
for (marker_var in names(named_markers)){
  readable_name <- named_markers[[marker_var]]
  # cat(sprintf("\n\n### %s {.tabset .tabset-fade} \n", readable_name))
  
  fits[[marker_var]]=fit_svycoxph(df_combined, 
                        covariates = covariates, 
                        trt_var = trt_var, 
                        time_var = time_var,
                        event_var = event_var,
                        marker_var = marker_var, 
                        weight_var = weight_var, 
                        tf = tf, 
                        itxn = 0)
}
tab=getFormattedSummary(fits, robust=T)
knitr::kable(tab)


# interaction
cat("Pooled, interaction\n")
fits=list()
for (marker_var in names(named_markers)){
  readable_name <- named_markers[[marker_var]]
  # cat(sprintf("\n\n### %s {.tabset .tabset-fade} \n", readable_name))
  
  fits[[marker_var]]=fit_svycoxph(df_combined, 
                        covariates = covariates, 
                        trt_var = trt_var, 
                        time_var = time_var,
                        event_var = event_var,
                        marker_var = marker_var, 
                        weight_var = weight_var, 
                        tf = tf, 
                        itxn = 1)
}
tab=getFormattedSummary(fits, robust=T)
knitr::kable(tab)
```


# RV144 Sieve (24 months) 


```{r, results = "asis", cache=T, fig.align='center'}

# med_vaccine <- function(df, 
#                                   covariates, 
#                                   trt_var,
#                                   time_var, 
#                                   event_var, 
#                                   marker_var,
#                                   weight_var, 
#                                   tf, 
#                                   filter = NULL, 
#                                   itxn = NULL, 
#                                   ylim_cutoffs  = c(-1, 1, 0.2)){
#   
# 
#   df$ph2 = !is.na(df$IgG3_AE.A244_V1V2_Tags_293F)
#   
#   dat <- load_data(
#     time       = time_var,
#     event      = event_var,
#     vacc       = trt_var,
#     marker     = marker_var,
#     covariates = covariates,
#     weights    = weight_var,
#     ph2        = "ph2",
#     data       = df
#   )
#   
#   fit  = est_med(dat = dat, type = "Cox", t_0 = tf, params_cox = params_med_cox(edge_ind = TRUE))
#   print(fit)
# 
#   fit2 = est_med(dat = dat, type = "Cox", t_0 = tf)
#   print(fit2)
# 
#   fit1 = est_med(dat = dat, type = "NP", t_0 = tf)
#   print(fit1)
#   
# }



get_C_index <- function(df, 
                                  covariates, 
                                  trt_var,
                                  time_var, 
                                  event_var, 
                                  marker_var,
                                  weight_var, 
                                  tf, 
                                  filter = NULL, 
                                  itxn = NULL, 
                                  ylim_cutoffs  = c(-1, 1, 0.2)){
  
  # filter for vaccine and ph2
  df_vaccine <- df %>% 
    filter(!!sym(trt_var) == 1 & !is.na(!!sym(marker_var)))
  
  des <- svydesign(ids = ~1, weights = as.formula(paste0("~", weight_var)), data = df_vaccine)
  
  f1 <- as.formula("Surv(HIVwk26fu, HIVwk26)         ~ "%.%marker_var%.%" + age_ge_26")
  f2 <- as.formula("Surv(HIVwk26fu, HIVwk26.is.169K) ~ "%.%marker_var%.%" + age_ge_26")
  
  fit1 <- svycoxph(f1, design = des)
  fit2 <- svycoxph(f2, design = des)
  
  c(
    HIVwk26=paste0(formatDouble(summary(fit1)$concordance["C"],3), " (", formatDouble(summary(fit1)$concordance['se(C)'],3), ")"),
    HIVwk26.is.169K=paste0(formatDouble(summary(fit2)$concordance["C"],3), " (", formatDouble(summary(fit1)$concordance['se(C)'],3), ")"))

}


get_AUC <- function(df, 
                                  covariates, 
                                  trt_var,
                                  time_var, 
                                  event_var, 
                                  marker_var,
                                  weight_var, 
                                  tf, 
                                  filter = NULL, 
                                  itxn = NULL, 
                                  ylim_cutoffs  = c(-1, 1, 0.2)){
  
  # filter for vaccine and ph2
  df_vaccine <- df %>% 
    filter(!!sym(trt_var) == 1 & !is.na(!!sym(marker_var)))
  
  des <- svydesign(ids = ~1, weights = as.formula(paste0("~", weight_var)), data = df_vaccine)
  
  f1 <- as.formula("HIVwk26         ~ "%.%marker_var%.%" + age_ge_26")
  f2 <- as.formula("HIVwk26.is.169K ~ "%.%marker_var%.%" + age_ge_26")
  
  fit1 <- svyglm(f1,
              design = des,
              family = quasibinomial())
  p1 <- predict(fit1, type = "link")
  roc1 <- WeightedROC(p1, df_vaccine$HIVwk26, df_vaccine[[weight_var]])
  
  fit2 <- svyglm(f2,
              design = des,
              family = quasibinomial())
  p2 <- predict(fit2, type = "link")
  roc2 <- WeightedROC(p2, df_vaccine$HIVwk26.is.169K[!is.na(df_vaccine$HIVwk26.is.169K)], df_vaccine[[weight_var]][!is.na(df_vaccine$HIVwk26.is.169K)])

  c(
    HIVwk26=        paste0(formatDouble(WeightedAUC(roc1),3)),
    HIVwk26.is.169K=paste0(formatDouble(WeightedAUC(roc2),3)))

}


covariates <- c("age_ge_26") # , "study_region"
time_var <- "HIVwk26fu"
tf <- 459 
event_var <- "HIVwk26"
trt_var <- "trt"
named_markers <- c(
  "IgG_gp70_B.CaseA_V1V2" = "IgG V1V2 B.CaseA-gp70",
  "IgG_AE.A244_V1V2_Tags_293F" = "IgG V1V2 AE.A244-Tags",
  "IgG_C.1086C_V1V2_Tags" = "IgG V1V2 C.1086-Tags",
  "IgG_gp70_C.1086C_V1V2_293F" = "IgG V1V2 C.1086-gp70",
  "IgG3_gp70_B.CaseA_V1V2" = "IgG3 V1V2 B.CaseA-gp70",
  "IgG3_AE.A244_V1V2_Tags_293F" = "IgG3 V1V2 AE.A244-Tags",
  "IgG3_C.1086C_V1V2_Tags" = "IgG3 V1V2 C.1086-Tags",
  "IgG3_gp70_C.1086C_V1V2_293F" = "IgG3 V1V2 C.1086-gp70"
)

weight_var <- "sample_weight"


cat("svycoxph fits C-index\n")

tab=sapply (names(named_markers), function(marker_var){
  
  fits[[marker_var]]=get_C_index(subset(df_combined, study_region=='RV144'), 
                        covariates = covariates, 
                        trt_var = trt_var, 
                        time_var = time_var,
                        event_var = event_var,
                        marker_var = marker_var, 
                        weight_var = weight_var, 
                        tf = tf)
})
knitr::kable(tab)


cat("svyglm fits AUC\n")

tab=sapply (names(named_markers), function(marker_var){
  
  fits[[marker_var]]=get_AUC(subset(df_combined, study_region=='RV144'), 
                        covariates = covariates, 
                        trt_var = trt_var, 
                        time_var = time_var,
                        event_var = event_var,
                        marker_var = marker_var, 
                        weight_var = weight_var, 
                        tf = tf)
})
knitr::kable(tab)


```


# RV144 Sieve (42 months) 

```{r, results = "asis", cache=T, fig.align='center'}

get_C_index <- function(df, 
                                  covariates, 
                                  trt_var,
                                  time_var, 
                                  event_var, 
                                  marker_var,
                                  weight_var, 
                                  tf, 
                                  filter = NULL, 
                                  itxn = NULL, 
                                  ylim_cutoffs  = c(-1, 1, 0.2)){
  
  # filter for vaccine and ph2
  df_vaccine <- df %>% 
    filter(!!sym(trt_var) == 1 & !is.na(!!sym(marker_var)))
  
  des <- svydesign(ids = ~1, weights = as.formula(paste0("~", weight_var)), data = df_vaccine)
  
  f1 <- as.formula("Surv(HIVm42fu, HIVm42)         ~ "%.%marker_var%.%" + age_ge_26")
  f2 <- as.formula("Surv(HIVm42fu, HIVm42.is.169K) ~ "%.%marker_var%.%" + age_ge_26")
  
  fit1 <- svycoxph(f1, design = des)
  fit2 <- svycoxph(f2, design = des)
  
  c(
    HIVm42=paste0(formatDouble(summary(fit1)$concordance["C"],3), " (", formatDouble(summary(fit1)$concordance["C"]-1.96*summary(fit1)$concordance['se(C)'],3), ", ", formatDouble(summary(fit1)$concordance["C"]+1.96*summary(fit1)$concordance['se(C)'],3), ")"),
    HIVm42.is.169K=paste0(formatDouble(summary(fit2)$concordance["C"],3), " (", formatDouble(summary(fit2)$concordance["C"]-1.96*summary(fit2)$concordance['se(C)'],3), ", ", formatDouble(summary(fit2)$concordance["C"]+1.96*summary(fit2)$concordance['se(C)'],3), ")"))

}


get_AUC <- function(df, 
                                  covariates, 
                                  trt_var,
                                  time_var, 
                                  event_var, 
                                  marker_var,
                                  weight_var, 
                                  tf, 
                                  filter = NULL, 
                                  itxn = NULL, 
                                  ylim_cutoffs  = c(-1, 1, 0.2)){
  
  # filter for vaccine and ph2
  df_vaccine <- df %>% 
    filter(!!sym(trt_var) == 1 & !is.na(!!sym(marker_var)))
  
  des <- svydesign(ids = ~1, weights = as.formula(paste0("~", weight_var)), data = df_vaccine)
  
  f1 <- as.formula("HIVm42         ~ "%.%marker_var%.%" + age_ge_26")
  f2 <- as.formula("HIVm42.is.169K ~ "%.%marker_var%.%" + age_ge_26")
  
  fit1 <- svyglm(f1,
              design = des,
              family = quasibinomial())
  p1 <- predict(fit1, type = "link")
  roc1 <- WeightedROC(p1, df_vaccine$HIVm42, df_vaccine[[weight_var]])
  
  fit2 <- svyglm(f2,
              design = des,
              family = quasibinomial())
  p2 <- predict(fit2, type = "link")
  roc2 <- WeightedROC(p2, df_vaccine$HIVm42.is.169K[!is.na(df_vaccine$HIVm42.is.169K)], df_vaccine[[weight_var]][!is.na(df_vaccine$HIVm42.is.169K)])

  c(
    HIVm42=        paste0(formatDouble(WeightedAUC(roc1),3)),
    HIVm42.is.169K=paste0(formatDouble(WeightedAUC(roc2),3)))

}


covariates <- c("age_ge_26") # , "study_region"
time_var <- "HIVm42fu"
tf <- 459 
event_var <- "HIVm42"
trt_var <- "trt"
named_markers <- c(
  "IgG_gp70_B.CaseA_V1V2" = "IgG V1V2 B.CaseA-gp70",
  "IgG_AE.A244_V1V2_Tags_293F" = "IgG V1V2 AE.A244-Tags",
  "IgG_C.1086C_V1V2_Tags" = "IgG V1V2 C.1086-Tags",
  "IgG_gp70_C.1086C_V1V2_293F" = "IgG V1V2 C.1086-gp70",
  "IgG3_gp70_B.CaseA_V1V2" = "IgG3 V1V2 B.CaseA-gp70",
  "IgG3_AE.A244_V1V2_Tags_293F" = "IgG3 V1V2 AE.A244-Tags",
  "IgG3_C.1086C_V1V2_Tags" = "IgG3 V1V2 C.1086-Tags",
  "IgG3_gp70_C.1086C_V1V2_293F" = "IgG3 V1V2 C.1086-gp70"
)

weight_var <- "sample_weight"

cat("svycoxph fits C-index\n")
tab=sapply (names(named_markers), function(marker_var){
  
  get_C_index(df_rv144, 
                        covariates = covariates, 
                        trt_var = trt_var, 
                        time_var = time_var,
                        event_var = event_var,
                        marker_var = marker_var, 
                        weight_var = weight_var, 
                        tf = tf)
})
knitr::kable(tab)

cat("svyglm fits AUC\n")
tab=sapply (names(named_markers), function(marker_var){
  
  get_AUC(df_rv144, 
                        covariates = covariates, 
                        trt_var = trt_var, 
                        time_var = time_var,
                        event_var = event_var,
                        marker_var = marker_var, 
                        weight_var = weight_var, 
                        tf = tf)
})
knitr::kable(tab)


```

# RV144 Ab + T cell (24 and 42 months) 

V1V2 markres are in the same order as in previous sections.


```{r}
rv144_tcell = read.csv("/trials/vaccine/thai_trial_rv144/case_control_analysis/pdata/mcelrath_ics_92TH023EnvCD4.csv")
# mcelrath_ics_imputed.csv

rv144_tcell = subset(rv144_tcell, outcome=="92TH023Env.CD4+.Average_polyfunctionality")

# rv144_tcell$ptid matches id_map$pin
id_map = read.csv("/trials/vaccine/thai_trial_rv144/adhoc/Moodie_Correlates_May2024/adata/rv144_pubids_v2.csv")
rv144_tcell$pub_id = id_map$pub_id_v2[match(rv144_tcell$ptid, id_map$pin)]

df_rv144$CD4.Average_polyfunctionality.92TH023Env = rv144_tcell$y[match(df_rv144$pub_id, rv144_tcell$pub_id)]


```

```{r}


get_ab_tcell <- function(df, 
                                  covariates, 
                                  trt_var,
                                  time_var, 
                                  event_var, 
                                  marker_var,
                                  weight_var, 
                                  filter = NULL, 
                                  itxn = NULL, 
                                  ylim_cutoffs  = c(-1, 1, 0.2)){
  
  # filter for vaccine and ph2
  df_vaccine <- df %>% 
    filter(!!sym(trt_var) == 1 & !is.na(!!sym(marker_var)))
  
  des <- svydesign(ids = ~1, weights = as.formula(paste0("~", weight_var)), data = df_vaccine)
  
  f1 <- as.formula("Surv("%.%time_var%.%", "%.%event_var%.%")         ~ I(scale(CD4.Average_polyfunctionality.92TH023Env))+"%.%marker_var%.%" + age_ge_26")

  svycoxph(f1, design = des)

}

get_tcell <- function(df, 
                                  covariates, 
                                  trt_var,
                                  time_var, 
                                  event_var, 
                                  marker_var,
                                  weight_var, 
                                  filter = NULL, 
                                  itxn = NULL, 
                                  ylim_cutoffs  = c(-1, 1, 0.2)){
  
  # filter for vaccine and ph2
  df_vaccine <- df %>% 
    filter(!!sym(trt_var) == 1 & !is.na(!!sym(marker_var)))
  
  des <- svydesign(ids = ~1, weights = as.formula(paste0("~", weight_var)), data = df_vaccine)
  
  f1 <- as.formula("Surv("%.%time_var%.%", "%.%event_var%.%") ~ I(scale(CD4.Average_polyfunctionality.92TH023Env)) + age_ge_26")

  svycoxph(f1, design = des)

}


covariates <- c("age_ge_26") # , "study_region"
trt_var <- "trt"
weight_var <- "sample_weight"

named_markers <- c(
  "IgG_gp70_B.CaseA_V1V2" = "IgG V1V2 B.CaseA-gp70",
  "IgG_AE.A244_V1V2_Tags_293F" = "IgG V1V2 AE.A244-Tags",
  "IgG_C.1086C_V1V2_Tags" = "IgG V1V2 C.1086-Tags",
  "IgG_gp70_C.1086C_V1V2_293F" = "IgG V1V2 C.1086-gp70",
  "IgG3_gp70_B.CaseA_V1V2" = "IgG3 V1V2 B.CaseA-gp70",
  "IgG3_AE.A244_V1V2_Tags_293F" = "IgG3 V1V2 AE.A244-Tags",
  "IgG3_C.1086C_V1V2_Tags" = "IgG3 V1V2 C.1086-Tags",
  "IgG3_gp70_C.1086C_V1V2_293F" = "IgG3 V1V2 C.1086-gp70"
)


cat("24 months\n")
time_var <- "HIVwk26fu"
event_var <- "HIVwk26"
fits=lapply (names(named_markers), function(marker_var){
  get_ab_tcell(df_rv144, 
                        covariates = covariates, 
                        trt_var = trt_var, 
                        time_var = time_var,
                        event_var = event_var,
                        marker_var = marker_var, 
                        weight_var = weight_var)
})

tab=getFormattedSummary(fits, robust=T)
rownames(tab)[2]="V1V2"
knitr::kable(tab)


cat("42 months\n")
time_var  <- "HIVm42fu"
event_var <- "HIVm42"
fits=lapply (names(named_markers), function(marker_var){
  get_ab_tcell(df_rv144, 
                        covariates = covariates, 
                        trt_var = trt_var, 
                        time_var = time_var,
                        event_var = event_var,
                        marker_var = marker_var, 
                        weight_var = weight_var)
})


cat("24 months t cell only\n")
time_var <- "HIVwk26fu"
event_var <- "HIVwk26"
fits=lapply (names(named_markers)[1], function(marker_var){
  get_tcell(df_rv144, 
                        covariates = covariates, 
                        trt_var = trt_var, 
                        time_var = time_var,
                        event_var = event_var,
                        marker_var = marker_var, 
                        weight_var = weight_var)
})

tab=getFormattedSummary(fits, robust=T)
tab

cat("42 months t cell only\n")
time_var  <- "HIVm42fu"
event_var <- "HIVm42"
fits=lapply (names(named_markers)[1], function(marker_var){
  get_tcell(df_rv144, 
                        covariates = covariates, 
                        trt_var = trt_var, 
                        time_var = time_var,
                        event_var = event_var,
                        marker_var = marker_var, 
                        weight_var = weight_var)
})

tab=getFormattedSummary(fits, robust=T)
tab

```
