---
title: "Age Risk Correlate"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(survey)
library(kyotil)
library(readxl)

dat_prevent19_stage1=read.csv('/trials/covpn/p3004/analysis/correlates/Part_A_Blinded_Phase_Data/adata/prevent19_data_processed_20240320.csv')
dat_azd1222_stage1=read.csv('/trials/covpn/p3002/analysis/correlates/Part_A_Blinded_Phase_Data/adata/azd1222_data_processed_with_riskscore.csv')
dat_unk302 = read.csv('/trials/covpn/p3004/analysis/correlates/UK302/adata/nvx_uk302_data_processed_20240320.csv')

```

Age is a potential confounder because immune markers are lower in older people and age is also associated with risk of mild-moderate-severe COVID and severe COVID in complicated ways. 


## Mild-moderate-severe ancestral COVID risk

### NVX PREVENT19 stage 1, placebo arm
Age (continuous) is a better predictor than age group, log likelihood ratio 1.5.
```{r}
coxph(Surv(EventTimePrimaryD35,EventIndPrimaryD35)~Age, subset(dat_prevent19_stage1, ph1.D35==1 & Trt==0 & Bserostatus==0 & Country==0))
coxph(Surv(EventTimePrimaryD35,EventIndPrimaryD35)~Senior, subset(dat_prevent19_stage1, ph1.D35==1 & Trt==0 & Bserostatus==0 & Country==0))
```

### NVX UK302, placebo arm
Age group is a better predictor than age, log likelihood ratio 2.2.
```{r}
coxph(Surv(EventTimePrimaryD35,EventIndPrimaryD35)~Age+Region, subset(dat_unk302, ph1.D35==1 & Trt==0 & Bserostatus==0))
coxph(Surv(EventTimePrimaryD35,EventIndPrimaryD35)~Senior+Region, subset(dat_unk302, ph1.D35==1 & Trt==0 & Bserostatus==0))
```



### AZ stage 1, placebo arm
Age group is a better predictor than age, log likelihood ratio 3-4 depending on whether risk score is adjusted.
```{r}
coxph(Surv(EventTimePrimaryD57,EventIndPrimaryD57)~Age+Country, subset(dat_azd1222_stage1, ph1.D57==1 & Trt==0 & Bserostatus==0))
coxph(Surv(EventTimePrimaryD57,EventIndPrimaryD57)~Senior+Country, subset(dat_azd1222_stage1, ph1.D57==1 & Trt==0 & Bserostatus==0))
coxph(Surv(EventTimePrimaryD57,EventIndPrimaryD57)~Age+Country+risk_score, subset(dat_azd1222_stage1, ph1.D57==1 & Trt==0 & Bserostatus==0))
coxph(Surv(EventTimePrimaryD57,EventIndPrimaryD57)~Senior+Country+risk_score, subset(dat_azd1222_stage1, ph1.D57==1 & Trt==0 & Bserostatus==0))
```
