---
title: "Imputation Check"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```



```{r, echo=FALSE, include=FALSE}
{
library(survey)
library(kyotil)

dat_mapped=read.csv('/trials/covpn/p3003/analysis/mapping_immune_correlates/adata/COVID_ENSEMBLE_PartAComplete_variant_mapped_20240123.csv')
dat_proc = read.csv('/trials/covpn/p3003/analysis/correlates/Part_A_Blinded_Phase_Data/adata/janssen_partA_VL_data_processed_20240126.csv')
assay_metadata=read.csv('~/correlates_reporting2/assay_metadata/janssen_partA_VL_assay_metadata.csv')
assays=assay_metadata$assay

country.codes=c("USA", "ARG", "BRA", "CHL", "COL", "MEX", "PER", "ZAF")
dat_mapped$cc=country.codes[dat_mapped$Country+1]
dat_proc$cc=country.codes[dat_proc$Country+1]

dat_pooled_partA = read.csv('/trials/covpn/p3003/analysis/correlates/Part_A_Blinded_Phase_Data/adata/janssen_pooled_partA_data_processed_with_riskscore.csv')

stopifnot(all(dat_pooled_partA$Ptid==dat_mapped$Ptid))
stopifnot(all(dat_proc$Ptid==dat_mapped$Ptid))

# forVariants is F if ancestral ID50 is measured before variants study, T if for variants study
dat_mapped$forVariants = ifelse(!is.na(dat_pooled_partA$Day29pseudoneutid50),F,T)

# an indicator for non-cases in the whole cohort
kp = with(dat_mapped, EventIndPrimaryIncludeNotMolecConfirmedD1 == 0)

# an indicator for cases in the whole cohort
cases= with(dat_mapped, EventIndPrimaryIncludeNotMolecConfirmedD1 == 1)
dat_proc$cases= with(dat_proc, EventIndPrimaryIncludeNotMolecConfirmedD1 == 1)
dat_mapped$ph2.D29 = dat_proc$ph2.D29
dat_mapped$cases = dat_proc$cases

# an alias for subcohort
subc = dat_mapped$SubcohortInd==1

dat_mapped$COL_variants_study = with(dat_mapped, cc=="COL" & EventIndPrimaryIncludeNotMolecConfirmedD1==0 & SubcohortInd!=1 & !is.na(Day29bindSpike_D614))
dat_mapped$SubcohortIndPlus = ifelse(dat_mapped$SubcohortInd | dat_mapped$COL_variants_study, 1, 0)
table(dat_mapped$SubcohortIndPlus, dat_mapped$SubcohortInd)
}


```




```{r, echo=FALSE}

for (r in 0:2) {
  cat("\n\n", switch(r+1, "US", "LatAm", "RSA"),"\n\n")

  for(j in 1:2) {
    if (j==1) {
      # bAb, 4 is not included because bindSpike_D614 is removed from dat_proc
      aa = c(assays[1], assays[5:13]) 
    } else if (j==2) {
      # nAb
      aa = assays[14:20] 
    }
    cat("\n", switch(j, "bAb", "nAb"), "\n")
    print(aa)

    cat("\nbefore imputation")
    # for hard imputed markers
    dat=subset(dat_mapped, Trt == 1 & Bserostatus==0 & Region==r & ph2.D29==1) # use ph2.D29==1 to focus on the ph2 b/c there are ptids outside subcohort who have anc bAb but not anc nAb
    aaa = c(aa[1], aa[-1])
    dat$tmp=NULL
    for (i in 1:length(aaa)) { 
      dat$tmp = paste0(dat$tmp, ifelse(is.na(dat[["Day29"%.%aaa[i]]]), 0, 1))
    }
    print(table(dat$tmp, dat$EventIndPrimaryIncludeNotMolecConfirmedD1))

    cat("\nafter imputation")
    # for hard imputed markers
    dat=subset(dat_proc, Trt == 1 & Bserostatus==0 & Region==r & ph2.D29==1) # use ph2.D29==1 to focus on the ph2 b/c there are ptids outside subcohort who have anc bAb but not anc nAb
    aaa = c(aa[1], aa[-1])
    dat$tmp=NULL
    for (i in 1:length(aaa)) { 
      dat$tmp = paste0(dat$tmp, ifelse(is.na(dat[["Day29"%.%aaa[i]]]), 0, 1))
    }
    print(table(dat$tmp, dat$EventIndPrimaryIncludeNotMolecConfirmedD1))

    cat("\nafter imputation, showing multiply imputed markers")
    dat=subset(dat_proc, Trt == 1 & Bserostatus==0 & Region==r & ph2.D29==1) # use ph2.D29==1 to focus on the ph2 b/c there are ptids outside subcohort who have anc bAb but not anc nAb
    aaa = c(aa[1], aa[-1]%.%"_1")
    dat$tmp=NULL
    for (i in 1:length(aaa)) { 
      dat$tmp = paste0(dat$tmp, ifelse(is.na(dat[["Day29"%.%aaa[i]]]), 0, 1))
    }
    print(table(dat$tmp, dat$EventIndPrimaryIncludeNotMolecConfirmedD1))
  }

}

# subset(dat_proc, Region==2 & cases==FALSE & !is.na(Day29bindSpike) & !is.na(Day29bindSpike_P.1) & is.na(Day29bindSpike_P.1_1))[,c("SubcohortInd","EventIndPrimaryIncludeNotMolecConfirmedD1")]


```

In US, imputation has no impact. There are 27 in the 1110000 group in nAb before imputation, which gets merged into 1000000 group in the multiple imputed markers. This is because they are outside the subcohort and when doing multiple imputation, they are not carried as multiple imputation is restricted to ph2. 

In LatAm, after imputation, 98 non-cases (Colombians) have bindSpike imputed, and one non-case has variants bAb imputed.

In RSA, after imputation, six non-cases have variants bAb imputed. Also, the number of cases with variants bAb increases from 10 to 13. 

Note the multiply imputed version (imputation #1) which affects cases.