---
title: "VAT08 Stage 1 and 2 Data"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T)

library(survey)
library(kyotil)

country.codes=c("Colombia", "Ghana", "Honduras", "India", "Japan", "Kenya", "Nepal", "United States", "Mexico", "Uganda", "Ukraine")
region.1 = c( # stage 1
  "United States" = 1, "Japan" = 1, 
  "Colombia" = 2, "Honduras" = 2, 
  "Ghana" = 3, "Kenya" = 3, 
  "Nepal" = 4, "India" = 4)
region.2 = c( # stage 2
  "Colombia" = 1, "Mexico" = 1, 
  "Ghana" = 2, "Kenya" = 2, "Uganda" = 2,
  "Nepal" = 3, "India" = 3)


dat_mapped=read.csv('/trials/covpn/p3005/analysis/mapping_immune_correlates/combined/adata/COVID_Sanofi_stage1and2_mapped_20240117.csv')
# dat_proc = read.csv('/trials/covpn/p3005/analysis/correlates/Part_A_Blinded_Phase_Data/adata/vat08_combined_data_processed_20240111.csv')
dat_proc = read.csv('/trials/covpn/p3005/analysis/correlates/Part_A_Blinded_Phase_Data/adata/vat08_combined_data_processed_20240117.csv')

assay_metadata=read.csv('~/correlates_reporting2/assay_metadata/vat08_combined_assay_metadata.csv')
assays=assay_metadata$assay

dat_mapped$EventIndPrimaryD1 = dat_mapped$EventIndFirstInfectionD1
dat_mapped$EventTimePrimaryD1 = dat_mapped$EventTimeFirstInfectionD1
dat_mapped$EventIndPrimaryD43= dat_mapped$EventIndFirstInfectionD43
dat_mapped$EventTimePrimaryD43= dat_mapped$EventTimeFirstInfectionD43
dat_mapped$EarlyendpointD43 <- with(dat_mapped, EarlyinfectionD43==1 | (EventIndPrimaryD1==1 & EventTimePrimaryD1 < NumberdaysD1toD43 + 7),1,0)
dat_mapped$ph1.D43= with(dat_mapped, EarlyendpointD43==0 & Perprotocol==1 & EventTimePrimaryD43 >= 7)
dat_mapped$Senior=ifelse(dat_mapped$Age>=60,1,0)
dat_mapped$cc = country.codes[dat_mapped$Country]
# first set it to stage 1 region, then change the region for stage 2 countries
dat_mapped$region = region.1[dat_mapped$cc] 
dat_mapped$region = ifelse(dat_mapped$Trialstage==2, region.2[dat_mapped$cc], dat_mapped$region)


dat_mapped$SUBJID = sub("VAT00008-","",dat_mapped$Subjectid)
dat_mapped$SUBJID = gsub("-","",dat_mapped$SUBJID,)

dat_proc$SUBJID = sub("VAT00008-","",dat_proc$Ptid)
dat_proc$SUBJID = gsub("-","",dat_proc$SUBJID,)

```

### nAb immunogenicity and imputation
Note that the marker level in the NN, placebo is higher in Stage 2 than in Stage 1, probably reflecting different countries.
```{r}
myboxplot(Day43bindSpike~Trt+Bserostatus+Trialstage, dat_mapped, ylab="D43 bAb Spike",
  names=rep(c("N,pla", "N,vac", "NN,pla", "NN,vac"),2),
  main="Stage 1                                        Stage 2",
  cex.axis=0.8)
abline(v=4.5)
```

There are five different ID50s and one score.
```{r}
assays=assays[startsWith(assays,"pseudoneutid50")]
print(assays)
```

Correlation is high between variant markers in Stage 2 non-naive, vaccine arm at both baseline
```{r}
mypairs(subset(dat_proc, Trialstage==2 & Bserostatus==1 & Trt==1 & ph1.D43)[,"B"%.%assays[1:5]])
```

and D43 

```{r}
mypairs(subset(dat_proc, Trialstage==2 & Bserostatus==1 & Trt==1 & ph1.D43)[,"Day43"%.%assays[1:5]])
```
 
Correlation is medium between variant markers at D43 in Stage 2 naive, vaccine arm. (The correlation between the ancestral marker and the other markers range between 0.63 and 0.67.)
```{r}
mypairs(subset(dat_proc, Trialstage==2 & Bserostatus==0 & Trt==1 & ph1.D43)[,"Day43"%.%assays[1:5]])
```

Correlation is low between baseline and D22 or D43 in Stage 2 non-naive, vaccine arm.
```{r}
mypairs(subset(dat_proc, Trialstage==2 & Bserostatus==1 & Trt==1 & ph1.D43)[,c("B","Day22","Day43")%.%assays[1]])
```


A closer look at the relationship between baseline and Day 43 markers in the baseline positive. Note that the D43 markers appear saturated since level seems flat across different baseline marker levels.
```{r}
par(mfrow=c(2,4))
  # ancestral marker
  corplot(Day43pseudoneutid50~Bpseudoneutid50, subset(dat_proc, Trialstage==2 & Bserostatus==1 & Trt==1 & ph1.D43), ylim=c(0,4))
  myboxplot(Day43pseudoneutid50~I(Bpseudoneutid50>0.2), subset(dat_proc, Trialstage==2 & Bserostatus==1 & Trt==1 & ph1.D43), names=c("Undetectable at B","Detectable at B"), ylab="D43", ylim=c(0,4))
  my.interaction.plot(subset(dat_proc, Trialstage==2 & Bserostatus==1 & Trt==1 & ph1.D43 & !is.na(Bpseudoneutid50) & !is.na(Day43pseudoneutid50), c(Bpseudoneutid50, Day43pseudoneutid50)), 
                      x.ori = 0, xaxislabels = c("B", "D43"), cex.axis = 1, add = FALSE, xlab = "", ylab = "", pcol = NULL, lcol = NULL)  
  corplot(Delta43overBpseudoneutid50~Bpseudoneutid50, subset(dat_proc, Trialstage==2 & Bserostatus==1 & Trt==1 & ph1.D43))
  
  # BA.1
  corplot(Day43pseudoneutid50_BA.1~Bpseudoneutid50_BA.1, subset(dat_proc, Trialstage==2 & Bserostatus==1 & Trt==1 & ph1.D43), ylim=c(0,4))
  myboxplot(Day43pseudoneutid50_BA.1~I(Bpseudoneutid50_BA.1>0.2), subset(dat_proc, Trialstage==2 & Bserostatus==1 & Trt==1 & ph1.D43), names=c("Undetectable at B","Detectable at B"), ylab="D43", ylim=c(0,4))
  my.interaction.plot(subset(dat_proc, Trialstage==2 & Bserostatus==1 & Trt==1 & ph1.D43 & !is.na(Bpseudoneutid50_BA.1) & !is.na(Day43pseudoneutid50_BA.1), c(Bpseudoneutid50_BA.1, Day43pseudoneutid50_BA.1)), 
                      x.ori = 0, xaxislabels = c("B", "D43"), cex.axis = 1, add = FALSE, xlab = "", ylab = "", pcol = NULL, lcol = NULL)  
  corplot(Delta43overBpseudoneutid50_BA.1~Bpseudoneutid50_BA.1, subset(dat_proc, Trialstage==2 & Bserostatus==1 & Trt==1 & ph1.D43))
```
 

Overall, "because the correlation among variants is pretty good for the non-naives and really the analysis focuses on the non-naives" (Peter), we decide to **impute variants for those who have data for at least one variant to make the complexity of data processing more manageable**. 

Missingness across baseline, d22 and d43, for the ancestral markers in the vaccine arms. The results support the decision "**to keep it simple and require for RIS membership availability of data at all 3 time points**" (Peter).
```{r}
for(trt in 1:0) {
  myprint(trt)
  for (i in 2:1) {
    cat(paste0("stage ", i, '\n'))
    dat=subset(dat_proc, Trialstage==i & Trt==trt & ph1.D43)
    times=c("B","Day22","Day43")
    for (i in 1:3) {
      dat[['tmp'%.%i]]=ifelse(is.na(dat[[times[i]%.%'pseudoneutid50']]), 0, 1)
    }
    dat$tmp=with(dat,paste0(tmp1,tmp2,tmp3))
    print(table(dat$tmp))
    cat("\n")
  }
}
```

Missingness across variants. Some ptids only have the ancestral marker measured. The missingness pattern is explained by the fact that samples from different steps have different set of markers measured. We decide to impute all variants if one variant marker exists.

```{r}
# for (tp in c("B")) {
for (tp in c("B", "Day22", "Day43")) {
  # before imputation
  dat1=dat_mapped
  # after imputation
  # dat1=dat_proc
  
  for(trt in 1) {
    myprint(tp, trt)
    for (i in 2:1) {
      cat(paste0("stage ", i, '\n'))
      if (trt==2) {
        # pool over arms
        dat=subset(dat1, Trialstage==i & ph1.D43)
      } else {
        dat=subset(dat1, Trialstage==i & ph1.D43 & Trt==trt)
      }
      for (i in 1:5) {
        dat[['tmp'%.%i]]=ifelse(is.na(dat[[tp%.%assays[i]]]), 0, 1)
      }
      dat$tmp=with(dat,paste0(tmp1,tmp2,tmp3,tmp4,tmp5))
      print(table(dat$tmp))
      cat("\n")
      # print(table(dat$EventIndPrimaryD43, dat$tmp, dat$Bserostatus))
    }
  }

}
```




```{r}
# a more detailed look at missingness by batch
# for (tp in c("B")) {
# #for (tp in c("B", "Day22", "Day43")) {
#   # before imputation
#   dat1=dat_mapped
#   # after imputation
#   # dat1=dat_proc
#   
#   for(trt in 1) {
#     myprint(tp, trt)
#     for (i in 2:1) { # stage
#       cat(paste0("stage ", i, '\n'))
#       if (trt==2) {
#         # pool over arms
#         dat=subset(dat1, Trialstage==i & ph1.D43)
#       } else {
#         dat=subset(dat1, Trialstage==i & ph1.D43 & Trt==trt)
#       }
#       for (i in 1:5) {
#         dat[['tmp'%.%i]]=ifelse(is.na(dat[[tp%.%assays[i]]]), 0, 1)
#       }
#       dat$tmp=with(dat,paste0(tmp1,tmp2,tmp3,tmp4,tmp5))
#       print(mytable(dat$EventIndPrimaryD43, dat$tmp, dat$nAbBatch, dat$Bserostatus))
#     }
#   }
# 
# }
```


The number of D43 nAb ph2 samples by Bserostatus 0/1 (row) and Case 1/0 (column) and broken down by treatment arms (vaccine, placebo).
```{r}
dat1=dat_proc

f=function(tab2, tab1, tab0) {
  for (i in 1:2) {
    print(paste0(tab2[i,1], " (", tab1[i,1], ", ", tab0[i,1], ") ", tab2[i,2], " (", tab1[i,2], ", ", tab0[i,2], ")"))
  }
}

for (i in 2:1) {
  cat(paste0("stage ", i, '\n'))
  dat=subset(dat1, Trialstage==i & ph1.D43 & TwophasesampIndD43nAb)
  tab2 = table(dat$Bserostatus, dat$EventIndPrimaryD43)[,2:1] # [,2:1] moves cases before non-cases
  dat=subset(dat1, Trialstage==i & ph1.D43 & Trt==1 & TwophasesampIndD43nAb)
  tab1 = table(dat$Bserostatus, dat$EventIndPrimaryD43)[,2:1] # [,2:1] moves cases before non-cases
  dat=subset(dat1, Trialstage==i & ph1.D43 & Trt==0 & TwophasesampIndD43nAb)
  tab0 = table(dat$Bserostatus, dat$EventIndPrimaryD43)[,2:1] # [,2:1] moves cases before non-cases
  f(tab2, tab1, tab0)
}
```


  
### Check which ptids are in which batch

We have list of ptids sampled in step 2 in both stages of the trial.
```{r, include=T}
stage2step2=read.csv("~/Aiying700.csv")
dat_mapped$stage2step2 = dat_mapped$Subjectid %in% stage2step2$Unique.Subject.Identifier
dat_proc$stage2step2 = dat_proc$Ptid %in% stage2step2$Unique.Subject.Identifier

stage1step2=read.csv("~/JinStage1Step2.csv")
dat_mapped$stage1step2 = dat_mapped$SUBJID %in% stage1step2$SUBJID
dat_proc$stage1step2 = dat_proc$SUBJID %in% stage1step2$SUBJID
```

Stage 2, nAb. batch 1 = step2 for both cases and noncases
```{r}
with(subset(dat_proc, Trt==1 & Trialstage==2 & ph2.D43.nAb), table(stage2step2, EventIndPrimaryD1, nAbBatch))
with(subset(dat_proc, Trt==0 & Trialstage==2 & ph2.D43.nAb), table(stage2step2, EventIndPrimaryD1, nAbBatch))
with(subset(dat_proc, Trt==1 & Trialstage==2 & ph2.D22.nAb), table(stage2step2, EventIndPrimaryD1, nAbBatch))
with(subset(dat_proc, Trt==0 & Trialstage==2 & ph2.D22.nAb), table(stage2step2, EventIndPrimaryD1, nAbBatch))
```

Stage 1, nAb. Most non-cases are done in batch 2, most cases are done in batch 1. Step 1 and 2 are spread mostly equally between batches.
```{r}
with(subset(dat_proc, Trialstage==1 & ph2.D43.nAb), table(stage1step2, nAbBatch, EventIndPrimaryD1))
```

bAb.

```{r}
# stage 1
with(subset(dat_proc, Trialstage==1 & ph2.D22.bAb), table(stage1step2, EventIndPrimaryD1))

# stage 2
with(subset(dat_proc, Trialstage==2 & ph2.D22.bAb), table(stage2step2, EventIndPrimaryD1))
```



