---
title: "IB-201P and IB-202P Exploratory Plots (I)"
output: 
  pdf_document:
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(copcor)
library(survey)
library(kyotil)
library(glue)
library(Hmisc)
library(knitr)
library(GGally)
```

```{r data, echo=F, include=F}
config.processing <- config::get(config = "iliad_ib202p", file="/home/yfong/correlates_processing/config.yml") 
dat_mapped_202=read.csv(config.processing$mapped_data)

config.processing <- config::get(config = "iliad_ib201p", file="/home/yfong/correlates_processing/config.yml") 
dat_mapped_201=read.csv(config.processing$mapped_data)
dat_mapped_201$Trt02[is.na(dat_mapped_201$Trt02)]=0

# config.reporting  <- config::get(config = "iliad_ib202p, file="/home/yfong/correlates_reporting2/config.yml") 
# dat_proc=read.csv(config.reporting$data_cleaned)

assay_metadata=read.csv(glue('~/correlates_reporting2/assay_metadata/iliad_ib202p_assay_metadata.csv'))
assays = assay_metadata$assay
panels = unique(assay_metadata$panel)
antigens = c("WCE", setdiff(unique(assay_metadata$antigen), c("WCE", NA)))

mytable(dat_mapped_202$Trt) # 21 0s and 24 1s
mytable(dat_mapped_202$Perprotocol) # all 1
mytable(dat_mapped_202$EventIndPrimaryC14) # all 1

summary(dat_mapped_202$Day28_FHA_Nasal_IgA)
summary(10**(dat_mapped_202$Day28_FHA_Nasal_IgA)) # min is half lloq

summary(dat_mapped_202$Day28_FHA_Serum_IgA)
summary(10**(dat_mapped_202$Day28_FHA_Serum_IgA)) # min is half lloq
```

```{r}
mytable(dat_mapped_201$Trt01, dat_mapped_201$Trt02)
mytable(dat_mapped_202$Trt)
```

# Data missingness pattern



# Boxplots comparing treatment groups and popluations

The BPZE1-vaccinated in IB-201p have higher Day28_FHA_Nasal_IgA than those in IB-202p. The same is also true when we compare the comparison group. Is this true? Is it due to background differences? B_FHA_Nasal_IgA is missing from IB-202p, right?

```{r boxplots, echo=F}
ylim=c(-1.4,2.2)

par(mfrow=c(1,3)); shrink_margin()
myboxplot(Day28_FHA_Nasal_IgA~Trt01, dat_mapped_201, ylim=ylim, xlab="Trt01", main="IB-201p")
myboxplot(Day28_FHA_Nasal_IgA~Trt02, dat_mapped_201, ylim=ylim, xlab="Trt02", main="IB-201p")
myboxplot(Day28_FHA_Nasal_IgA~Trt,   dat_mapped_202, ylim=ylim, xlab="Trt", main="IB-202p")

par(mfrow=c(1,3)); shrink_margin()
myboxplot(B_FHA_Nasal_IgA~Trt01, dat_mapped_201, ylim=ylim, xlab="Trt01", main="IB-201p")
myboxplot(B_FHA_Nasal_IgA~Trt02, dat_mapped_201, ylim=ylim, xlab="Trt02", main="IB-201p")
# myboxplot(B_FHA_Nasal_IgA~Trt,   dat_mapped_202, ylim=ylim, xlab="Trt", main="IB-202p")

wilcox.test(subset(dat_mapped_201, Trt01==0, Day28_FHA_Nasal_IgA, drop=T), 
            subset(dat_mapped_202, Trt==1, Day28_FHA_Nasal_IgA, drop=T))


```

```{r scatterplot_age}

par(mfrow=c(1,2))
shrink_margin()
plot(Day28_FHA_Nasal_IgA~Age, dat_mapped_201, ylim=ylim)
abline(lm(Day28_FHA_Nasal_IgA~Age, dat_mapped_201))
plot(Day28_FHA_Nasal_IgA~Age, dat_mapped_202, ylim=ylim)
abline(lm(Day28_FHA_Nasal_IgA~Age, dat_mapped_202))

```

\clearpage

# Pairs plots for different antigens within the same class

```{r, echo=F}
make_pairs=function(p) {
  min_val = min(dat_mapped_201[,glue("Day28_{antigens}_{p}")], dat_mapped_202[,glue("Day28_{antigens}_{p}")], na.rm=T)
  max_val = max(dat_mapped_201[,glue("Day28_{antigens}_{p}")], dat_mapped_202[,glue("Day28_{antigens}_{p}")], na.rm=T)
  custom_continuous <- function(data, mapping, ...) {
    ggplot(data = data, mapping = mapping) +
      geom_point() +
      xlim(min_val, max_val) + ylim(min_val, max_val)  # adjust these limits as needed
  }

  tmp = dat_mapped_201[,glue("Day28_{antigens}_{p}")]
  tmp = tmp[complete.cases(tmp),]
  capture.output(suppressWarnings(suppressMessages({  
    p2 <- ggpairs(tmp,
      lower = list(continuous = custom_continuous))+ theme(
      strip.text = element_text(size = 7))
    p2
  })))
  
  tmp = dat_mapped_202[,glue("Day28_{antigens}_{p}")]
  tmp = tmp[complete.cases(tmp),]
  capture.output(suppressWarnings(suppressMessages({  
    p1 <- ggpairs(tmp,
      lower = list(continuous = custom_continuous)) + theme(
      strip.text = element_text(size = 7))
    p1
  })))
  
}
```

\newpage
```{r fig.show='hold', fig.width=7, fig.height=7, out.width='49%', echo=F, fig.cap="Nasal IgA. Left: IB-201P; right: IB-202P."}
a <- make_pairs (panels[1])
```

\newpage
```{r fig.show='hold', fig.width=7, fig.height=7, out.width='49%', echo=F, fig.cap="Normalized nasal IgA. Left: IB-201P; right: IB-202P."}
a <- make_pairs (panels[2])
```

\newpage
```{r fig.show='hold', fig.width=7, fig.height=7, out.width='49%', echo=F, fig.cap="Serum IgA. Left: IB-201P; right: IB-202P."}
a <- make_pairs (panels[3])
```

\newpage
```{r fig.show='hold', fig.width=7, fig.height=7, out.width='49%', echo=F, fig.cap="Serum IgG. Left: IB-201P; right: IB-202P."}
a <- make_pairs (panels[4])
```

\newpage

# Correlation between sIgA and normalized sIgA

```{r correlation_between_sIgA_and_norm_sIgA, echo=F, fig.cap='Top: 201; bottom: 202.', fig.height=5.3, fig.width=14}
par(mfrow=c(2,5)); par(mar = c(4, 3, 2, 1), mgp = c(2, 0.5, 0))
for (a in antigens) {
  corplot(dat_mapped_201[,glue('Day28_{a}_Nasal_IgA')], dat_mapped_201[,glue('Day28_{a}_Norm_Nasal_IgA')], method="p", add.diagonal.line=F, main=a, xlab="Nasal IgA", ylab="Norm Nasal IgA", cex.main=1.2)
}
for (a in antigens) {
  corplot(dat_mapped_202[,glue('Day28_{a}_Nasal_IgA')], dat_mapped_202[,glue('Day28_{a}_Norm_Nasal_IgA')], method="p", add.diagonal.line=F, main=a, xlab="Nasal IgA", ylab="Norm Nasal IgA", cex.main=1.4)
}
```

\newpage

# Correlation between baseline and Day 28 markers

```{r correlation_between_baseline_and_D28_201, echo=F, fig.width=10, fig.height=10, fig.cap="IB-201P Trt 01"}
par(mfrow=c(5,5)); shrink_margin()

for (a in assays[1:21]) {
  corplot(dat_mapped_201[dat_mapped_201$Trt01==0,glue("B_{a}")], dat_mapped_201[dat_mapped_201$Trt01==0,glue("Day28_{a}")], main=a, xlab="Baseline", ylab="Day 28", method="p", cex.main=1)  
}

```


```{r correlation_between_baseline_and_D28_202, echo=F, fig.width=10, fig.height=10, fig.cap="IB-202P Trt 1"}
par(mfrow=c(5,5)); shrink_margin()

for (a in assays[1:22]) {
  if (!all(is.na(dat_mapped_202[,glue("B_{a}")]))) {
    corplot(dat_mapped_202[dat_mapped_202$Trt==1,glue("B_{a}")], dat_mapped_202[dat_mapped_202$Trt==1,glue("Day28_{a}")], main=a, xlab="Baseline", ylab="Day 28", method="p", cex.main=1.1)  
  } else {
    empty.plot()
  }
}
```
