---
title: "VAT08 Stage 1 and 2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


```{r load data, echo=FALSE, include=FALSE}
library(survey)
library(kyotil)

country.codes=c("Colombia", "Ghana", "Honduras", "India", "Japan", "Kenya", "Nepal", "United States", "Mexico", "Uganda", "Ukraine")
# "Colombia" = 1, "Ghana" = 2, "Honduras" = 3, "India" = 4, "Japan" = 5, "Kenya" = 6, "Nepal" = 7, "United States" = 8, "Mexico" = 9, "Uganda" = 10, "Ukraine" = 11

dat_mapped=read.csv('/trials/covpn/p3005/analysis/mapping_immune_correlates/combined/adata/COVID_Sanofi_stage1and2_mapped_20240117.csv')
# dat_proc = read.csv('/trials/covpn/p3005/analysis/correlates/Part_A_Blinded_Phase_Data/adata/vat08_combined_data_processed_20240111.csv')
dat_proc = read.csv('/trials/covpn/p3005/analysis/correlates/Part_A_Blinded_Phase_Data/adata/vat08_combined_data_processed_20240117.csv')

assay_metadata=read.csv('~/correlates_reporting2/assay_metadata/vat08_combined_assay_metadata.csv')
assays=assay_metadata$assay

dat_mapped$EventIndPrimaryD1 = dat_mapped$EventIndFirstInfectionD1
dat_mapped$EventTimePrimaryD1 = dat_mapped$EventTimeFirstInfectionD1
dat_mapped$EventIndPrimaryD43= dat_mapped$EventIndFirstInfectionD43
dat_mapped$EventTimePrimaryD43= dat_mapped$EventTimeFirstInfectionD43
dat_mapped$EarlyendpointD43 <- with(dat_mapped, EarlyinfectionD43==1 | (EventIndPrimaryD1==1 & EventTimePrimaryD1 < NumberdaysD1toD43 + 7),1,0)
dat_mapped$ph1.D43= with(dat_mapped, EarlyendpointD43==0 & Perprotocol==1 & EventTimePrimaryD43 >= 7)
dat_mapped$Senior=ifelse(dat_mapped$Age>=60,1,0)
dat_mapped$cc = country.codes[dat_mapped$Country]
dat_mapped$SUBJID = sub("VAT00008-","",dat_mapped$Subjectid)
dat_mapped$SUBJID = gsub("-","",dat_mapped$SUBJID,)

dat_proc$SUBJID = sub("VAT00008-","",dat_proc$Ptid)
dat_proc$SUBJID = gsub("-","",dat_proc$SUBJID,)
```

### Check which ptids are in which batch

```{r}
stage2step2=read.csv("~/Aiying700.csv")
stage1step2=read.csv("~/JinStage1Step2.csv")
dat_mapped$stage2step2 = dat_mapped$Subjectid %in% stage2step2$Unique.Subject.Identifier
dat_mapped$stage1step2 = dat_mapped$SUBJID %in% stage1step2$SUBJID
dat_proc$stage2step2 = dat_proc$Ptid %in% stage2step2$Unique.Subject.Identifier
dat_proc$stage1step2 = dat_proc$SUBJID %in% stage1step2$SUBJID

# stage2: batch 1 = step2 and nothing else
with(subset(dat_mapped, Trialstage==2), table(stage2step2, nAbBatch, EventIndPrimaryD1))

# stage 1
with(subset(dat_mapped, Trialstage==1), table(stage1step2, nAbBatch, EventIndPrimaryD1))

# bAb

# stage 1
with(subset(dat_proc, Trialstage==1 & TwophasesampIndD43bAb), table(stage1step2, EventIndPrimaryD1))

# stage 2
with(subset(dat_proc, Trialstage==2 & TwophasesampIndD43bAb), table(stage2step2, EventIndPrimaryD1))
```


### nAb markers correlation

The list of markers:
```{r}
assays=assays[startsWith(assays,"pseudoneutid50")]
print(assays)
```

Correlation is high between variant markers at both baseline and D43 in Stage 2 non-naive, vaccine arm.
```{r}
mypairs(subset(dat_proc, Trialstage==2 & Bserostatus==1 & Trt==1 & ph1.D43)[,"B"%.%assays[1:5]])
mypairs(subset(dat_proc, Trialstage==2 & Bserostatus==1 & Trt==1 & ph1.D43)[,"Day43"%.%assays[1:5]])
```

Correlation is medium between variant markers at D43 in Stage 2 naive, vaccine arm. The correlation between the ancestral marker and the other markers range between 0.63 and 0.67.
```{r}
mypairs(subset(dat_proc, Trialstage==2 & Bserostatus==0 & Trt==1 & ph1.D43)[,"B"%.%assays[1:5]])
mypairs(subset(dat_proc, Trialstage==2 & Bserostatus==0 & Trt==1 & ph1.D43)[,"Day43"%.%assays[1:5]])
```

Correlation is low between baseline and D22 or D43 in Stage 2 non-naive, vaccine arm.
```{r}
mypairs(subset(dat_proc, Trialstage==2 & Bserostatus==1 & Trt==1 & ph1.D43)[,c("B","Day22","Day43")%.%assays[1]])
```
Closer look at the relationship between baseline and Day 43 markers in the baseline positive. Note that the D43 markers appear saturated since level seems flat across different baseline marker levels.
```{r}
par(mfrow=c(2,4))
  # ancestral marker
  corplot(Day43pseudoneutid50~Bpseudoneutid50, subset(dat_proc, Trialstage==2 & Bserostatus==1 & Trt==1 & ph1.D43), ylim=c(0,4))
  myboxplot(Day43pseudoneutid50~I(Bpseudoneutid50>0.2), subset(dat_proc, Trialstage==2 & Bserostatus==1 & Trt==1 & ph1.D43), names=c("Undetectable at B","Detectable at B"), ylab="D43", ylim=c(0,4))
  my.interaction.plot(subset(dat_proc, Trialstage==2 & Bserostatus==1 & Trt==1 & ph1.D43 & !is.na(Bpseudoneutid50) & !is.na(Day43pseudoneutid50), c(Bpseudoneutid50, Day43pseudoneutid50)), 
                      x.ori = 0, xaxislabels = c("B", "D43"), cex.axis = 1, add = FALSE, xlab = "", ylab = "", pcol = NULL, lcol = NULL)  
  corplot(Delta43overBpseudoneutid50~Bpseudoneutid50, subset(dat_proc, Trialstage==2 & Bserostatus==1 & Trt==1 & ph1.D43))
  
  # BA.1
  corplot(Day43pseudoneutid50_BA.1~Bpseudoneutid50_BA.1, subset(dat_proc, Trialstage==2 & Bserostatus==1 & Trt==1 & ph1.D43), ylim=c(0,4))
  myboxplot(Day43pseudoneutid50_BA.1~I(Bpseudoneutid50_BA.1>0.2), subset(dat_proc, Trialstage==2 & Bserostatus==1 & Trt==1 & ph1.D43), names=c("Undetectable at B","Detectable at B"), ylab="D43", ylim=c(0,4))
  my.interaction.plot(subset(dat_proc, Trialstage==2 & Bserostatus==1 & Trt==1 & ph1.D43 & !is.na(Bpseudoneutid50_BA.1) & !is.na(Day43pseudoneutid50_BA.1), c(Bpseudoneutid50_BA.1, Day43pseudoneutid50_BA.1)), 
                      x.ori = 0, xaxislabels = c("B", "D43"), cex.axis = 1, add = FALSE, xlab = "", ylab = "", pcol = NULL, lcol = NULL)  
  corplot(Delta43overBpseudoneutid50_BA.1~Bpseudoneutid50_BA.1, subset(dat_proc, Trialstage==2 & Bserostatus==1 & Trt==1 & ph1.D43))
```
 
### nAb markers missingness

Focusing on the vaccine arm. Tables are made with table(EventIndPrimaryD43, tmp, Bserostatus). The pattern is explained by the fact that samples from different steps have different set of markers measured.

```{r}
# for (tp in c("B")) {
for (tp in c("B", "Day22", "Day43")) {
  # before imputation
  dat1=dat_mapped
  # after imputation
  # dat1=dat_proc
  
  for(trt in 1) {
    myprint(tp, trt)
    for (i in 2:1) {
      cat(paste0("stage ", i, '\n'))
      if (trt==2) {
        # pool over arms
        dat=subset(dat1, Trialstage==i & ph1.D43)
      } else {
        dat=subset(dat1, Trialstage==i & ph1.D43 & Trt==trt)
      }
      for (i in 1:5) {
        dat[['tmp'%.%i]]=ifelse(is.na(dat[[tp%.%assays[i]]]), 0, 1)
      }
      dat$tmp=with(dat,paste0(tmp1,tmp2,tmp3,tmp4,tmp5))
      print(table(dat$tmp))
      cat("\n")
      # print(table(dat$EventIndPrimaryD43, dat$tmp, dat$Bserostatus))
    }
  }

}
```




```{r}
# for (tp in c("B")) {
# #for (tp in c("B", "Day22", "Day43")) {
#   # before imputation
#   dat1=dat_mapped
#   # after imputation
#   # dat1=dat_proc
#   
#   for(trt in 1) {
#     myprint(tp, trt)
#     for (i in 2:1) { # stage
#       cat(paste0("stage ", i, '\n'))
#       if (trt==2) {
#         # pool over arms
#         dat=subset(dat1, Trialstage==i & ph1.D43)
#       } else {
#         dat=subset(dat1, Trialstage==i & ph1.D43 & Trt==trt)
#       }
#       for (i in 1:5) {
#         dat[['tmp'%.%i]]=ifelse(is.na(dat[[tp%.%assays[i]]]), 0, 1)
#       }
#       dat$tmp=with(dat,paste0(tmp1,tmp2,tmp3,tmp4,tmp5))
#       print(mytable(dat$EventIndPrimaryD43, dat$tmp, dat$nAbBatch, dat$Bserostatus))
#     }
#   }
# 
# }
```


Distribution of D43 nAb ph2 samples by Bserostatus 0/1 and Case 1/0. (vaccine, placebo)
```{r}
dat1=dat_proc

f=function(tab2, tab1, tab0) {
  for (i in 1:2) {
    print(paste0(tab2[i,1], " (", tab1[i,1], ", ", tab0[i,1], ") ", tab2[i,2], " (", tab1[i,2], ", ", tab0[i,2], ")"))
  }
}

for (i in 2:1) {
  cat(paste0("stage ", i, '\n'))
  dat=subset(dat1, Trialstage==i & ph1.D43 & TwophasesampIndD43nAb)
  tab2 = table(dat$Bserostatus, dat$EventIndPrimaryD43)[,2:1] # [,2:1] moves cases before non-cases
  dat=subset(dat1, Trialstage==i & ph1.D43 & Trt==1 & TwophasesampIndD43nAb)
  tab1 = table(dat$Bserostatus, dat$EventIndPrimaryD43)[,2:1] # [,2:1] moves cases before non-cases
  dat=subset(dat1, Trialstage==i & ph1.D43 & Trt==0 & TwophasesampIndD43nAb)
  tab0 = table(dat$Bserostatus, dat$EventIndPrimaryD43)[,2:1] # [,2:1] moves cases before non-cases
  f(tab2, tab1, tab0)
}
```


Missingness across baseline, d22 and d43
```{r}
for(trt in 1) {
  myprint(trt)
  for (i in 2:1) {
    cat(paste0("stage ", i, '\n'))
    dat=subset(dat_proc, Trialstage==i & Trt==trt & ph1.D43)
    times=c("B","Day22","Day43")
    for (i in 1:3) {
      dat[['tmp'%.%i]]=ifelse(is.na(dat[[times[i]%.%'pseudoneutid50']]), 0, 1)
    }
    dat$tmp=with(dat,paste0(tmp1,tmp2,tmp3))
    print(table(dat$tmp))
    cat("\n")
  }
}
```


  