---
title: "Data Processing for AZD1222 Stage 2 Correlates"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(survey)
library(kyotil)

dat_mapped=read.csv('/trials/covpn/p3002/analysis/mapping_immune_correlates/stage2/adata/COVID_AstraZeneca_stage2_mapped_20240322.csv')
dat_mapped_stage1=read.csv('/trials/covpn/p3002/analysis/mapping_immune_correlates/stage1/adata/COVID_AstraZeneca_realdata_20221208.csv')
 
dat_mapped$EarlyendpointD57 <- with(dat_mapped, EarlyinfectionD57==1 | (EventIndPrimaryD1==1 & EventTimePrimaryD1 < NumberdaysD1toD57 + 7),1,0)
dat_mapped$ph1.D57 = with(dat_mapped, EarlyendpointD57==0 & Perprotocol==1 & EventTimePrimaryD57 >= 7)

dat_mapped$EventIndPrimaryType_short=substr(dat_mapped$EventIndPrimaryType,1,3)
dat_mapped$EventIndPrimaryType_short=ifelse(dat_mapped$EventIndPrimaryType_short=="", NA,dat_mapped$EventIndPrimaryType_short)
dat_mapped$EventIndPrimaryType_short=ifelse(is.na(dat_mapped$EventIndPrimaryType_short) & dat_mapped$EventIndPrimaryD1==1, "Unk",dat_mapped$EventIndPrimaryType_short)
dat_mapped$EventCalTimePrimaryD57 = with(dat_mapped, as.Date(D57Date)+EventTimePrimaryD57)
# color coding
dat_mapped$col=1
dat_mapped$col[!is.na(dat_mapped$Day57bindSpike_Delta3)]=3 # set ph2 ptids to green
dat_mapped$col[dat_mapped$SevereEventIndD57_120to21Dec10==1]=2 # set severe cases to red
dat_mapped$col2=1
dat_mapped$col2[dat_mapped$EventIndPrimaryD1==1]=2 # set cases to red


assay_metadata=read.csv('~/correlates_reporting2/assay_metadata/azd1222_stage2_assay_metadata.csv')
assays=assay_metadata$assay

dat_proc = read.csv('/trials/covpn/p3002/analysis/correlates/stage2/adata/azd1222_stage2_data_processed_20240322.csv')

times="Day"%.%c(57,90,180,360)
```


### Data descriptives

The dataset contains both treatment arms and both seropos and seroneg, and has US, CHL and PERU. Only the vaccine arm is sampled in stage 2.
```{r, include=F}
mytable(dat_mapped$Bserostatus)
mytable(dat_mapped$Country, dat_mapped$Trt)
mytable(dat_mapped$ph1.indicator, dat_mapped$Stage2_sampling_list, dat_mapped$Trt)
```



### Adjusting endpoint period

Distribution of event time by variant types. Ph2 cases are colored green and severe cases are colored red.

We chose 119/120 days post D57 to break the follow-up period into two because all Delta cases and all but two severe cases happened after that. 120 days post D57 is the first Delta case, on 2021-07-02.

We censor on 2021-12-10 to avoid the Omicron wave, the same day the PREVENT-19 stage2 data is censored on as well. We lose no severe cases by this censoring.
```{r, echo=T}
dat.tmp=subset(dat_mapped, EarlyinfectionD57==0 & Perprotocol==1 & Bserostatus==0 & Trt==1)

# D57 study day
myboxplot(EventTimePrimaryD57~EventIndPrimaryType_short, dat.tmp, ylab="EventTimePrimary57", col=dat.tmp$col, cex.axis=0.8)
abline(h=120, lty=2) 
print(min(subset(dat.tmp,EventIndPrimaryType_short=="Del",EventTimePrimaryD57),na.rm=T))
subset(dat.tmp,EventIndPrimaryType_short=="Del" & EventTimePrimaryD57==120, EventCalTimePrimaryD57)

# calendar day
myboxplot(EventCalTimePrimaryD57~EventIndPrimaryType_short, dat.tmp, ylab="Event Calendar Time", col=dat.tmp$col, cex.axis=0.8)
abline(h=120, lty=2) 
abline(h=as.Date("2021-12-10"), lty=2) 

# subset(dat_mapped,EventIndPrimaryType_short=="Del" & as.Date(DateDD1)<as.Date("2021-01-01"), c(Subjectid, EventTimePrimaryDate, DateDD1))
```


### Immunogenecity and imputation

Verifying marker values are subject to lower limits
```{r}
print(sort(unique(dat_mapped$Day57pseudoneutid50_D614G))[1:5])
print(sort(unique(dat_mapped$Day57pseudoneutid50_Delta))[1:5])
```


The following plot shows that Delta ID50 readouts are lower than ancestral ID50 and that marker level drops from over time. All cases are colored red.
```{r}
dat=dat_mapped[,c(rbind(times%.%"pseudoneutid50_D614G",times%.%"pseudoneutid50_Delta"))]
names(dat)=sub("pseudoneutid50","",names(dat))
names(dat)=sub("Day","D",names(dat))
myboxplot(dat, cex.axis=0.6, col=dat_mapped$col2)
```



Correlation is high between bAb markers (0.99 between the three Delta bAb markers), but moderate between the two nAb markers.
```{r}
dat=subset(dat_mapped, EarlyinfectionD57==0 & Perprotocol==1 & Bserostatus==0 & Trt==1)
dat=dat[,"Day57"%.%assays]
names(dat)=sub("Day57pseudoneut","",names(dat))
names(dat)=sub("Day57bindSpike_","",names(dat))
mypairs(dat)
```

A closer look at the correlation between ancestral ID50 and Delta ID50

```{r}
corplot(Day57pseudoneutid50_D614G~Day57pseudoneutid50_Delta, dat_mapped, asp=1)
```

bAb markers are all-or-none. 

For nAb, we will require Delta nAb to be present. For the 9 ptids without ancestral nAb but with Delta nAb, we will impute the ancestral nAb. There are a lot more ptids with just ancestral nAb but we won't use them in the correlates study to allow comparison between Delta and ancestral nAb.
```{r}
dat=subset(dat_mapped, EarlyinfectionD57==0 & Perprotocol==1 & Bserostatus==0 & Trt==1)
for (i in 1:length(assays)) {
  dat[['tmp'%.%i]]=ifelse(is.na(dat[['Day57'%.%assays[i]]]), 0, 1)
}
dat$tmp=with(dat,paste0(tmp1,tmp2,tmp3,tmp4,tmp5,tmp6,tmp7,tmp8,tmp9,tmp10))
print(table(dat$tmp, dat$DeltaEventIndD57_120to21Dec10))
```

We will only impute ancestral ID50 using Delta ID50. We will have two sets of weights, one for bAb and one for nAb. 
```{r}
dat=subset(dat_mapped)
dat$tmp1 = !is.na(dat$Day57pseudoneutid50_Delta)
dat$tmp2 = !is.na(dat$Day57bindSpike_Alpha)
dat$tmp=with(dat,paste0(as.integer(tmp1),as.integer(tmp2)))
print(table(dat$tmp, dat$DeltaEventIndD57_120to21Dec10))
```

```{r}
dat=subset(dat_mapped, ph1.D57==1)
dat$tmp1 = !is.na(dat$Day57pseudoneutid50_Delta)
dat$tmp2 = !is.na(dat$Day57bindSpike_Alpha)
dat$tmp=with(dat,paste0(as.integer(tmp1),as.integer(tmp2)))
print(table(dat$tmp, dat$DeltaEventIndD57_120to21Dec10))
```


### Two-phase sampling

Number of severe cases in ph1 and ph2
```{r}
with(subset(dat_mapped, EarlyinfectionD57==0 & Perprotocol==1 & Bserostatus==0 & Trt==1), mytable(!is.na(Day57bindSpike_Delta3), SevereEventIndD57_120to21Dec10))
```

Number of Delta cases in D57_120to21Dec10 in ph1 and ph2
```{r}
with(subset(dat_mapped, EarlyinfectionD57==0 & Perprotocol==1 & Bserostatus==0 & Trt==1), mytable(!is.na(Day57bindSpike_Delta3), DeltaEventIndD57_120to21Dec10))
```


Distributions of sampling weights:
```{r}
with (subset(dat_proc, ph2.D57nAb==1 & Trt==1 & Bserostatus==0), table(ph2.D57nAb, Wstratum))
with (subset(dat_proc, ph2.D57bAb==1 & Trt==1 & Bserostatus==0), table(ph2.D57bAb, Wstratum))
```



### Covariates adjustment


We will **adjust for Age in severe COVID correlates analyses**.
```{r}
coxph(Surv(SevereEventTimeD57_to21Dec10, SevereEventIndD57_120to21Dec10)~Age+risk_score, subset(dat_proc, ph1.D57_120==1 & Bserostatus==0 & Trt==1))
coxph(Surv(SevereEventTimeD57_to21Dec10, SevereEventIndD57_120to21Dec10)~Senior+risk_score, subset(dat_proc, ph1.D57_120==1 & Bserostatus==0 & Trt==1))
```


We will **adjust for Age>=65 in Delta COVID correlates analyses**. Age group is a stratification variable of the randomization and adjusted for in the primary efficacy analysis. Furthermore, nonparametric risk estimate shows that the risk as a function of age is a step function with change point at 65.


```{r}
coxph(Surv(DeltaEventTimeD57_to21Dec10, DeltaEventIndD57_120to21Dec10)~Age+risk_score, subset(dat_proc, ph1.D57_120==1 & Bserostatus==0 & Trt==1))
coxph(Surv(DeltaEventTimeD57_to21Dec10, DeltaEventIndD57_120to21Dec10)~Senior+risk_score, subset(dat_proc, ph1.D57_120==1 & Bserostatus==0 & Trt==1))
```