---
title: "Age Risk Correlate"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T)

library(survey)
library(kyotil)
library(readxl)
library(vaccine)
library(ggplot2)
library(cowplot)

dat_prevent19_stage1=read.csv('/trials/covpn/p3004/analysis/correlates/Part_A_Blinded_Phase_Data/adata/prevent19_data_processed_20240320.csv')
dat_azd1222_stage1=read.csv('/trials/covpn/p3002/analysis/correlates/Part_A_Blinded_Phase_Data/adata/azd1222_data_processed_with_riskscore.csv')
dat_unk302 = read.csv('/trials/covpn/p3004/analysis/correlates/UK302/adata/nvx_uk302_data_processed_20240320.csv')

```

Age is a potential confounder because immune markers are lower in older people and age is also associated with risk of mild-moderate-severe COVID and severe COVID in complicated ways. 


### Age risk curves

#### Summary

In AZ stage 1, the risk is a step function of age with a sudden drop at around 65 in the placebo arm; in the vaccine arm, the risk drops between 50 and 65. 

In NVX US stage 1, the risk shows a gradual drop as age increases in the placebo arm; in the vaccine arm, the risk is very low and mostly flat.

In NVX UK, the risk shows a gradual drop as age increases in the placebo arm; in the vaccine arm, the risk also decreases as age increases.

In NVX US stage 2, the risk of Delta COVID shows a gradual drop as age increases in the vaccine arm; the risk of severe COVID is low under 40, rises from 40 to 50 and stays elevated.



#### AZ stage 1

```{r}
load("~/correlates_reporting2/cor_coxph/output/age_risk/azd1222.stage1.Rdata")

plot_grid(
  p1=with(azd1222.stage1.plac, plot_ce(ests_cox, ests_np)) + coord_cartesian(ylim = c(0, 0.05), xlim = c(20, 95)) + ggtitle("Placebo"),
  p2=with(azd1222.stage1.vacc, plot_ce(ests_cox, ests_np)) + coord_cartesian(ylim = c(0, 0.05), xlim = c(20, 95)) + ggtitle("Vaccine"), 
  ncol = 2)

```


#### NVX PREVENT19 stage 1

```{r}
load("~/correlates_reporting2/cor_coxph/output/age_risk/prevent19.stage1.Rdata")

plot_grid(
  p1=with(prevent19.stage1.plac, plot_ce(ests_cox, ests_np)) + coord_cartesian(ylim = c(0, 0.05), xlim = c(20, 95)) + ggtitle("Placebo"),
  p2=with(prevent19.stage1.vacc, plot_ce(ests_cox, ests_cox_spline)) + coord_cartesian(ylim = c(0, 0.05), xlim = c(20, 95)) + ggtitle("Vaccine"), 
  ncol = 2)

```



#### NVX UK302 stage 1

```{r}
load("~/correlates_reporting2/cor_coxph/output/age_risk/uk302.Rdata")

plot_grid(
  p1=with(uk302.plac, plot_ce(ests_cox, ests_np)) + coord_cartesian(ylim = c(0, 0.05), xlim = c(20, 85)) + ggtitle("Placebo"),
  p2=with(uk302.vacc, plot_ce(ests_cox, ests_np)) + coord_cartesian(ylim = c(0, 0.05), xlim = c(20, 85)) + ggtitle("Vaccine"), 
  ncol = 2)

```



#### PREVENT19 stage 2

```{r}
load("~/correlates_reporting2/cor_coxph/output/age_risk/prevent19.stage2.Rdata")

plot_grid(
  p1=with(prevent19.stage2.delta,  plot_ce(ests_cox, ests_np)) + coord_cartesian(ylim = c(0, 0.1), xlim = c(20, 95)) + ggtitle("Delta COVID"),
  p2=with(prevent19.stage2.severe, plot_ce(ests_cox, ests_cox_spline)) + coord_cartesian(ylim = c(0, 0.05), xlim = c(20, 95)) + ggtitle("Severe COVID"), 
  ncol = 2)

```



### Cox models

#### NVX PREVENT19 stage 1, placebo arm
Age (continuous) is a better predictor than age group, log likelihood ratio 1.5.
```{r}
coxph(Surv(EventTimePrimaryD35,EventIndPrimaryD35)~Age, subset(dat_prevent19_stage1, ph1.D35==1 & Trt==0 & Bserostatus==0 & Country==0))
coxph(Surv(EventTimePrimaryD35,EventIndPrimaryD35)~Senior, subset(dat_prevent19_stage1, ph1.D35==1 & Trt==0 & Bserostatus==0 & Country==0))
```


###3 NVX UK302, placebo arm
Age group is a better predictor than age, log likelihood ratio 2.2.
```{r}
coxph(Surv(EventTimePrimaryD35,EventIndPrimaryD35)~Age+Region, subset(dat_unk302, ph1.D35==1 & Trt==0 & Bserostatus==0))
coxph(Surv(EventTimePrimaryD35,EventIndPrimaryD35)~Senior+Region, subset(dat_unk302, ph1.D35==1 & Trt==0 & Bserostatus==0))
```


#### AZ stage 1, placebo arm
Age group is a better predictor than age, log likelihood ratio 3-4 depending on whether risk score is adjusted.
```{r}
coxph(Surv(EventTimePrimaryD57,EventIndPrimaryD57)~Age+Country, subset(dat_azd1222_stage1, ph1.D57==1 & Trt==0 & Bserostatus==0))
coxph(Surv(EventTimePrimaryD57,EventIndPrimaryD57)~Senior+Country, subset(dat_azd1222_stage1, ph1.D57==1 & Trt==0 & Bserostatus==0))
coxph(Surv(EventTimePrimaryD57,EventIndPrimaryD57)~Age+Country+risk_score, subset(dat_azd1222_stage1, ph1.D57==1 & Trt==0 & Bserostatus==0))
coxph(Surv(EventTimePrimaryD57,EventIndPrimaryD57)~Senior+Country+risk_score, subset(dat_azd1222_stage1, ph1.D57==1 & Trt==0 & Bserostatus==0))
```

