---
title: "Covail Modeling"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(copcor)
library(survey)
library(kyotil)
library(glue)
library(Hmisc)
library(knitr)

config.reporting  <- config::get(config = "covail_tcell", file="/home/yfong/correlates_reporting2/config.yml") 
config.processing <- config::get(config = "covail", file="/home/yfong/correlates_processing/config.yml") 

dat_proc=read.csv(config.reporting$data_cleaned)
dat_mapped=read.csv(config.processing$mapped_data)
dat=subset(dat_proc, ph1.D15 & TrtonedosemRNA==1) 

assay_metadata=read.csv('~/correlates_reporting2/assay_metadata/covail_assay_metadata.csv')
assays=assay_metadata$assay

tmp=assay_metadata$assay[8:nrow(assay_metadata)]
tcellsubsets = sub("_Wuhan.N", "", tmp[endsWith(tmp, ".N")]); tcellsubsets
S=tmp[endsWith(tmp, ".S") & startsWith(tmp, "c")]
S1=c(tcellsubsets%.%"_COV2.CON.S1", tcellsubsets%.%"_BA.4.5.S1")
S2=c(tcellsubsets%.%"_COV2.CON.S2", tcellsubsets%.%"_BA.4.5.S2")
N=tcellsubsets%.%"_Wuhan.N"
tcellvv=c(S1, S2, N)

nAbs = setdiff(assays[startsWith(assays, "pseudoneutid50_")], c('pseudoneutid50_MDW'))
frnt=assays[startsWith(assays, "frnt")]

# special treatment for seromyx
# there are 198 assays, which are not tracked in assay metadata
tmp=read.csv("/trials/covpn/COVAILcorrelates/download_data/covail/SeromYxDataJuly23_2025.csv")
tmp$assay= paste0(tmp$tgttype, "_", tmp$vstrain)
seromyx=sort(unique(tmp$assay))


f=Surv(COVIDtimeD22toD181, COVIDIndD22toD181) ~ FOIstandardized + standardized_risk_score

primary = config.reporting$primary_markers

# compare all Pfizer and all Moderna and onedosemRNA to decide whether to stratify by stage or not
dat.onedosemRNA =    subset(dat_proc, ph1.D15 & TrtonedosemRNA==1 & !arm %in% c(16,17)) 
dat.onedoseModerna = subset(dat.onedosemRNA, arm<=6)
dat.onedosePfizer  = subset(dat.onedosemRNA, arm> 6)

```

## Intro

The antibody data includes arm 16 and 17. The T cell data excludes arm 16 and 17.

```{r compare ph1 between antibody study and t cell study}
mytable(dat_proc$ph1.D15, dat_proc$ph1.D15.tcell)
mytable(dat_proc$ph1.D15, dat_proc$arm)
mytable(dat_proc$ph1.D15.tcell, dat_proc$arm)
mytable(dat.onedosemRNA$ph1.D15.tcell, dat.onedosemRNA$ph1.D15)

```

```{r, fig.width=8, fig.height=8}
mypairs(dat_proc[,c("Bcd4_IFNg.IL2_Wuhan.N", "Bcd4_IFNg.IL2_BA.4.5.S", "Day15cd4_IFNg.IL2_BA.4.5.S", "Bpseudoneutid50_D614G", "Day15pseudoneutid50_D614G", "Bpseudoneutid50_BA.4.BA.5", "Day15pseudoneutid50_BA.4.BA.5")])
mypairs(dat_proc[,c("Bcd4_IFNg.IL2_Wuhan.N", "Bcd4_IFNg.IL2_BA.4.5.S", "Day15cd4_IFNg.IL2_BA.4.5.S")])
```



## Multivariate models having pseudo neut and T cell and seromyx


```{r}
design=  twophase(id = list( ~ 1,  ~ 1), strata = list(NULL,  ~ Wstratum.tcell), subset =  ~ ph2.D15.tcell, data = subset(dat.onedosemRNA, naive==0))

fits=list(
  svycoxph(f=Surv(COVIDtimeD22toD91, COVIDIndD22toD91)   ~ scale(Day15TIGG_BA45S) + I(scale(Bcd4_IFNg.IL2_BA.4.5.S)) * I(scale(Day15pseudoneutid50_BA.4.BA.5)) + FOIstandardized + standardized_risk_score + strata(stage), design),
  svycoxph(f=Surv(COVIDtimeD22toD91, COVIDIndD22toD91)   ~ scale(Day15IGA1_BA45S) + I(scale(Bcd4_IFNg.IL2_BA.4.5.S)) * I(scale(Day15pseudoneutid50_BA.4.BA.5)) + FOIstandardized + standardized_risk_score + strata(stage), design),
  svycoxph(f=Surv(COVIDtimeD22toD91, COVIDIndD22toD91)   ~ scale(Day15G2AH_BA45S) + I(scale(Bcd4_IFNg.IL2_BA.4.5.S)) * I(scale(Day15pseudoneutid50_BA.4.BA.5)) + FOIstandardized + standardized_risk_score + strata(stage), design),
  svycoxph(f=Surv(COVIDtimeD22toD91, COVIDIndD22toD91)   ~ scale(BTIGG_BA45S) + I(scale(Bcd4_IFNg.IL2_BA.4.5.S)) * I(scale(Day15pseudoneutid50_BA.4.BA.5)) + FOIstandardized + standardized_risk_score + strata(stage), design),
  svycoxph(f=Surv(COVIDtimeD22toD91, COVIDIndD22toD91)   ~ scale(BIGA1_BA45S) + I(scale(Bcd4_IFNg.IL2_BA.4.5.S)) * I(scale(Day15pseudoneutid50_BA.4.BA.5)) + FOIstandardized + standardized_risk_score + strata(stage), design),
  svycoxph(f=Surv(COVIDtimeD22toD91, COVIDIndD22toD91)   ~ scale(BG2AH_BA45S) + I(scale(Bcd4_IFNg.IL2_BA.4.5.S)) * I(scale(Day15pseudoneutid50_BA.4.BA.5)) + FOIstandardized + standardized_risk_score + strata(stage), design),
  
  svycoxph(f=Surv(COVIDtimeD22toD91, COVIDIndD22toD91)   ~ scale(Delta15overBTIGG_BA45S) + I(scale(Bcd4_IFNg.IL2_BA.4.5.S)) * I(scale(Day15pseudoneutid50_BA.4.BA.5)) + FOIstandardized + standardized_risk_score + strata(stage), design),
  svycoxph(f=Surv(COVIDtimeD22toD91, COVIDIndD22toD91)   ~ scale(Delta15overBIGA1_BA45S) + I(scale(Bcd4_IFNg.IL2_BA.4.5.S)) * I(scale(Day15pseudoneutid50_BA.4.BA.5)) + FOIstandardized + standardized_risk_score + strata(stage), design),
  svycoxph(f=Surv(COVIDtimeD22toD91, COVIDIndD22toD91)   ~ scale(Delta15overBG2AH_BA45S) + I(scale(Bcd4_IFNg.IL2_BA.4.5.S)) * I(scale(Day15pseudoneutid50_BA.4.BA.5)) + FOIstandardized + standardized_risk_score + strata(stage), design),
  svycoxph(f=Surv(COVIDtimeD22toD91, COVIDIndD22toD91)   ~ scale(Delta15overBpseudoneutid50_BA.4.BA.5) + I(scale(Bcd4_IFNg.IL2_BA.4.5.S)) * I(scale(Day15pseudoneutid50_BA.4.BA.5)) + FOIstandardized + standardized_risk_score + strata(stage), design),
  svycoxph(f=Surv(COVIDtimeD22toD91, COVIDIndD22toD91)   ~ scale(Delta15overBfrnt50_BA.4.BA.5) + I(scale(Bcd4_IFNg.IL2_BA.4.5.S)) * I(scale(Day15pseudoneutid50_BA.4.BA.5)) + FOIstandardized + standardized_risk_score + strata(stage), design),
  svycoxph(f=Surv(COVIDtimeD22toD91, COVIDIndD22toD91)   ~ scale(Delta15overBcd4_IFNg.IL2_BA.4.5.S) + I(scale(Bcd4_IFNg.IL2_BA.4.5.S)) * I(scale(Day15pseudoneutid50_BA.4.BA.5)) + FOIstandardized + standardized_risk_score + strata(stage), design)
)
tab=getFormattedSummary(fits, robust=T, exp=T); 
tab[is.na(tab)]=""
kable(tab)
```


## Multivariate models having pseudo neut and FRNT

```{r interaction models with covariates}
design=  twophase(id = list( ~ 1,  ~ 1), strata = list(NULL,  ~ Wstratum.frnt), subset =  ~ ph2.D15.frnt, data = subset(dat.onedosemRNA, naive==0))

fits=list(
  svycoxph(f=Surv(COVIDtimeD22toD181, COVIDIndD22toD181) ~ scale(Day15frnt50_BA.4.BA.5) + scale(Day15pseudoneutid50_BA.4.BA.5) + FOIstandardized + standardized_risk_score + strata(stage), design)
)
tab=getFormattedSummary(fits, robust=T, exp=T); 
tab[is.na(tab)]=""
kable(tab)
```


```{r check if frnt can be fit with xassays}
design=  twophase(id = list( ~ 1,  ~ 1), strata = list(NULL,  ~ Wstratum.xassays), subset =  ~ ph2.D15.xassays, data = subset(dat.onedosemRNA, naive==0))

fits=list(
  svycoxph(f=Surv(COVIDtimeD22toD181, COVIDIndD22toD181) ~ scale(Day15frnt50_BA.4.BA.5) + scale(Day15pseudoneutid50_BA.4.BA.5) + FOIstandardized + standardized_risk_score + strata(stage), design)
)
tab=getFormattedSummary(fits, robust=T, exp=T); 
tab[is.na(tab)]=""
kable(tab)
```


## Multivariate models having pseudo neut and T cell

```{r checking if ph2.d15.xassays still works}
design=  twophase(id = list( ~ 1,  ~ 1), strata = list(NULL,  ~ Wstratum.xassays), subset =  ~ ph2.D15.xassays, data = subset(dat.onedosemRNA, naive==0))

# yes interaction for D22toD91
fits=list(
  svycoxph(f=Surv(COVIDtimeD22toD181, COVIDIndD22toD181) ~ I(scale(Bcd4_IFNg.IL2_BA.4.5.S)) * I(scale(Day15pseudoneutid50_BA.4.BA.5)) + FOIstandardized + standardized_risk_score + strata(stage), design),
  svycoxph(f=Surv(COVIDtimeD22toD91, COVIDIndD22toD91)   ~ I(scale(Bcd4_IFNg.IL2_BA.4.5.S)) * I(scale(Day15pseudoneutid50_BA.4.BA.5)) + FOIstandardized + standardized_risk_score + strata(stage), design)
)
tab=getFormattedSummary(fits, robust=T, exp=T); 
tab[is.na(tab)]=""
kable(tab)
```

```{r interaction models with covariates}
design=  twophase(id = list( ~ 1,  ~ 1), strata = list(NULL,  ~ Wstratum.tcell), subset =  ~ ph2.D15.tcell, data = subset(dat.onedosemRNA, naive==0))

# yes interaction for D22toD91
fits=list(
  svycoxph(f=Surv(COVIDtimeD22toD181, COVIDIndD22toD181) ~ I(scale(Bcd4_IFNg.IL2_BA.4.5.S)) * I(scale(Day15pseudoneutid50_BA.4.BA.5)) + FOIstandardized + standardized_risk_score + strata(stage), design),
  svycoxph(f=Surv(COVIDtimeD22toD91, COVIDIndD22toD91)   ~ I(scale(Bcd4_IFNg.IL2_BA.4.5.S)) * I(scale(Day15pseudoneutid50_BA.4.BA.5)) + FOIstandardized + standardized_risk_score + strata(stage), design)
)
tab=getFormattedSummary(fits, robust=T, exp=T); 
tab[is.na(tab)]=""
kable(tab)

# yes interaction for D22toD91
fits=list(
  svycoxph(f=Surv(COVIDtimeD22toD181, COVIDIndD22toD181) ~ I(scale(Bcd4_IFNg.IL2_BA.4.5.S)) * I(scale(Day15pseudoneutid50_D614G)) + FOIstandardized + standardized_risk_score + strata(stage), design),
  svycoxph(f=Surv(COVIDtimeD22toD91, COVIDIndD22toD91)   ~ I(scale(Bcd4_IFNg.IL2_BA.4.5.S)) * I(scale(Day15pseudoneutid50_D614G)) + FOIstandardized + standardized_risk_score + strata(stage), design)
)
tab=getFormattedSummary(fits, robust=T, exp=T); 
tab[is.na(tab)]=""
kable(tab)

# yes interaction for D22toD91
fits=list(
  svycoxph(f=Surv(COVIDtimeD22toD181, COVIDIndD22toD181) ~ I(scale(Bcd4_FS_BA.4.5.S)) * I(scale(Day15pseudoneutid50_BA.4.BA.5)) + FOIstandardized + standardized_risk_score + strata(stage), design),
  svycoxph(f=Surv(COVIDtimeD22toD91, COVIDIndD22toD91)   ~ I(scale(Bcd4_FS_BA.4.5.S)) * I(scale(Day15pseudoneutid50_BA.4.BA.5)) + FOIstandardized + standardized_risk_score + strata(stage), design)
)
tab=getFormattedSummary(fits, robust=T, exp=T); 
tab[is.na(tab)]=""
kable(tab)

# yes interaction for D22toD91
fits=list(
  svycoxph(f=Surv(COVIDtimeD22toD181, COVIDIndD22toD181) ~ I(scale(Bcd4_FS_BA.4.5.S)) * I(scale(Bpseudoneutid50_D614G)) + FOIstandardized + standardized_risk_score + strata(stage), design),
  svycoxph(f=Surv(COVIDtimeD22toD91, COVIDIndD22toD91)   ~ I(scale(Bcd4_FS_BA.4.5.S)) * I(scale(Bpseudoneutid50_D614G)) + FOIstandardized + standardized_risk_score + strata(stage), design)
)
tab=getFormattedSummary(fits, robust=T, exp=T); 
tab[is.na(tab)]=""
kable(tab)

# no interaction
fits=list(
  svycoxph(f=Surv(COVIDtimeD22toD181, COVIDIndD22toD181) ~ I(scale(Bcd4_IFNg.IL2_BA.4.5.S)) * I(scale(Day15cd4_IFNg.IL2_BA.4.5.S)) + FOIstandardized + standardized_risk_score + strata(stage), design),
  svycoxph(f=Surv(COVIDtimeD22toD91, COVIDIndD22toD91)   ~ I(scale(Bcd4_IFNg.IL2_BA.4.5.S)) * I(scale(Day15cd4_IFNg.IL2_BA.4.5.S)) + FOIstandardized + standardized_risk_score + strata(stage), design)
)
tab=getFormattedSummary(fits, robust=T, exp=T, type=5); 
tab[is.na(tab)]=""
kable(tab)

# no interaction
fits=list(
  svycoxph(f=Surv(COVIDtimeD22toD181, COVIDIndD22toD181) ~ I(scale(Bcd4_IFNg.IL2_BA.4.5.S)) * I(scale(Bpseudoneutid50_BA.4.BA.5)) + FOIstandardized + standardized_risk_score + strata(stage), design),
  svycoxph(f=Surv(COVIDtimeD22toD91, COVIDIndD22toD91)   ~ I(scale(Bcd4_IFNg.IL2_BA.4.5.S)) * I(scale(Bpseudoneutid50_BA.4.BA.5)) + FOIstandardized + standardized_risk_score + strata(stage), design)
)
tab=getFormattedSummary(fits, robust=T, exp=T); 
tab[is.na(tab)]=""
kable(tab)

# yes interaction for D22toD91
fits=list(
  svycoxph(f=Surv(COVIDtimeD22toD181, COVIDIndD22toD181) ~ I(scale(Bcd4_IFNg.IL2_BA.4.5.S)) * I(scale(Bpseudoneutid50_D614G)) + FOIstandardized + standardized_risk_score + strata(stage), design),
  svycoxph(f=Surv(COVIDtimeD22toD91, COVIDIndD22toD91)   ~ I(scale(Bcd4_IFNg.IL2_BA.4.5.S)) * I(scale(Bpseudoneutid50_D614G)) + FOIstandardized + standardized_risk_score + strata(stage), design)
)
tab=getFormattedSummary(fits, robust=T, exp=T); 
tab[is.na(tab)]=""
kable(tab)
```

```{r plot for interaction model, fig.width=10, fig.height=4.5}
par(mfrow=c(1,2)); shrink_margin()

design=  twophase(id = list( ~ 1,  ~ 1), strata = list(NULL,  ~ Wstratum.tcell), subset =  ~ ph2.D15.tcell, data = subset(dat.onedosemRNA, naive==0))

dat=subset(dat.onedosemRNA, naive==0 & ph2.D15.tcell)

# make an interaction plot for one of the models
fit = svycoxph(f=Surv(COVIDtimeD22toD91, COVIDIndD22toD91)   ~ Bcd4_IFNg.IL2_BA.4.5.S * Day15pseudoneutid50_BA.4.BA.5 + FOIstandardized + standardized_risk_score + strata(stage), design)
fit

# first, x axis is d15 nab
xx = wtd.quantile(dat$Day15pseudoneutid50_BA.4.BA.5, dat$Wstratum.tcell, seq(0.05,0.95, by=0.05)); xx
yy = wtd.quantile(dat$Bcd4_IFNg.IL2_BA.4.5.S, dat$Wstratum.tcell, c(0.25,0.50,0.75)); yy
hrs=sapply(1:3, function (i) {
  dat.tmp= cbind(
    Bcd4_IFNg.IL2_BA.4.5.S=yy[i], 
    Day15pseudoneutid50_BA.4.BA.5=xx, 
    FOIstandardized=wtd.quantile(dat$FOIstandardized, dat$Wstratum.tcell, .5),
    standardized_risk_score=wtd.quantile(dat$FOIstandardized, dat$standardized_risk_score, .5),
    yy[i]*xx
  )
  hr = dat.tmp %*% coef(fit)
})
colnames(hrs)=c("1st Q","Median","3rd Q")
mymatplot(xx, hrs, xlab="Day15pseudoneutid50_BA.4.BA.5", legend.title="Bcd4_IFNg.IL2_BA.4.5.S", legend.x=3, ylab="log relative risk compared to baseline", col=1:3, legend.cex = .8)

# second, x axis is B cd4
xx = wtd.quantile(dat$Bcd4_IFNg.IL2_BA.4.5.S, dat$Wstratum.tcell, seq(0.05,0.95, by=0.05)); xx
yy = wtd.quantile(dat$Day15pseudoneutid50_BA.4.BA.5, dat$Wstratum.tcell, c(0.25,0.50,0.75)); yy
hrs=sapply(1:3, function (i) {
  dat.tmp= cbind(
    Bcd4_IFNg.IL2_BA.4.5.S=xx, 
    Day15pseudoneutid50_BA.4.BA.5=yy[i], 
    FOIstandardized=wtd.quantile(dat$FOIstandardized, dat$Wstratum.tcell, .5),
    standardized_risk_score=wtd.quantile(dat$FOIstandardized, dat$standardized_risk_score, .5),
    yy[i]*xx
  )
  hr = dat.tmp %*% coef(fit)
})
colnames(hrs)=c("1st Q","Median","3rd Q")
mymatplot(xx, hrs, xlab="Bcd4_IFNg.IL2_BA.4.5.S", legend.title="Day15pseudoneutid50_BA.4.BA.5", legend.x=3, ylab="log relative risk compared to baseline", col=1:3, legend.cex = .8)

```

```{r plot for interaction model quality check with scale, fig.width=10, fig.height=4.5}
par(mfrow=c(1,2)); shrink_margin()

design=  twophase(id = list( ~ 1,  ~ 1), strata = list(NULL,  ~ Wstratum.tcell), subset =  ~ ph2.D15.tcell, data = subset(dat.onedosemRNA, naive==0))

dat=subset(dat.onedosemRNA, naive==0 & ph2.D15.tcell)

# make an interaction plot for one of the models
fit = svycoxph(f=Surv(COVIDtimeD22toD91, COVIDIndD22toD91)   ~ scale(Bcd4_IFNg.IL2_BA.4.5.S) * scale(Day15pseudoneutid50_BA.4.BA.5) + scale(FOIstandardized) + scale(standardized_risk_score) + strata(stage), design)
fit

# first, x axis is d15 nab
xx = seq(-2,2,by=0.2)
yy = c(-1,0,1)
hrs=sapply(1:3, function (i) {
  dat.tmp= cbind(
    Bcd4_IFNg.IL2_BA.4.5.S=yy[i], 
    Day15pseudoneutid50_BA.4.BA.5=xx, 
    FOIstandardized=0,
    standardized_risk_score=0,
    yy[i]*xx
  )
  hr = dat.tmp %*% coef(fit)
})
colnames(hrs)=c("-1","0","1")
mymatplot(xx, hrs, xlab="Day15pseudoneutid50_BA.4.BA.5", legend.title="Bcd4_IFNg.IL2_BA.4.5.S", legend.x=3, ylab="log relative risk compared to baseline", col=1:3, legend.cex = .8)

# second, x axis is B cd4
xx = seq(-2,2,by=0.2)
yy = c(-1,0,1)
hrs=sapply(1:3, function (i) {
  dat.tmp= cbind(
    Bcd4_IFNg.IL2_BA.4.5.S=xx, 
    Day15pseudoneutid50_BA.4.BA.5=yy[i], 
    FOIstandardized=0,
    standardized_risk_score=0,
    yy[i]*xx
  )
  hr = dat.tmp %*% coef(fit)
})
colnames(hrs)=c("-1","0","1")
mymatplot(xx, hrs, xlab="Bcd4_IFNg.IL2_BA.4.5.S", legend.title="Day15pseudoneutid50_BA.4.BA.5", legend.x=3, ylab="log relative risk compared to baseline", col=1:3, legend.cex = .8)

```

```{r interaction models}
design=  twophase(id = list( ~ 1,  ~ 1), strata = list(NULL,  ~ Wstratum.tcell), subset =  ~ ph2.D15.tcell, data = subset(dat.onedosemRNA, naive==0))

# yes interaction for D22toD91
fits=list(
  svycoxph(f=Surv(COVIDtimeD22toD181, COVIDIndD22toD181) ~ I(scale(Bcd4_IFNg.IL2_BA.4.5.S)) * I(scale(Day15pseudoneutid50_BA.4.BA.5)), design),
  svycoxph(f=Surv(COVIDtimeD22toD91, COVIDIndD22toD91)   ~ I(scale(Bcd4_IFNg.IL2_BA.4.5.S)) * I(scale(Day15pseudoneutid50_BA.4.BA.5)), design)
)
tab=getFormattedSummary(fits, robust=T, exp=T); 
tab[is.na(tab)]=""
kable(tab)

# yes interaction for D22toD91
fits=list(
  svycoxph(f=Surv(COVIDtimeD22toD181, COVIDIndD22toD181) ~ I(scale(Bcd4_IFNg.IL2_BA.4.5.S)) * I(scale(Day15pseudoneutid50_D614G)), design),
  svycoxph(f=Surv(COVIDtimeD22toD91, COVIDIndD22toD91)   ~ I(scale(Bcd4_IFNg.IL2_BA.4.5.S)) * I(scale(Day15pseudoneutid50_D614G)), design)
)
tab=getFormattedSummary(fits, robust=T, exp=T); 
tab[is.na(tab)]=""
kable(tab)

# yes interaction for D22toD91
fits=list(
  svycoxph(f=Surv(COVIDtimeD22toD181, COVIDIndD22toD181) ~ I(scale(Bcd4_FS_BA.4.5.S)) * I(scale(Day15pseudoneutid50_BA.4.BA.5)), design),
  svycoxph(f=Surv(COVIDtimeD22toD91, COVIDIndD22toD91)   ~ I(scale(Bcd4_FS_BA.4.5.S)) * I(scale(Day15pseudoneutid50_BA.4.BA.5)), design)
)
tab=getFormattedSummary(fits, robust=T, exp=T); 
tab[is.na(tab)]=""
kable(tab)

# yes interaction for D22toD91
fits=list(
  svycoxph(f=Surv(COVIDtimeD22toD181, COVIDIndD22toD181) ~ I(scale(Bcd4_FS_BA.4.5.S)) * I(scale(Bpseudoneutid50_D614G)), design),
  svycoxph(f=Surv(COVIDtimeD22toD91, COVIDIndD22toD91)   ~ I(scale(Bcd4_FS_BA.4.5.S)) * I(scale(Bpseudoneutid50_D614G)), design)
)
tab=getFormattedSummary(fits, robust=T, exp=T); 
tab[is.na(tab)]=""
kable(tab)

# no interaction
fits=list(
  svycoxph(f=Surv(COVIDtimeD22toD181, COVIDIndD22toD181) ~ I(scale(Bcd4_IFNg.IL2_BA.4.5.S)) * I(scale(Day15cd4_IFNg.IL2_BA.4.5.S)), design),
  svycoxph(f=Surv(COVIDtimeD22toD91, COVIDIndD22toD91)   ~ I(scale(Bcd4_IFNg.IL2_BA.4.5.S)) * I(scale(Day15cd4_IFNg.IL2_BA.4.5.S)), design)
)
tab=getFormattedSummary(fits, robust=T, exp=T, type=5); 
tab[is.na(tab)]=""
kable(tab)

# no interaction
fits=list(
  svycoxph(f=Surv(COVIDtimeD22toD181, COVIDIndD22toD181) ~ I(scale(Bcd4_IFNg.IL2_BA.4.5.S)) * I(scale(Bpseudoneutid50_BA.4.BA.5)), design),
  svycoxph(f=Surv(COVIDtimeD22toD91, COVIDIndD22toD91)   ~ I(scale(Bcd4_IFNg.IL2_BA.4.5.S)) * I(scale(Bpseudoneutid50_BA.4.BA.5)), design)
)
tab=getFormattedSummary(fits, robust=T, exp=T); 
tab[is.na(tab)]=""
kable(tab)

# yes interaction for D22toD91
fits=list(
  svycoxph(f=Surv(COVIDtimeD22toD181, COVIDIndD22toD181) ~ I(scale(Bcd4_IFNg.IL2_BA.4.5.S)) * I(scale(Bpseudoneutid50_D614G)), design),
  svycoxph(f=Surv(COVIDtimeD22toD91, COVIDIndD22toD91)   ~ I(scale(Bcd4_IFNg.IL2_BA.4.5.S)) * I(scale(Bpseudoneutid50_D614G)), design)
)
tab=getFormattedSummary(fits, robust=T, exp=T); 
tab[is.na(tab)]=""
kable(tab)

```

```{r }
design=  twophase(id = list( ~ 1,  ~ 1), strata = list(NULL,  ~ Wstratum.tcell), subset =  ~ ph2.D15.tcell, data = subset(dat.onedosemRNA, naive==0))

fits=list(
  svycoxph(f=Surv(COVIDtimeD22toD181, COVIDIndD22toD181) ~ Bcd4_IFNg.IL2_BA.4.5.S + Day15cd4_IFNg.IL2_BA.4.5.S + Bpseudoneutid50_BA.4.BA.5 + Day15pseudoneutid50_BA.4.BA.5, design)
,
  svycoxph(f=Surv(COVIDtimeD22toD181, COVIDIndD22toD181) ~ Bcd4_IFNg.IL2_BA.4.5.S  + Day15pseudoneutid50_BA.4.BA.5, design)
,
  svycoxph(f=Surv(COVIDtimeD22toD181, COVIDIndD22toD181) ~ Bcd4_IFNg.IL2_BA.4.5.S + Day15cd4_IFNg.IL2_BA.4.5.S, design)
,
  svycoxph(f=Surv(COVIDtimeD22toD181, COVIDIndD22toD181) ~ Bpseudoneutid50_BA.4.BA.5 + Day15pseudoneutid50_BA.4.BA.5, design)
,
  svycoxph(f=Surv(COVIDtimeD22toD181, COVIDIndD22toD181) ~ Bpseudoneutid50_BA.4.BA.5 + Bcd4_IFNg.IL2_BA.4.5.S, design)
,
  svycoxph(f=Surv(COVIDtimeD22toD181, COVIDIndD22toD181) ~ Day15cd4_IFNg.IL2_BA.4.5.S + Day15pseudoneutid50_BA.4.BA.5, design)
,
  svycoxph(f=Surv(COVIDtimeD22toD181, COVIDIndD22toD181) ~ Day15cd4_IFNg.IL2_BA.4.5.S + Bpseudoneutid50_BA.4.BA.5, design)
,
  svycoxph(f=Surv(COVIDtimeD22toD181, COVIDIndD22toD181) ~ Bcd4_IFNg.IL2_BA.4.5.S + Day15pseudoneutid50_BA.4.BA.5 + Bcd4_IFNg.IL2_Wuhan.N, design)
,
  svycoxph(f=Surv(COVIDtimeD22toD181, COVIDIndD22toD181) ~ Bcd4_IFNg.IL2_BA.4.5.S + Bcd4_IFNg.IL2_Wuhan.N, design)
)
tab=getFormattedSummary(fits, robust=T, exp=T, type=5); 
tab[is.na(tab)]=""
kable(tab)

# yes interaction for D22toD91
fits=list(
  svyglm(COVIDIndD22toD181 ~ I(scale(Bcd4_IFNg.IL2_BA.4.5.S)) + I(scale(Day15pseudoneutid50_BA.1)), design),
  svyglm(COVIDIndD22toD181 ~ I(scale(Day15pseudoneutid50_BA.1)) , design),
  svyglm(COVIDIndD22toD181 ~ I(scale(Bcd4_IFNg.IL2_BA.4.5.S)), design),
  svyglm(COVIDIndD22toD91 ~ I(scale(Bcd4_IFNg.IL2_BA.4.5.S)) + I(scale(Day15pseudoneutid50_BA.1)), design),
  svyglm(COVIDIndD22toD91 ~ I(scale(Day15pseudoneutid50_BA.1)) , design),
  svyglm(COVIDIndD22toD91 ~ I(scale(Bcd4_IFNg.IL2_BA.4.5.S)), design)
)
# sapply(fits, trainauc, w=T)
sapply(fits, trainauc)

library(aucm)
fit.a = rauc(COVIDIndD22toD181 ~ I(scale(Bcd4_IFNg.IL2_BA.4.5.S)) + I(scale(Day15pseudoneutid50_BA.1)), dat = subset(dat.onedosemRNA, naive==0 & ph2.D15.tcell))
fit.a$train.auc

fit.e = eauc(COVIDIndD22toD181 ~ I(scale(Bcd4_IFNg.IL2_BA.4.5.S)) + I(scale(Day15pseudoneutid50_BA.1)), dat = subset(dat.onedosemRNA, naive==0 & ph2.D15.tcell))
fastauc(drop(with(subset(dat.onedosemRNA, naive==0 & ph2.D15.tcell), I(scale(Bcd4_IFNg.IL2_BA.4.5.S)) + fit.e$coef[2]*I(scale(Day15pseudoneutid50_BA.1))))
, subset(dat.onedosemRNA, naive==0 & ph2.D15.tcell, COVIDIndD22toD181, drop=T))



summary(fits[[1]])
summary(fits[[2]])
summary(fits[[3]])
summary(fits[[4]])

trainauc(fits[[1]])
trainauc(fits[[2]])
trainauc(fits[[3]])
trainauc(fits[[4]])


tab=getFormattedSummary(fits, robust=T, exp=T, type=5); 
tab[is.na(tab)]=""
kable(tab)



 
```

```{r}

dat.tmp = subset(dat_proc, naive==0 & ph2.D15.tcell & TrtonedosemRNA==1 & !arm %in% c(16,17)) 

fastauc(dat.tmp$Bcd4_IFNg.IL2_BA.4.5.S, dat.tmp$COVIDIndD22toD181)

fastauc(dat.tmp$Day15pseudoneutid50_BA.1, dat.tmp$COVIDIndD22toD181)

fit = glm(COVIDIndD22toD181 ~ I(scale(Bcd4_IFNg.IL2_BA.4.5.S)) * I(scale(Day15pseudoneutid50_BA.1)), dat.tmp, family="binomial")
trainauc(fit)

  
# fastauc(dat.tmp$Day15cd4_IFNg.IL2_BA.4.5.S, dat.tmp$COVIDIndD22toD181)

```


```{r scatterplot of t cell and nAb markers}

corplot(Bcd4_IFNg.IL2_BA.4.5.S~Day15pseudoneutid50_BA.4.BA.5, subset(dat.onedosemRNA, naive==0 & ph2.D15.tcell), col=subset(dat.onedosemRNA, naive==0 & ph2.D15.tcell, COVIDIndD22toD181, drop=T)+1, cex=1.2)
abline(h=wtd.quantile(subset(dat.onedosemRNA, naive==0 & ph2.D15.tcell, Bcd4_IFNg.IL2_BA.4.5.S, drop=T), subset(dat.onedosemRNA, naive==0 & ph2.D15.tcell, wt.D15.tcell, drop=T), .5))
abline(v=wtd.quantile(subset(dat.onedosemRNA, naive==0 & ph2.D15.tcell, Day15pseudoneutid50_BA.4.BA.5, drop=T), subset(dat.onedosemRNA, naive==0 & ph2.D15.tcell, wt.D15.tcell, drop=T), .5))

corplot(Bpseudoneutid50_BA.1~Day15pseudoneutid50_BA.1, subset(dat.onedosemRNA, naive==0), col=subset(dat.onedosemRNA, naive==0, COVIDIndD22toD181, drop=T)+1, cex=1.2)
abline(h=wtd.quantile(subset(dat.onedosemRNA, naive==0 & ph2.D15.tcell, Bpseudoneutid50_BA.1, drop=T), subset(dat.onedosemRNA, naive==0 & ph2.D15.tcell, wt.D15.tcell, drop=T), .5))
abline(v=wtd.quantile(subset(dat.onedosemRNA, naive==0 & ph2.D15.tcell, Day15pseudoneutid50_BA.1, drop=T), subset(dat.onedosemRNA, naive==0 & ph2.D15.tcell, wt.D15.tcell, drop=T), .5))

corplot(Bcd4_FS_BA.4.5.S~Day15pseudoneutid50_BA.1, subset(dat.onedosemRNA, naive==0), col=subset(dat.onedosemRNA, naive==0, COVIDIndD22toD181, drop=T)+1, cex=2)

```

```{r bivariate models with covariates}

dat.tmp = subset(dat.onedosemRNA, naive==0)

# scale markers
dat.tmp.ph2 = subset(dat.onedosemRNA, naive==0 & ph2.D15.tcell)
dat.tmp$Bcd4_IFNg.IL2_BA.4.5.S = scale(dat.tmp$Bcd4_IFNg.IL2_BA.4.5.S, center=F, scale=sqrt(wtd.var(dat.tmp.ph2$Bcd4_IFNg.IL2_BA.4.5.S, dat.tmp.ph2$wt.D15.tcell)))
dat.tmp$Day15pseudoneutid50_BA.4.BA.5 = scale(dat.tmp$Day15pseudoneutid50_BA.4.BA.5, center=F, scale=sqrt(wtd.var(dat.tmp.ph2$Day15pseudoneutid50_BA.4.BA.5, dat.tmp.ph2$wt.D15.tcell)))
dat.tmp$Bpseudoneutid50_BA.4.BA.5 = scale(dat.tmp$Bpseudoneutid50_BA.4.BA.5, center=F, scale=sqrt(wtd.var(dat.tmp.ph2$Bpseudoneutid50_BA.4.BA.5, dat.tmp.ph2$wt.D15.tcell)))
dat.tmp$Day15cd4_IFNg.IL2_BA.4.5.S = scale(dat.tmp$Day15cd4_IFNg.IL2_BA.4.5.S, center=F, scale=sqrt(wtd.var(dat.tmp.ph2$Day15cd4_IFNg.IL2_BA.4.5.S, dat.tmp.ph2$wt.D15.tcell)))

myprint(sqrt(wtd.var(dat.tmp.ph2$Bcd4_IFNg.IL2_BA.4.5.S, dat.tmp.ph2$wt.D15.tcell)))
myprint(sqrt(wtd.var(dat.tmp.ph2$Day15pseudoneutid50_BA.4.BA.5, dat.tmp.ph2$wt.D15.tcell)))
myprint(sqrt(wtd.var(dat.tmp.ph2$Bpseudoneutid50_BA.4.BA.5, dat.tmp.ph2$wt.D15.tcell)))
myprint(sqrt(wtd.var(dat.tmp.ph2$Day15cd4_IFNg.IL2_BA.4.5.S, dat.tmp.ph2$wt.D15.tcell)))

design=  twophase(id = list( ~ 1,  ~ 1), strata = list(NULL,  ~ Wstratum.tcell), subset =  ~ ph2.D15.tcell, data = dat.tmp)

ff=c("Bcd4_IFNg.IL2_BA.4.5.S  + Day15pseudoneutid50_BA.4.BA.5"
      , "Bcd4_IFNg.IL2_BA.4.5.S+ Bpseudoneutid50_BA.4.BA.5"
      , "Day15cd4_IFNg.IL2_BA.4.5.S + Day15pseudoneutid50_BA.4.BA.5"
      , "Day15cd4_IFNg.IL2_BA.4.5.S + Bpseudoneutid50_BA.4.BA.5"
      )

fits=list(
  svycoxph(f=Surv(COVIDtimeD22toD181, COVIDIndD22toD181) ~ Bcd4_IFNg.IL2_BA.4.5.S     + Day15pseudoneutid50_BA.4.BA.5+ FOIstandardized + standardized_risk_score + strata(stage), design)
,
  svycoxph(f=Surv(COVIDtimeD22toD181, COVIDIndD22toD181) ~ Bcd4_IFNg.IL2_BA.4.5.S     + Bpseudoneutid50_BA.4.BA.5 + FOIstandardized + standardized_risk_score + strata(stage), design)
,
  svycoxph(f=Surv(COVIDtimeD22toD181, COVIDIndD22toD181) ~ Day15cd4_IFNg.IL2_BA.4.5.S + Day15pseudoneutid50_BA.4.BA.5+ FOIstandardized + standardized_risk_score + strata(stage), design)
,
  svycoxph(f=Surv(COVIDtimeD22toD181, COVIDIndD22toD181) ~ Day15cd4_IFNg.IL2_BA.4.5.S + Bpseudoneutid50_BA.4.BA.5+ FOIstandardized + standardized_risk_score + strata(stage), design)

#   svycoxph(f=Surv(COVIDtimeD22toD181, COVIDIndD22toD181) ~ Bcd4_IFNg.IL2_BA.4.5.S + Day15cd4_IFNg.IL2_BA.4.5.S + Bpseudoneutid50_BA.4.BA.5 + Day15pseudoneutid50_BA.4.BA.5+ FOIstandardized + standardized_risk_score + strata(stage), design)
# ,
#   svycoxph(f=Surv(COVIDtimeD22toD181, COVIDIndD22toD181) ~ Bcd4_IFNg.IL2_BA.4.5.S + Day15cd4_IFNg.IL2_BA.4.5.S+ FOIstandardized + standardized_risk_score + strata(stage), design)
# ,
#   svycoxph(f=Surv(COVIDtimeD22toD181, COVIDIndD22toD181) ~ Bpseudoneutid50_BA.4.BA.5 + Day15pseudoneutid50_BA.4.BA.5+ FOIstandardized + standardized_risk_score + strata(stage), design)
# ,
# ,
#   svycoxph(f=Surv(COVIDtimeD22toD181, COVIDIndD22toD181) ~ Bcd4_IFNg.IL2_BA.4.5.S + Day15pseudoneutid50_BA.4.BA.5 + Bcd4_IFNg.IL2_Wuhan.N+ FOIstandardized + standardized_risk_score + strata(stage), design)
# ,
#   svycoxph(f=Surv(COVIDtimeD22toD181, COVIDIndD22toD181) ~ Bcd4_IFNg.IL2_BA.4.5.S + Bcd4_IFNg.IL2_Wuhan.N+ FOIstandardized + standardized_risk_score + strata(stage), design)
)

# per 10 fold
tab1=getFormattedSummary(fits, robust=T, exp=T, type=12); 
tab1[is.na(tab1)]=""
kable(tab1)

# per 3 fold
tab2=getFormattedSummary(fits, robust=T, exp=T, type=12, scale.factor=log10(3)); 
tab2[is.na(tab2)]=""
kable(tab2)

# generalized wald test p values
tab3=getFormattedSummary(fits, robust=T, exp=T, type=13, rows=c(1,2)); tab3

# combine the first row of tab2 and the second row of tab1
tab = t(rbind(tab2[1,], tab1[2,]))
tab=cbind(ff, tab, genWald = drop(tab3))
kable(tab)

```


```{r some markers have low dynamic range}
a="Bcd4_IL4.IL5.IL13.154_BA.4.5.S"
a="Day15cd4_154_BA.4.5.S"
a="Bcd4_FS_Wuhan.N"

dat.onedosemRNA$Bcd4_IL4.IL5.IL13.154_BA.4.5.S_alt = pmax(-1.699, dat.onedosemRNA$Bcd4_IL4.IL5.IL13.154_BA.4.5.S)
dat.onedosemRNA$Day15cd4_IL4.IL5.IL13.154_BA.4.5.S_alt = pmax(-1.699, dat.onedosemRNA$Day15cd4_IL4.IL5.IL13.154_BA.4.5.S)

design=  twophase(id = list( ~ 1,  ~ 1), strata = list(NULL,  ~ Wstratum.tcell), subset =  ~ ph2.D15.tcell, data = subset(dat.onedosemRNA, naive==0))

fit = svycoxph(f=as.formula(glue("Surv(COVIDtimeD22toD91, COVIDIndD22toD91) ~ {a}")), design)
summary(fit)

fit = svycoxph(f=Surv(COVIDtimeD22toD91, COVIDIndD22toD91) ~ Bcd4_IL4.IL5.IL13.154_BA.4.5.S_alt, design)
summary(fit)

fit = svycoxph(f=Surv(COVIDtimeD22toD91, COVIDIndD22toD91) ~ Day15cd4_IL4.IL5.IL13.154_BA.4.5.S_alt, design)
summary(fit)


myboxplot(Bcd4_IL4.IL5.IL13.154_BA.4.5.S_alt~COVIDIndD22toD91, subset(dat.onedosemRNA, naive==0), names=c("non-cases", "cases"))
mytable(subset(dat.onedosemRNA, naive==0, Bcd4_IL4.IL5.IL13.154_BA.4.5.S_alt))
mytable(subset(dat.onedosemRNA, naive==0, Day15cd4_IL4.IL5.IL13.154_BA.4.5.S_alt))


# Naive
a="Bcd4_FS_Wuhan.N"

design=  twophase(id = list( ~ 1,  ~ 1), strata = list(NULL,  ~ Wstratum.tcell), subset =  ~ ph2.D15.tcell, data = subset(dat.onedosemRNA, naive==1))

fit = svycoxph(f=as.formula(glue("Surv(COVIDtimeD22toD91, COVIDIndD22toD91) ~ FOIstandardized + 
    standardized_risk_score + strata(stage) + {a}")), design)
summary(fit)

getFormattedSummary(list(fit), scale.factor=.01, robust=T, exp=T)

myboxplot(Bcd4_FS_Wuhan.N~COVIDIndD22toD91, subset(dat.onedosemRNA, naive==1), names=c("non-cases", "cases"))
mytable(subset(dat.onedosemRNA, naive==0, Bcd4_IL4.IL5.IL13.154_BA.4.5.S_alt))
mytable(subset(dat.onedosemRNA, naive==0, Day15cd4_IL4.IL5.IL13.154_BA.4.5.S_alt))

```

There are no obvious issues with model fitting with Day15cd4_154_BA.4.5.S continuous, which is highly significant, especially after covariates adjustment. The trichotomized version has overall p value 0.089. 
```{r fits}
a="Day15cd4_154_BA.4.5.S" #

design=  twophase(id = list( ~ 1,  ~ 1), strata = list(NULL,  ~ Wstratum.tcell), subset =  ~ ph2.D15.tcell, data = subset(dat.onedosemRNA, naive==0))

hist(subset(dat.onedosemRNA, naive==0)[[a]])

fits = list(
  svycoxph(f=as.formula(glue("Surv(COVIDtimeD22toD91, COVIDIndD22toD91) ~ {a}  ")), design)
,
  svycoxph(f=as.formula(glue("Surv(COVIDtimeD22toD91, COVIDIndD22toD91) ~ {a}   + strata(stage)")), design)
,
  svycoxph(f=as.formula(glue("Surv(COVIDtimeD22toD91, COVIDIndD22toD91) ~ {a}   + FOIstandardized + standardized_risk_score + strata(stage)")), design)

)
for(fit in fits) print(summary(fit))
getFormattedSummary(fits, robust=T, exp=T)
```


```{r fold change}
design=  twophase(id = list( ~ 1,  ~ 1), strata = list(NULL,  ~ Wstratum.tcell), subset =  ~ ph2.D15.tcell, data = subset(dat.onedosemRNA, naive==0))

fits=list(
  svycoxph(f=Surv(COVIDtimeD22toD181, COVIDIndD22toD181) ~ Bcd4_IFNg.IL2_BA.4.5.S  + Day15pseudoneutid50_BA.4.BA.5, design)
,
  svycoxph(f=Surv(COVIDtimeD22toD181, COVIDIndD22toD181) ~ Bcd4_IFNg.IL2_BA.4.5.S + Delta15overBcd4_IFNg.IL2_BA.4.5.S, design)
,
  svycoxph(f=Surv(COVIDtimeD22toD181, COVIDIndD22toD181) ~ Delta15overBcd4_IFNg.IL2_BA.4.5.S, design)
,
  svycoxph(f=Surv(COVIDtimeD22toD181, COVIDIndD22toD181) ~ Bpseudoneutid50_BA.4.BA.5 + Delta15overBpseudoneutid50_BA.4.BA.5, design)
,
  svycoxph(f=Surv(COVIDtimeD22toD181, COVIDIndD22toD181) ~ Delta15overBpseudoneutid50_BA.4.BA.5, design)
)
tab=getFormattedSummary(fits, robust=T, exp=T, type=5); 
tab[is.na(tab)]=""
kable(tab)

```

The following models show that in Bcd4_IFNg.IL2_BA.4.5.S, S1 is mainly responsible.
```{r S1 S2}
design=  twophase(id = list( ~ 1,  ~ 1), strata = list(NULL,  ~ Wstratum.tcell), subset =  ~ ph2.D15.tcell, data = subset(dat.onedosemRNA, naive==0))

fits=list(
  svycoxph(f=Surv(COVIDtimeD22toD181, COVIDIndD22toD181) ~ Bcd4_IFNg.IL2_BA.4.5.S   + Day15pseudoneutid50_BA.4.BA.5, design)
,
  svycoxph(f=Surv(COVIDtimeD22toD181, COVIDIndD22toD181) ~ Bcd4_IFNg.IL2_BA.4.5.S1  + Day15pseudoneutid50_BA.4.BA.5, design)
,
  svycoxph(f=Surv(COVIDtimeD22toD181, COVIDIndD22toD181) ~ Bcd4_IFNg.IL2_BA.4.5.S2  + Day15pseudoneutid50_BA.4.BA.5, design)
)
tab=getFormattedSummary(fits, robust=T, exp=T, type=5); 
tab[is.na(tab)]=""
kable(tab)

```



```{r log transforming FS}
design=  twophase(id = list( ~ 1,  ~ 1), strata = list(NULL,  ~ Wstratum.tcell), subset =  ~ ph2.D15.tcell, data = subset(dat.onedosemRNA, naive==0))

fits=list(
  svycoxph(f=Surv(COVIDtimeD22toD91, COVIDIndD22toD91) ~ log10(Day15cd4_FS_BA.4.5.S) + FOIstandardized + standardized_risk_score + strata(stage), design)
,
  svycoxph(f=Surv(COVIDtimeD22toD91, COVIDIndD22toD91) ~ log10(Bcd4_FS_Wuhan.N) + FOIstandardized + standardized_risk_score + strata(stage), design)
,
  svycoxph(f=Surv(COVIDtimeD22toD91, COVIDIndD22toD91) ~ Bcd4_FS_Wuhan.N + FOIstandardized + standardized_risk_score + strata(stage), design)
)
tab=getFormattedSummary(fits, robust=T, exp=T, type=5); 
tab[is.na(tab)]=""
kable(tab)

```




```{r antilog transforming percentages}
design=  twophase(id = list( ~ 1,  ~ 1), strata = list(NULL,  ~ Wstratum.tcell), subset =  ~ ph2.D15.tcell, data = subset(dat.onedosemRNA, naive==0))

fits=list(
  svycoxph(f=Surv(COVIDtimeD22toD91, COVIDIndD22toD91) ~ I(10^(Day15cd4_IFNg.IL2_BA.4.5.S)) + FOIstandardized + standardized_risk_score + strata(stage), design)
,
  svycoxph(f=Surv(COVIDtimeD22toD91, COVIDIndD22toD91) ~ Day15cd4_IFNg.IL2_BA.4.5.S + FOIstandardized + standardized_risk_score + strata(stage), design)
)
tab=getFormattedSummary(fits, robust=T, exp=T, type=5); 
tab[is.na(tab)]=""
kable(tab)

```