---
title: "PREVENT-19 Stage 1 Correlates for NVX IgG and ACE2 Assays"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(survey)
library(kyotil)
library(readxl)

dat_mapped=read.csv('/trials/covpn/p3004/analysis/mapping_immune_correlates/stage1/adata/COVID_Novavax_realdata_20240313.csv')
dat_mapped$EarlyendpointD35 <- with(dat_mapped, EarlyinfectionD35==1 | (EventIndPrimaryD1==1 & EventTimePrimaryD1 < NumberdaysD1toD35 + 7),1,0)
dat_mapped$ph1.D35 = with(dat_mapped, EarlyendpointD35==0 & Perprotocol==1 & EventTimePrimaryD35 >= 7)

dat_proc=read.csv('/trials/covpn/p3004/analysis/correlates/Part_A_Blinded_Phase_Data/adata/prevent19_data_processed_20240316.csv')

dat_raw=read_excel('/trials/covpn/p3004/download_data/formatted_for_fred_hutch.xlsx')
```


## Data descriptive

This dataset adds two NVX assays to the stage 1 dataset and contains both vaccine and placebo arms and seroneg/seropos.
```{r, include=F}
mytable(dat_mapped$Trt)
mytable(dat_mapped$Bserostatus)
mytable(dat_mapped$Country)
```

A decision is made to use the same clinical database that was used in the original correlates paper, and not use the updated clinical database. The updated database includes some late changes, e.g. US147-0424 is a case in the new database. For the stage 2 study, we will use the updated clinical database. 

There are 1750 subjects with NVX IgG, of which 1710 belong to the original Stage 1 dataset. 
```{r}
mytable(!is.na(dat_raw[,"IGG Day 35"]))
sum(("2019nCoV301-"%.%dat_raw[,1,drop=T]) %in% dat_mapped$Subjectid)
with(subset(dat_mapped, ph1.D35 & Trt==1 & Bserostatus==0 & Country==0), mytable(!is.na(Day35ACE2), !is.na(Day35bindNVXIgG), EventIndPrimaryD1))
```

NVX ACE2 was measured on 1708 out of the 1710 subjects with NVX IgG. We will define ph2 as requiring both IgG and ACE2.
```{r}
with(subset(dat_mapped, ph1.D35 & Trt==1 & Bserostatus==0 & Country==0), mytable(!is.na(Day35ACE2), !is.na(Day35bindNVXIgG), EventIndPrimaryD1))
```

There are 15 cases in the vaccine arm, US, baseline negative, 12 out of which are in ph1.D35 and have both bindSpike and bindNVXIgG. For the non-cases, 186 from the subcohort have bindNVXIgG, but 1462 outside the subcohort have bindNVXIgG. 
```{r}
with(subset(dat_proc, ph1.D35 & Trt==1 & Bserostatus==0 & Country==0), mytable(!is.na(Day35bindSpike), !is.na(Day35ACE2), EventIndPrimaryD1))
```
Because the sampling for bindNVXIgG factors in the strata for the subcohort sampling, we will use 1648 non-cases and compute weights 
```{r}
with(subset(dat_proc, ph1.D35 & Trt==1 & Country==0 & Bserostatus==0), mytable(ph2.D35NVX, Wstratum))
```


## Assay data

Correlation between USG bindSpike and NVX IgG and ACE2. The two NVX assays are more highly correlated. 
```{r}
with(subset(dat_mapped, ph1.D35 & Trt==1), mypairs(cbind(Day35bindSpike, Day35bindNVXIgG, Day35ACE2)))
```

The scatterplot shows that the bindNVXIgG readout has some outliers. We define the outliers to be the red dots based on the scatterplot between bindNVXIgG and ACE2. No outliers are cases. The green dots are not defined as outliers although they show larger discrepancy between bindNVXIgG and bindSpike.

```{r}
# use this version to get dat for outliers study
dat_proc1=read.csv('/trials/covpn/p3004/analysis/correlates/Part_A_Blinded_Phase_Data/adata/prevent19_data_processed_20240313.csv')
dat=subset(dat_proc1, ph1.D35 & Trt==1 & Bserostatus==0 & Country==0) 


outliers1 = subset(dat, Day35bindNVXIgG-Day35ACE2 < 1.8 & Day35ACE2 > 2 & Day35bindNVXIgG > 3, Ptid, drop=T)
outliers2 = subset(dat, Day35bindNVXIgG-Day35bindSpike < .9, Ptid, drop=T)
any(subset(dat, EventIndPrimaryD35==1, Ptid, drop=T) %in% outliers1)

col=ifelse(dat$Ptid %in% outliers1, 2, 1)
col[dat$Ptid %in% outliers2 & col==1]=3

par(mfrow=c(1,2))
corplot(Day35bindNVXIgG~Day35ACE2, dat, col=col, asp=1)
abline(1.8,1, lty=2)
# abline(h=log10(500))

corplot(Day35bindNVXIgG~Day35bindSpike, dat, col=col, asp=1)
abline(1,1, lty=2)

```

The list of outliers
```{r}
outliers1
```

List of newly tested ptids are highlighted in red below.
```{r}
stratum7 = "2019nCoV301-"%.%c("US005-0247","US013-0005","US013-0051","US018-0022","US027-0191","US039-0294","US039-0381","US049-0037","US081-0007","US081-0050","US097-0030","US097-0034","US097-0042","US097-0127","US098-0067","US098-0084","US106-0027","US134-0011","US135-0068","US135-0229","US139-0041","US142-0036","US143-0039","US143-0081","US143-0102","US143-0513","US143-0518","US143-0585","US144-0051","US147-0145","US147-0163","US147-0275","US147-0344","US152-0176","US152-0337","US154-0100","US154-0209","US156-0093","US157-0048","US160-0192","US160-0239","US160-0275","US160-0382","US160-0392","US160-0436","US160-0525","US161-0306","US162-0187","US170-0064","US176-0014","US178-0161","US179-0057","US179-0332","US179-0382","US180-0004","US180-0227","US187-0007","US189-0040","US191-0162","US191-0301","US191-0334","US191-0366","US194-0284","US195-0053","US196-0057","US203-0065","US204-0100","US204-0127","US206-0203","US206-0260","US207-0292","US208-0029","US213-0007","US213-0080","US215-0003","US215-0081","US215-0142","US215-0160","US215-0175","US217-0160","US219-0056","US225-0013","US228-0018","US228-0113","US228-0182","US228-0183","US230-0014","US230-0046","US230-0054","US232-0001","US232-0004","US235-0031","US235-0062","US236-0062","US239-0036","US239-0177","US239-0316","US242-0004","US243-0020","US249-0089")
stratum8 = "2019nCoV301-"%.%c("US005-0018","US005-0272","US039-0004","US039-0081","US047-0105","US049-0219","US060-0015","US060-0138","US081-0042","US097-0009","US097-0021","US097-0031","US097-0040","US104-0092","US134-0084","US135-0010","US135-0158","US142-0018","US142-0021","US142-0041","US142-0060","US142-0064","US142-0117","US143-0233","US146-0107","US147-0266","US152-0183","US154-0020","US154-0123","US154-0222","US156-0002","US156-0013","US156-0145","US157-0045","US160-0037","US160-0085","US160-0477","US160-0506","US160-0555","US161-0272","US162-0247","US163-0039","US163-0041","US164-0113","US166-0010","US168-0348","US172-0008","US172-0031","US176-0006","US176-0027","US176-0028","US176-0034","US178-0252","US179-0068","US188-0053","US191-0048","US191-0099","US191-0144","US191-0246","US194-0170","US194-0219","US196-0378","US203-0016","US203-0039","US204-0027","US204-0103","US204-0138","US205-0131","US205-0145","US206-0286","US208-0247","US211-0005","US211-0008","US211-0063","US215-0026","US215-0027","US215-0109","US215-0112","US215-0218","US217-0074","US217-0143","US217-0266","US218-0017","US219-0060","US225-0030","US231-0148","US232-0026","US232-0208","US232-0245","US232-0305","US239-0078","US239-0242","US239-0251","US239-0309","US240-0061","US242-0027","US242-0040","US244-0039","US245-0078","US245-0116")

col=ifelse(dat$Ptid %in% c(stratum7, stratum8), 2, 1)

par(mfrow=c(1,2))
corplot(Day35bindNVXIgG~Day35ACE2, dat, col=col, ylim=c(1.9,6))
abline(1.8,1, lty=2)

corplot(Day35bindNVXIgG~Day35bindSpike, dat, col=col, ylim=c(1.9,6))
abline(1,1, lty=2)

```


The smallest value of NVX IgG is 100, consistent with LLOQ being 200. The unit EU (ELISA Unit), which can be divided by 22 to get IU. Pos.cutoff is set to 500 according to Iksung, ULOQ is set to 2,904,275 EU/mL.
```{r}
10**(sort(dat_mapped$Day35bindNVXIgG)[1:20])
```


The smallest value of NVX IgG is 5, consistent with LOD being 10. The scatterplot between ACE2 and ELISA suggests that ACE2 may be more specific at the low end of the readout.
```{r}
10**(sort(dat_mapped$Day35ACE2)[1:100])
```

Correlation plot between baseline and D35 marker. Without placebo, it is hard to tell the range of non-specific binding. 
```{r}
par(mfrow=c(1,2))
lim=range(dat_mapped$Day35ACE2, na.rm=T)
corplot(Day35ACE2~BACE2, dat_mapped[dat_mapped$Trt==1,], xlim=lim, asp=1, main="ACE2, Vacc")
lim=range(dat_mapped$Day35bindNVXIgG, na.rm=T)
corplot(Day35bindNVXIgG~BbindNVXIgG, dat_mapped[dat_mapped$Trt==1,], xlim=lim, asp=1, main="IgG, Vacc")
```

Distributions of sampling weights shows that for the USG markers, stratum 27 and 28 (7 and 8) have weights 2.0 and 2.7, respectively. For the NVX markers, if we exclude the latest batch that contains the outliers, the weights rise to 4.3 and 4.2, respectively. 
```{r}
with (subset(dat_proc, ph1.D35==1 & Trt==1 & Bserostatus==0 & Country==0), table(wt.D35, Wstratum))
with (subset(dat_proc, ph1.D35==1 & Trt==1 & Bserostatus==0 & Country==0), table(wt.D35NVX, Wstratum))
```

