---
output:
  pdf_document: default
  html_document: default
  
---
# Graphical Description of Immunogenicity Data {#immuno-graphical}

```{r immuno-graphical-setup, echo = FALSE, message = FALSE, include=FALSE}
library(here)
library(latex2exp)
library(knitr)

here::i_am("immuno_graphical/report.Rmd")

all_assays <- c("bindSpike", "bindSpike_B.1.1.7", "bindSpike_B.1.351", "bindSpike_P.1", 
                "bindRBD", "bindRBD_B.1.1.7", "bindRBD_B.1.351", "bindRBD_P.1", 
                "bindN",
                "pseudoneutid50", "pseudoneutid80", 
                "liveneutmn50",
                "ADCP")

if(include_bindN && grepl("bind", assays) && !grepl("bindN", assays) && !grepl("janssen_.+partA.*", attr(config,"config"))){
  assay_immuno <- all_assays[all_assays %in% c(assays, "bindN")]
  labels.assays.all <- c("Binding Antibody to N", labels.assays)
  names(labels.assays.all)[1] <- "bindN"
  labels.assays <- labels.assays.all[assay_immuno]
} else {
  assay_immuno <- assays
}
```

```{r immuno-graphical-caption-setup, echo = FALSE, message = FALSE, include=FALSE}

is.ensemble <- study_name=="ENSEMBLE" | study_name=="MockENSEMBLE" # only ENSEMBLE has by country and by HIV group figures

config <- config::get(config = Sys.getenv("TRIAL"))
if.pair <- ifelse(length(config$assays)>1, 1, 0)
if.pos.exist <- 1#ifelse(study_name=="AZD1222", 0, 1)

minority.disclaimer <- switch(study_name, 
                              "COVE"="",
                              "MockCOVE"="",
                              "ENSEMBLE"="These plots are restricted to only United States trial participants.",
                              "MockENSEMBLE"="These plots are restricted to only United States trial participants.",
                              "PREVENT19"="",
                              "AZD1222"="",
                              "VAT08m"="",
                              "PROFISCOV"="")

neut.marker.captions <- switch(study_name, 
                               "COVE"="The dashed lines in each figure are ULOQ, LLOQ, and positivity cutoffs for binding antibody assays, or ULOQ, LLOQ, and LLOD for neutralizing antibody assays, from top to bottom respectively.",
                               "MockCOVE"="The dashed lines in each figure are ULOQ, LLOQ, and positivity cutoffs for binding antibody assays, or ULOQ, LLOQ, and LLOD for neutralizing antibody assays, from top to bottom respectively.",
                               "ENSEMBLE"="The dashed lines in each figure are ULOQ and positivity cut-off from top to bottom for binding antibody assays, or ULOQ and LLOQ for neutralizing antibody assays, from top to bottom respectively.",
                               "MockENSEMBLE"="The dashed lines in each figure are ULOQ and positivity cut-off for binding antibody assays, or ULOQ and LLOQ for neutralizing antibody assays, from top to bottom respectively.",
                               "PREVENT19"="The dashed lines in each figure are ULOQ, positivity cut-off and LLOQ for binding antibody assays, or ULOQ and LLOD for neutralizing antibody assays, from top to bottom respectively.",
                               
                               "AZD1222"="The dashed lines in each figure are ULOQ, positivity cut-off and LLOQ for binding antibody assays, or ULOQ and LLOD for neutralizing antibody assays, from top to bottom respectively.",
                               
                               "VAT08m"="The dashed lines in each figure is LLOD for neutralizing antibody assays.",
                               "PROFISCOV"="The dashed lines in each figure are ULOQ, positivity cut-off and LLOD for binding antibody assays, or LLOD/positivity cut-off for neutralizing antibody assays, from top to bottom respectively."
                               # PROFISCOV nAb has a ULOQ value out of figure limit
                               )

```

## Pairs plots of antibody markers for overall per-protocal cohort

### Baseline SARS-CoV-2 Negative

```{r, echo=FALSE, results='asis'}

bsero="BaselineNeg" # bsero in c("BaselineNeg","BaselinePos")[1:(if.pos.exist+1)]
bseroLabel <- ifelse(bsero=="BaselineNeg", "negative", "positive")

trt="vaccine"
  
for (country in c("Nvx_US_Mex", if(study_name=="PREVENT19") "Nvx_US")){
  # only doable when there are >1 assays
  if (if.pair==1){
    
    for(tp in times[!times %in% c(paste0("Delta",timepoints[length(timepoints)],"over",timepoints[1]))]) {
      
      tpLabel <- gsub("ay ", "", labels.time[tp])
      
      res = knitr::knit_child(c(here::here('immuno_graphical', 'report_pair_by_time.Rmd')), quiet = TRUE)
      cat(res, sep = '\n')
      cat("\\clearpage", sep = '\n')
    }
  }
      
  for (asy in assay_immuno){
    
    asyLabel <- gsub("%","\\\\%", labels.assays[asy])
    
    res = knitr::knit_child(c(here::here('immuno_graphical', 'report_pair_by_assay.Rmd')), quiet = TRUE)
    cat(res, sep = '\n')
    cat("\\clearpage", sep = '\n')
  }
  
}
```

### Baseline SARS-CoV-2 Positive

```{r, echo=FALSE, results='asis', eval = if.pos.exist==1}

bsero="BaselinePos"
bseroLabel <- ifelse(bsero=="BaselineNeg", "negative", "positive")

trt="vaccine"
  
for (country in c("Nvx_US_Mex", if(study_name=="PREVENT19") "Nvx_US")){
  
  # only doable when there are >1 assays
  if (if.pair==1){
      
    for(tp in times[!times %in% c(paste0("Delta",timepoints[length(timepoints)],"over",timepoints[1]))]) {
      
      tpLabel <- gsub("ay ", "", labels.time[tp])
      
      res = knitr::knit_child(c(here::here('immuno_graphical', 'report_pair_by_time.Rmd')), quiet = TRUE)
      cat(res, sep = '\n')
      cat("\\clearpage", sep = '\n')
    }
  }

  for (asy in assay_immuno){
    
    asyLabel <- gsub("%","\\\\%", labels.assays[asy])
    
    res = knitr::knit_child(c(here::here('immuno_graphical', 'report_pair_by_assay.Rmd')), quiet = TRUE)
    cat(res, sep = '\n')
    cat("\\clearpage", sep = '\n')
    
  }
}
```

### Baseline SARS-CoV-2 Positive Placebo Arm

```{r, echo=FALSE, results='asis', eval = if.pos.exist==1}

bsero="BaselinePos"
bseroLabel <- ifelse(bsero=="BaselineNeg", "negative", "positive")

trt="placebo"
  
for (country in c("Nvx_US_Mex", if(study_name=="PREVENT19") "Nvx_US")){
  
  # only doable when there are >1 assays
  if (if.pair==1){
    
    for(tp in times[!times %in% c(paste0("Delta",timepoints[length(timepoints)],"over",timepoints[1]))]) {
      
      tpLabel <- gsub("ay ", "", labels.time[tp])
      
      res = knitr::knit_child(c(here::here('immuno_graphical', 'report_pair_by_time.Rmd')), quiet = TRUE)
      cat(res, sep = '\n')
      cat("\\clearpage", sep = '\n')
    }
    
  }
  
  for (asy in assay_immuno){
    
    asyLabel <- gsub("%","\\\\%", labels.assays[asy])
    
    res = knitr::knit_child(c(here::here('immuno_graphical', 'report_pair_by_assay.Rmd')), quiet = TRUE)
    cat(res, sep = '\n')
    cat("\\clearpage", sep = '\n')
  }
    
}
```

## RCDF plots of antibody markers for overall per-protocol cohort
```{r, echo=FALSE, results='asis'}
  
for (trt in c("trt_both", "trt_vaccine")){
  trtLabel <- ifelse(trt=="trt_both", "x randomization arm", "vaccine arm")
  
  for (bsero in c("bstatus_both", "bstatus_Neg", "bstatus_Pos")){
    if (bsero=="bstatus_Pos" & if.pos.exist==0) next
    if (trt=="trt_both" & bsero!="bstatus_both") next # trt_both is only for bstatus both
    
    bseroLabel <- ifelse(bsero=="bstatus_both", "by baseline status", ifelse(bsero=="bstatus_Neg", "baseline negative", "baseline positive"))
    
    for(tp in times[!times %in% c("B",paste0("Delta",timepoints[length(timepoints)],"over",timepoints[1]))]) {
            
      tpLabel <- gsub("ay ", "", labels.time[tp])
      
      for (asy in c("","bAb","nAb","other")){
        if ( (sum(grepl("bind", assays))==0 & asy=="bAb") | (sum(grepl("neut", assays))==0 & asy=="nAb") | (sum(grepl("ADCP", assays))==0 & asy=="other")) next
        if (asy=="" & (trt!="trt_both" | bsero!="bstatus_both")) next  # trt_both & bstatus_both are only for all assays
        if (asy!="" & trt=="trt_both" & bsero=="bstatus_both") next  # trt_both & bstatus_both are only for all assays
        
        res = knitr::knit_child(c(here::here('immuno_graphical', 'report_rcdf.Rmd')), quiet = TRUE)
        cat(res, sep = '\n')
        cat("\\clearpage", sep = '\n')
      }
    }
  }
}
```

\clearpage
## Scatter plots of antibody markers versus age for overall per-protocol cohort

### Baseline SARS-CoV-2 Negative

```{r, echo=FALSE, results='asis'}

bsero="BaselineNeg" # bsero in c("BaselineNeg","BaselinePos")[1:(if.pos.exist+1)]
bseroLabel <- ifelse(bsero=="BaselineNeg", "negative", "positive")

trt="Vaccine"
trtLabel="vaccine"
  
for(tp in times[!grepl("Delta", times)]) {
  
  tpLabel <- gsub("ay ", "", labels.time[tp])
  
  res = knitr::knit_child(c(here::here('immuno_graphical', 'report_scatter.Rmd')), quiet = TRUE)
  cat(res, sep = '\n')
  cat("\\clearpage", sep = '\n')
}
    
```

### Baseline SARS-CoV-2 Positive

```{r, echo=FALSE, results='asis', eval = if.pos.exist==1}
 
bsero="BaselinePos" # bsero in c("BaselineNeg","BaselinePos")[1:(if.pos.exist+1)]
bseroLabel <- ifelse(bsero=="BaselineNeg", "negative", "positive")

trt="Vaccine"
trtLabel="vaccine"

if (if.pos.exist==1) {  
  for(tp in times[!grepl("Delta", times)]) {
    
    tpLabel <- gsub("ay ", "", labels.time[tp])
    
    res = knitr::knit_child(c(here::here('immuno_graphical', 'report_scatter.Rmd')), quiet = TRUE)
    cat(res, sep = '\n')
    cat("\\clearpage", sep = '\n')
  }
}
    
```

### Baseline SARS-CoV-2 Positive Placebo Arm

```{r, echo=FALSE, results='asis', eval = if.pos.exist==1}

bsero="BaselinePos" # bsero in c("BaselineNeg","BaselinePos")[1:(if.pos.exist+1)]
bseroLabel <- ifelse(bsero=="BaselineNeg", "negative", "positive")

trt="Placebo"
trtLabel="placebo"

if (if.pos.exist==1) {  
  for(tp in times[!grepl("Delta", times)]) {
    
    tpLabel <- gsub("ay ", "", labels.time[tp])
    
    res = knitr::knit_child(c(here::here('immuno_graphical', 'report_scatter.Rmd')), quiet = TRUE)
    cat(res, sep = '\n')
    cat("\\clearpage", sep = '\n')
  }
}
    
```

### Baseline SARS-CoV-2 Negative Placebo Arm

```{r, echo=FALSE, results='asis'}

bsero="BaselineNeg" # bsero in c("BaselineNeg","BaselinePos")[1:(if.pos.exist+1)]
bseroLabel <- ifelse(bsero=="BaselineNeg", "negative", "positive")

trt="Placebo"
trtLabel="placebo"

for(tp in times[!grepl("Delta", times)]) {
  
  tpLabel <- gsub("ay ", "", labels.time[tp])
  
  res = knitr::knit_child(c(here::here('immuno_graphical', 'report_scatter.Rmd')), quiet = TRUE)
  cat(res, sep = '\n')
  cat("\\clearpage", sep = '\n')
}
    
```

\clearpage
## Box plots of antibody markers for overall per-protocol cohort

### Baseline SARS-CoV-2 Negative

```{r, echo=FALSE, results='asis'}

bsero="BaselineNeg" # bsero in c("BaselineNeg","BaselinePos")[1:(if.pos.exist+1)]
bseroLabel <- ifelse(bsero=="BaselineNeg", "negative", "positive")
  
for(tp in times[!times %in% c(paste0("Delta",timepoints[length(timepoints)],"over",timepoints[1]))]) {
  
  tpLabel <- gsub("ay ", "", labels.time[tp])
  
  res = knitr::knit_child(c(here::here('immuno_graphical', 'report_box.Rmd')), quiet = TRUE)
  cat(res, sep = '\n')
  cat("\\clearpage", sep = '\n')
}
    
```

### Baseline SARS-CoV-2 Positive

```{r, echo=FALSE, results='asis', eval = if.pos.exist==1}

bsero="BaselinePos" # bsero in c("BaselineNeg","BaselinePos")[1:(if.pos.exist+1)]
bseroLabel <- ifelse(bsero=="BaselineNeg", "negative", "positive")

for(tp in times[!times %in% c(paste0("Delta",timepoints[length(timepoints)],"over",timepoints[1]))]) {
  
  tpLabel <- gsub("ay ", "", labels.time[tp])
  
  res = knitr::knit_child(c(here::here('immuno_graphical', 'report_box.Rmd')), quiet = TRUE)
  cat(res, sep = '\n')
  cat("\\clearpage", sep = '\n')
}
    
```

### Baseline negative vs. positive vaccine recipients

```{r, echo=FALSE, results='asis'}

trt="vaccine"
  
for(tp in times[!times %in% c(paste0("Delta",timepoints[length(timepoints)],"over",timepoints[1]))]) {
  
  tpLabel <- gsub("ay ", "", labels.time[tp])
  
  res = knitr::knit_child(c(here::here('immuno_graphical', 'report_box_neg_vs_pos.Rmd')), quiet = TRUE)
  cat(res, sep = '\n')
  cat("\\clearpage", sep = '\n')
}
    
```

### Baseline negative vs. positive placebo recipients

```{r, echo=FALSE, results='asis'}

trt="placebo"
  
for(tp in times[!times %in% c(paste0("Delta",timepoints[length(timepoints)],"over",timepoints[1]))]) {
  
  tpLabel <- gsub("ay ", "", labels.time[tp])
  
  res = knitr::knit_child(c(here::here('immuno_graphical', 'report_box_neg_vs_pos.Rmd')), quiet = TRUE)
  cat(res, sep = '\n')
  cat("\\clearpage", sep = '\n')
}
    
```

\clearpage
## Spaghetti plots of antibody markers over time for overall per-protocol cohort

### Baseline SARS-CoV-2 Negative

```{r, fig.cap = paste0("Spaghetti plots of Ab markers over time: baseline negative vaccine + placebo arm"), eval = any(c("B", paste0("Day",timepoints[1]), "Day57") %in% times)}
include_graphics(here(
  "immuno_graphical", "output", attr(config,"config"), 
  paste0("spaghetti_plot_BaselineNeg_", study_name, ".pdf")
))
```

\clearpage
### Baseline SARS-CoV-2 Positive

```{r, fig.cap = paste0("Spaghetti plots of Ab markers over time: baseline positive vaccine + placebo arm"), eval = any(c("B", paste0("Day",timepoints[1]), "Day57") %in% times & if.pos.exist==1)}
include_graphics(here(
  "immuno_graphical", "output", attr(config,"config"),
  paste0("spaghetti_plot_BaselinePos_", study_name, ".pdf")
))
```

\clearpage
## RCDF plots of antibody markers by demographics for per-protocol cohort

### Baseline SARS-CoV-2 Negative

```{r, echo=FALSE, results='asis'}

bsero="BaselineNeg" # bsero in c("BaselineNeg","BaselinePos")[1:(if.pos.exist+1)]
bseroLabel <- ifelse(bsero=="BaselineNeg", "negative", "positive")

trt="Vaccine"
trtLabel="vaccine"

if_no_minority = attr(config,"config") %in% c("janssen_la_partA","janssen_sa_partA",
                                       "janssen_la_partAsenior","janssen_la_partAnonsenior",
                                       "janssen_sa_partAnonsenior")
demos <- c("age_group","risk_group","age_risk_group","sex_group","age_sex_group","ethnicity","race",if(!if_no_minority)c("minority_group","age_minority_group"),if(study_name=="ENSEMBLE")"country", if(study_name=="ENSEMBLE")"hiv_group")

demoLabels <- c("age groups","high-risk condition","age and high-risk condition","sex assigned at birth","age and sex assgined at birth","ethnicity","race",if(!if_no_minority)c("dichotomous classification of
race and ethnic group","age and dichotomous classification of
race and ethnic group"),if(study_name=="ENSEMBLE")"country of residence", if(study_name=="ENSEMBLE")"HIV
positivity")
names(demoLabels) <- demos
  
for (dm in demos){
  for(tp in times[!times %in% c("B",paste0("Delta",timepoints[length(timepoints)],"over",timepoints[1]))]) {
    
    tpLabel <- gsub("ay ", "", labels.time[tp])
    dmLabel <- demoLabels[dm]
    
    res = knitr::knit_child(c(here::here('immuno_graphical', 'report_rcdf_demographic.Rmd')), quiet = TRUE)
    cat(res, sep = '\n')
    cat("\\clearpage", sep = '\n')
  }
}
    
```

### Baseline SARS-CoV-2 Positive

```{r, echo=FALSE, results='asis', eval = if.pos.exist==1}

bsero="BaselinePos" # bsero in c("BaselineNeg","BaselinePos")[1:(if.pos.exist+1)]
bseroLabel <- ifelse(bsero=="BaselineNeg", "negative", "positive")

trt="Vaccine"
trtLabel="vaccine"

if_no_minority = attr(config,"config") %in% c("janssen_la_partA","janssen_sa_partA",
                                       "janssen_la_partAsenior","janssen_la_partAnonsenior",
                                       "janssen_sa_partAnonsenior")
demos <- c("age_group","risk_group","age_risk_group","sex_group","age_sex_group","ethnicity","race",if(!if_no_minority)c("minority_group","age_minority_group"),if(study_name=="ENSEMBLE")"country", if(study_name=="ENSEMBLE")"hiv_group")

demoLabels <- c("age groups","high-risk condition","age and high-risk condition","sex assigned at birth","age and sex assgined at birth","ethnicity","race",if(!if_no_minority)c("dichotomous classification of
race and ethnic group","age and dichotomous classification of
race and ethnic group"),if(study_name=="ENSEMBLE")"country of residence", if(study_name=="ENSEMBLE")"HIV
positivity")
names(demoLabels) <- demos
  
for (dm in demos){
  for(tp in times[!times %in% c("B",paste0("Delta",timepoints[length(timepoints)],"over",timepoints[1]))]) {
    
    tpLabel <- gsub("ay ", "", labels.time[tp])
    dmLabel <- demoLabels[dm]
    
    res = knitr::knit_child(c(here::here('immuno_graphical', 'report_rcdf_demographic.Rmd')), quiet = TRUE)
    cat(res, sep = '\n')
    cat("\\clearpage", sep = '\n')
  }
}
    
```

### Baseline SARS-CoV-2 Positive Placebo Arm

```{r, echo=FALSE, results='asis', eval = if.pos.exist==1}

bsero="BaselinePos" # bsero in c("BaselineNeg","BaselinePos")[1:(if.pos.exist+1)]
bseroLabel <- ifelse(bsero=="BaselineNeg", "negative", "positive")

trt="Placebo"
trtLabel="placebo"

if_no_minority = attr(config,"config") %in% c("janssen_la_partA","janssen_sa_partA",
                                       "janssen_la_partAsenior","janssen_la_partAnonsenior",
                                       "janssen_sa_partAnonsenior")
demos <- c("age_group","risk_group","age_risk_group","sex_group","age_sex_group","ethnicity","race",if(!if_no_minority)c("minority_group","age_minority_group"),if(study_name=="ENSEMBLE")"country", if(study_name=="ENSEMBLE")"hiv_group")

demoLabels <- c("age groups","high-risk condition","age and high-risk condition","sex assigned at birth","age and sex assgined at birth","ethnicity","race",if(!if_no_minority)c("dichotomous classification of
race and ethnic group","age and dichotomous classification of
race and ethnic group"),if(study_name=="ENSEMBLE")"country of residence", if(study_name=="ENSEMBLE")"HIV
positivity")
names(demoLabels) <- demos

for (dm in demos){
  for(tp in times[!times %in% c("B",paste0("Delta",timepoints[length(timepoints)],"over",timepoints[1]))]) {
    
    tpLabel <- gsub("ay ", "", labels.time[tp])
    dmLabel <- demoLabels[dm]
    
    res = knitr::knit_child(c(here::here('immuno_graphical', 'report_rcdf_demographic.Rmd')), quiet = TRUE)
    cat(res, sep = '\n')
    cat("\\clearpage", sep = '\n')
  }
}
    
```


\clearpage
## Boxplots of antibody markers by demographics for per-protocol cohort

### Baseline SARS-CoV-2 Negative

```{r, echo=FALSE, results='asis'}

bsero="BaselineNeg" # bsero in c("BaselineNeg","BaselinePos")[1:(if.pos.exist+1)]
bseroLabel <- ifelse(bsero=="BaselineNeg", "negative", "positive")

trt="Vaccine"
trtLabel="vaccine"

if_no_minority = attr(config,"config") %in% c("janssen_la_partA","janssen_sa_partA",
                                       "janssen_la_partAsenior","janssen_la_partAnonsenior",
                                       "janssen_sa_partAnonsenior")
demos <- c("age_group","risk_group","age_x_risk_group","sex","age_x_sex_group","ethnicity","race",if(!if_no_minority)c("minority_group","age_x_minority"),if(study_name=="ENSEMBLE")"country", if(study_name=="ENSEMBLE")"hiv_group")

demoLabels <- c("age groups","high-risk condition","age and high-risk condition","sex assigned at birth","age and sex assgined at birth","ethnicity","race",if(!if_no_minority)c("dichotomous classification of
race and ethnic group","age and dichotomous classification of
race and ethnic group"),if(study_name=="ENSEMBLE")"country of residence", if(study_name=="ENSEMBLE")"HIV
positivity")
names(demoLabels) <- demos
  
for (dm in demos){
  for(tp in times[!times %in% c("B",paste0("Delta",timepoints[length(timepoints)],"over",timepoints[1]))]) {
    
    tpLabel <- gsub("ay ", "", labels.time[tp])
    dmLabel <- demoLabels[dm]
    
    res = knitr::knit_child(c(here::here('immuno_graphical', 'report_box_demographic.Rmd')), quiet = TRUE)
    cat(res, sep = '\n')
    cat("\\clearpage", sep = '\n')
  }
}
    
```

### Baseline SARS-CoV-2 Positive

```{r, echo=FALSE, results='asis', eval = if.pos.exist==1}

bsero="BaselinePos" # bsero in c("BaselineNeg","BaselinePos")[1:(if.pos.exist+1)]
bseroLabel <- ifelse(bsero=="BaselineNeg", "negative", "positive")

trt="Vaccine"
trtLabel="vaccine"

if_no_minority = attr(config,"config") %in% c("janssen_la_partA","janssen_sa_partA",
                                       "janssen_la_partAsenior","janssen_la_partAnonsenior",
                                       "janssen_sa_partAnonsenior")
demos <- c("age_group","risk_group","age_x_risk_group","sex","age_x_sex_group","ethnicity","race",if(!if_no_minority)c("minority_group","age_x_minority"),if(study_name=="ENSEMBLE")"country", if(study_name=="ENSEMBLE")"hiv_group")

demoLabels <- c("age groups","high-risk condition","age and high-risk condition","sex assigned at birth","age and sex assgined at birth","ethnicity","race",if(!if_no_minority)c("dichotomous classification of
race and ethnic group","age and dichotomous classification of
race and ethnic group"),if(study_name=="ENSEMBLE")"country of residence", if(study_name=="ENSEMBLE")"HIV
positivity")
names(demoLabels) <- demos
  
for (dm in demos){
  for(tp in times[!times %in% c("B",paste0("Delta",timepoints[length(timepoints)],"over",timepoints[1]))]) {
    
    tpLabel <- gsub("ay ", "", labels.time[tp])
    dmLabel <- demoLabels[dm]
    
    res = knitr::knit_child(c(here::here('immuno_graphical', 'report_box_demographic.Rmd')), quiet = TRUE)
    cat(res, sep = '\n')
    cat("\\clearpage", sep = '\n')
  }
}
    
```

\clearpage
### Baseline SARS-CoV-2 Positive Placebo Arm

```{r, echo=FALSE, results='asis', eval = if.pos.exist==1}

bsero="BaselinePos" # bsero in c("BaselineNeg","BaselinePos")[1:(if.pos.exist+1)]
bseroLabel <- ifelse(bsero=="BaselineNeg", "negative", "positive")

trt="Placebo"
trtLabel="placebo"

if_no_minority = attr(config,"config") %in% c("janssen_la_partA","janssen_sa_partA",
                                       "janssen_la_partAsenior","janssen_la_partAnonsenior",
                                       "janssen_sa_partAnonsenior")
demos <- c("age_group","risk_group","age_x_risk_group","sex","age_x_sex_group","ethnicity","race",if(!if_no_minority)c("minority_group","age_x_minority"),if(study_name=="ENSEMBLE")"country", if(study_name=="ENSEMBLE")"hiv_group")

demoLabels <- c("age groups","high-risk condition","age and high-risk condition","sex assigned at birth","age and sex assgined at birth","ethnicity","race",if(!if_no_minority)c("dichotomous classification of
race and ethnic group","age and dichotomous classification of
race and ethnic group"),if(study_name=="ENSEMBLE")"country of residence", if(study_name=="ENSEMBLE")"HIV
positivity")
names(demoLabels) <- demos
  
for (dm in demos){
  for(tp in times[!times %in% c("B",paste0("Delta",timepoints[length(timepoints)],"over",timepoints[1]))]) {
    
    tpLabel <- gsub("ay ", "", labels.time[tp])
    dmLabel <- demoLabels[dm]
    
    res = knitr::knit_child(c(here::here('immuno_graphical', 'report_box_demographic.Rmd')), quiet = TRUE)
    cat(res, sep = '\n')
    cat("\\clearpage", sep = '\n')
  }
}
    
```