---
output:
  pdf_document: default
  html_document: default
  
---
# Graphical Description of Immunogenicity Data {#immuno-graphical}

```{r immuno-graphical-setup, echo = FALSE, message = FALSE, include=FALSE}
library(here)
library(latex2exp)
library(knitr)

here::i_am("immuno_graphical/report.Rmd")

if (study_name !="VAT08"){
  bstatus.labels <- c("Baseline Neg", "Baseline Pos")
  bstatus.labels.2 <- c("BaselineNeg", "BaselinePos")
  bstatus.labels.3 <- c("baseline negative", "baseline positive")
} else {
  bstatus.labels <-  c("Naive", "Non-naive")
  bstatus.labels.2 <- bstatus.labels.3 <- c("naive", "non-naive")
}

# repeat whatever in param.R here
times = c("B", paste0("Day", config$timepoints), paste0("Delta", config$timepoints, "overB"))
if(attr(config,"config")=="janssen_pooled_partA") {
  times_ = c("B","Day29","Delta29overB","Day71"); timepoints_=c(29,71)
  labels.time = c("Day 1", "Day 29","D29 fold-rise over D1", "Day 71"); names(labels.time) = times_
  timepoints_=timepoints
} else if (attr(config,"config")=="prevent19_stage2") {
  times_ = c("Day35","C1") 
  labels.time = c("Day 35", "Crossover Day 1"); names(labels.time) = times_
  timepoints_=timepoints
} else {times_ = times; timepoints_=timepoints}

# set time vectors based on times_ and timepoints_
tps_no_delta_over_tinterm <-  times_[!times_ %in% c(paste0("Delta",timepoints_[length(timepoints_)],"over",timepoints_[1]))] #c("B", "Day29", "Delta29overB", "Day57", "Delta57overB")
tps_no_B_and_delta_over_tinterm <-  times_[!times_ %in% c("B",paste0("Delta",timepoints_[length(timepoints_)],"over",timepoints_[1]))] #c("Day29", "Delta29overB", "Day57", "Delta57overB")
tps_no_fold_change <- times_[!grepl("Delta", times_)]
tps_no_B_and_fold_change <- times_[!grepl("Delta", times_) & times_!="B"]
tps_delta_over_B <- times_[grepl("overB",times_)]



if(include_bindN && grepl("bind", assays) && !grepl("bindN", assays) && !grepl("janssen_.+partA.*", attr(config,"config")) && !grepl("vat08", attr(config,"config"))){
  assay_immuno <- c(assays, "bindN")
  labels.assays.all <- c("Binding Antibody to N", labels.assays)
  names(labels.assays.all)[1] <- "bindN"
  labels.assays <- labels.assays.all[assay_immuno]
} else {
  assay_immuno <- assays
}
```

```{r immuno-graphical-caption-setup, echo = FALSE, message = FALSE, include=FALSE}

is.ensemble <- study_name=="ENSEMBLE" | study_name=="MockENSEMBLE" # only ENSEMBLE has by country and by HIV group figures

config <- config::get(config = Sys.getenv("TRIAL"))
if.pair <- ifelse(length(assays)>1, 1, 0)
if.pos.exist <- 1#ifelse(study_name=="AZD1222", 0, 1)

minority.disclaimer <- switch(study_name, 
                              "COVE"="",
                              "MockCOVE"="",
                              "ENSEMBLE"="These plots are restricted to only United States trial participants.",
                              "MockENSEMBLE"="These plots are restricted to only United States trial participants.",
                              "PREVENT19"="",
                              "AZD1222"="",
                              "VAT08"="",
                              "PROFISCOV"="")

neut.marker.captions <- switch(study_name, 
                               "COVE"="The dashed lines in each figure are ULOQ, LLOQ, and positivity cutoffs for binding antibody assays, or ULOQ, LLOQ, and LLOD for neutralizing antibody assays, from top to bottom respectively.",
                               "MockCOVE"="The dashed lines in each figure are ULOQ, LLOQ, and positivity cutoffs for binding antibody assays, or ULOQ, LLOQ, and LLOD for neutralizing antibody assays, from top to bottom respectively.",
                               "ENSEMBLE"="The dashed lines in each figure are ULOQ and positivity cut-off from top to bottom for binding antibody assays, or ULOQ and LLOQ for neutralizing antibody assays, from top to bottom respectively.",
                               "MockENSEMBLE"="The dashed lines in each figure are ULOQ and positivity cut-off for binding antibody assays, or ULOQ and LLOQ for neutralizing antibody assays, from top to bottom respectively.",
                               #"PREVENT19"="The dashed lines in each figure are ULOQ, positivity cut-off and LLOQ for binding antibody assays, or ULOQ and LLOD for neutralizing antibody assays, from top to bottom respectively.",
                               "PREVENT19"="The dashed lines in each figure are ULOQ and LLOQ for binding antibody assays, or ULOQ and LLOD for neutralizing antibody assays, from top to bottom respectively.",
                               "AZD1222"="The dashed lines in each figure are ULOQ, positivity cut-off and LLOQ for binding antibody assays, or ULOQ and LLOD for neutralizing antibody assays, from top to bottom respectively.",
                               
                               "VAT08"="The dashed lines in each figure are ULOQ and LLOQ for binding antibody assays, or ULOQ and LLOD for neutralizing antibody assays, from top to bottom respectively.",
                               "PROFISCOV"="The dashed lines in each figure are ULOQ, positivity cut-off and LLOD for binding antibody assays, or LLOD/positivity cut-off for neutralizing antibody assays, from top to bottom respectively."
                               # PROFISCOV nAb has a ULOQ value out of figure limit
                               )

```

\clearpage
## Pairs plots of antibody markers for overall per-protocal cohort

```{r, echo=FALSE, results='asis'}

for (bsero in bstatus.labels.2) {
  
  bseroLabel <- bstatus.labels.3[match(bsero, bstatus.labels.2)]
  
  for (trt in c("vaccine","placebo", if(study_name=="VAT08") "pooled")) {  
    
    if (study_name!="VAT08" && trt=="placebo" && bsero==bstatus.labels.2[1]) next # only report for placebo baseline neg for VAT08
    if (attr(config,"config") %in% c("janssen_partA_VL","prevent19_stage2") && !(trt=="vaccine" && bsero==bstatus.labels.2[1])) next # only report for vaccine baseline neg for janssan_partA_VL
    
    for (country in c("Nvx_US_Mex", if(study_name=="PREVENT19") "Nvx_US")){
      # only doable when there are >1 assays
      if (if.pair==1){
        
        for(tp in times_[!times_ %in% c(paste0("Delta",timepoints_[length(timepoints_)],"over",timepoints_[1]))]) {
          
          if (study_name=="VAT08" && grepl("Delta", tp)) next # do not report delta timepoints for VAT08
          if (study_name=="VAT08" && trt=="pooled" && tp!="B") next # only report pooled at baseline for VAT08
          if (attr(config,"config")=="janssen_partA_VL" && !grepl("Day", tp)) next # only report peak timepoint for janssen_partA_VL
          
          for (reg in if (attr(config,"config")=="janssen_partA_VL") {c("LATAM_","ZA_")} else {""}) {
            
            for (ab in if (attr(config,"config")=="janssen_partA_VL") {c("bAb_","nAb_","")} else {""}) {
            
              tpLabel <- gsub("ay ", "", labels.time[tp])
              regLabel <- case_when(reg=="LATAM_" ~ "Latin America",
                                    reg=="ZA_" ~ "Southern Africa",
                                    TRUE ~ "")
              abLabel <- case_when(ab=="bAb_" ~ "bAb",
                                    ab=="nAb_" ~ "nAb",
                                    TRUE ~ "Ab")
              
              res = knitr::knit_child(c(here::here('immuno_graphical', 'report_pair_by_time.Rmd')), quiet = TRUE)
              cat(res, sep = '\n')
              cat("\\clearpage", sep = '\n')
            }
          }
          
        }
      }
          
      for (asy in assay_immuno){
        
        if (study_name=="VAT08" && trt=="pooled") next # do not report "pooled" for across timepoint plots
        if (study_name=="VAT08" && asy=="pseudoneutid50_mdw" && bsero=="naive") next # psv_mdw doesn't have any value for naive at baseline
        if (attr(config,"config") %in% c("janssen_partA_VL")) next # no figure for janssen_partA_VL
        
        asyLabel <- gsub("%","\\\\%", labels.assays[asy])
        
        res = knitr::knit_child(c(here::here('immuno_graphical', 'report_pair_by_assay.Rmd')), quiet = TRUE)
        cat(res, sep = '\n')
        cat("\\clearpage", sep = '\n')
      }
      
    }
  }
}

```

\clearpage
## RCDF plots of antibody markers for overall per-protocol cohort
```{r, echo=FALSE, results='asis'}

if (attr(config,"config") %in% c("vat08_combined","prevent19_stage2")){
  for (tp in tps_no_fold_change){
    
    tp_lb = ifelse(tp=="B", "Day1", tp)
    
    res = knitr::knit_child(c(here::here('immuno_graphical', 'report_rcdf_all.Rmd')), quiet = TRUE)
        cat(res, sep = '\n')
        cat("\\clearpage", sep = '\n')
  }
}

  
for (trt in c("trt_both", "trt_vaccine", if(study_name=="VAT08") "trt_placebo")){
  
  if (attr(config,"config")=="prevent19_stage2") next # no these figures for prevent19_stage2
  
  trtLabel <- ifelse(trt=="trt_both", "x randomization arm", paste0(gsub("trt_","", trt), " arm"))
  
  for (bsero in c("bstatus_both", "bstatus_Neg", "bstatus_Pos")){
    if (bsero=="bstatus_Pos" && if.pos.exist==0) next
    if (trt=="trt_both" && bsero!="bstatus_both" && study_name!="VAT08") next # trt_both is only for bstatus both if the study is VAT08
    if (attr(config,"config")=="janssen_partA_VL" && !(trt=="trt_vaccine" && bsero=="bstatus_Neg")) next # only report for vaccine baseline neg for janssan_partA_VL
    
    bseroLabel <- ifelse(bsero=="bstatus_both", "by serostatus", ifelse(bsero=="bstatus_Neg", bstatus.labels.3[1], bstatus.labels.3[2]))
    
    for(tp in times_[!times_ %in% c("B",paste0("Delta",timepoints_[length(timepoints_)],"over",timepoints_[1]))]) {
            
      if (study_name=="VAT08" && grepl("Delta", tp)) next # only report main timepoints for VAT08
      if (attr(config,"config")=="janssen_partA_VL" && !grepl("Day", tp)) next # only report peak timepoint for janssen_partA_VL
      
      tpLabel <- gsub("ay ", "", labels.time[tp])
      
      for (asy in if(study_name!="VAT08" | attr(config,"config")=="janssen_partA_VL") {c("bAb","nAb")} else {c("","bAb","nAb","other")}){ # for VAT08 and janssen_partA_VL, only report for bAb and nAb
        if ( (sum(grepl("bind", assays))==0 & asy=="bAb") | (sum(grepl("neut", assays))==0 & asy=="nAb") | (sum(grepl("ADCP", assays))==0 & asy=="other")) next
        if (asy=="" & (trt!="trt_both" | bsero!="bstatus_both")) next  # trt_both & bstatus_both are only for all assays
        if (asy!="" & trt=="trt_both" & bsero=="bstatus_both") next  # assay subset do not report for trt_both & bstatus_both
        if (study_name=="VAT08" && trt!="trt_both" && bsero!="bstatus_both") next # for VAT08, only report plots with one "both"
        
        
        for (reg in if (attr(config,"config")=="janssen_partA_VL") {c("LATAM_","ZA_")} else {""}) {
            
          regLabel <- case_when(reg=="LATAM_" ~ "Latin America",
                                reg=="ZA_" ~ "Southern Africa",
                                TRUE ~ "")
                
          res = knitr::knit_child(c(here::here('immuno_graphical', 'report_rcdf.Rmd')), quiet = TRUE)
          cat(res, sep = '\n')
          cat("\\clearpage", sep = '\n')
        }
      }
    }
  }
}
```

<!-- 
\clearpage
## Violin plots of antibody markers for overall per-protocol cohort
```{r, echo=FALSE, results='asis'}
if (attr(config,"config")=="janssen_partA_VL"){
  
  for (ab in c("bAb","nAb")){
    for (reg in c("LATAM","ZA")){
      
      regLabel <- case_when(reg=="LATAM" ~ "Latin America",
                            reg=="ZA" ~ "Southern Africa",
                            TRUE ~ "")
      
      res = knitr::knit_child(c(here::here('immuno_graphical', 'report_violin.Rmd')), quiet = TRUE)
          cat(res, sep = '\n')
          cat("\\clearpage", sep = '\n')
    }
  }
}
```

\clearpage
## Scatter plots of antibody markers versus age for overall per-protocol cohort

```{r, echo=FALSE, results='asis'}

if (study_name != "VAT08") { # VAT08 doesn't repor this
  for (bsero in bstatus.labels.2){
  
    bseroLabel <- gsub("baseline ", "", bstatus.labels.3[match(bsero, bstatus.labels.2)])
    
    for (trt in c("Vaccine", "Placebo")){
        
      trtLabel = tolower(trt)
      
      for(tp in times[!grepl("Delta", times)]) {
        
        tpLabel <- gsub("ay ", "", labels.time[tp])
        
        res = knitr::knit_child(c(here::here('immuno_graphical', 'report_scatter.Rmd')), quiet = TRUE)
        cat(res, sep = '\n')
        cat("\\clearpage", sep = '\n')
      }
    }
  }
}
    
```
-->

## Box plots of antibody markers for overall per-protocol cohort

```{r, echo=FALSE, results='asis'}

### Vaccine vs. Placebo (2 arms x 1 baseline status in each plot)
### (VAT08) Baseline neg/pos vs. vaccine/placebo (2 arms x 2 baseline statuses in each plot)
### (VAT08) Baseline neg/pos vs. vaccine/placebo vs. female/male (2 arms x 2 baseline statuses x 2 gender in each plot)

for (bsero in c(bstatus.labels.2, if(study_name=="VAT08") c("bstatus", "bstatus_gender") )) { # only VAT08 report 2 extra kind of plots
  
  if (attr(config,"config")=="janssen_partA_VL") next # janssen_partA_VL do not report this
  if (attr(config,"config")=="prevent19_stage2" & bsero==bstatus.labels.2[2]) next # prevent19_stage2 only has baseline neg
  
  bseroLabel <- c(bstatus.labels.3, if(study_name=="VAT08") c("naive + non-naive", "naive + non-naive") )[match(bsero, c(bstatus.labels.2, if(study_name=="VAT08") c("bstatus", "bstatus_gender")))]
  
  if (bsero=="bstatus_gender") {gender_lb = " females + males"
  } else {gender_lb=""}
  
  for(tp in times_[!times_ %in% c(paste0("Delta",timepoints_[length(timepoints_)],"over",timepoints_[1]))]) {
    
    if (study_name=="VAT08" && grepl("Delta", tp)) next # only report main timepoints for VAT08
    
    tpLabel <- gsub("ay ", "", labels.time[tp])
    
    res = knitr::knit_child(c(here::here('immuno_graphical', 'report_box.Rmd')), quiet = TRUE)
    cat(res, sep = '\n')
    cat("\\clearpage", sep = '\n')
  }
}
    
### Baseline negative vs. positive (2 baseline statuses x 1 arm in each plot)

for (trt in c("vaccine_arm","placebo_arm")) {
  
  if (attr(config,"config") %in% c("janssen_partA_VL","prevent19_stage2")) next # janssen_partA_VL and prevent19_stage2 do not report this
    
  for(tp in times[!times %in% c(paste0("Delta",timepoints[length(timepoints)],"over",timepoints[1]))]) {
    
    if (study_name=="VAT08" && grepl("Delta", tp)) next # only report main timepoints for VAT08
    
    tpLabel <- gsub("ay ", "", labels.time[tp])
    
    res = knitr::knit_child(c(here::here('immuno_graphical', 'report_box_neg_vs_pos.Rmd')), quiet = TRUE)
    cat(res, sep = '\n')
    cat("\\clearpage", sep = '\n')
  }
}

```

<!-- 
## Spaghetti plots of antibody markers over time for overall per-protocol cohort

```{r, fig.cap = paste0("Spaghetti plots of Ab markers over time: baseline negative vaccine + placebo arm"), eval = any(c("B", paste0("Day",timepoints[1]), "Day57") %in% times & study_name!="VAT08" & study_name!="ENSEMBLE" & study_name!="PREVENT19")}
include_graphics(here(
  "immuno_graphical", "output", attr(config,"config"), 
  paste0("spaghetti_plot_BaselineNeg_", study_name, ".pdf")
))
```


```{r, fig.cap = paste0("Spaghetti plots of Ab markers over time: baseline positive vaccine + placebo arm"), eval = any(c("B", paste0("Day",timepoints[1]), "Day57") %in% times & if.pos.exist==1 & study_name!="VAT08" & study_name!="ENSEMBLE" & study_name!="PREVENT19")}
include_graphics(here(
  "immuno_graphical", "output", attr(config,"config"),
  paste0("spaghetti_plot_BaselinePos_", study_name, ".pdf")
))
```

## RCDF plots of antibody markers by demographics for per-protocol cohort

```{r, echo=FALSE, results='asis'}

if_no_minority = attr(config,"config") %in% c("janssen_la_partA","janssen_sa_partA",
                                       "janssen_la_partAsenior","janssen_la_partAnonsenior",
                                       "janssen_sa_partAnonsenior")
demos <- c("age_group","risk_group","age_risk_group","sex_group","age_sex_group","ethnicity","race",if(!if_no_minority)c("minority_group","age_minority_group"),if(study_name=="ENSEMBLE")"country", if(study_name=="ENSEMBLE")"hiv_group")

demoLabels <- c("age groups","high-risk condition","age and high-risk condition","sex assigned at birth","age and sex assgined at birth","ethnicity","race",if(!if_no_minority)c("dichotomous classification of
race and ethnic group","age and dichotomous classification of
race and ethnic group"),if(study_name=="ENSEMBLE")"country of residence", if(study_name=="ENSEMBLE")"HIV
positivity")
names(demoLabels) <- demos

if (study_name!="VAT08") {
  for (bsero in c("BaselineNeg", if (if.pos.exist==1) "BaselinePos")){
    
    for (trt in c("Vaccine", "Placebo")){
      bseroLabel <- ifelse(bsero=="BaselineNeg", "negative", "positive")
      trtLabel=tolower(trt)
      
      if (trt=="Placebo" && bsero=="BaselineNeg") next # do not report Negative Placebo Arm
      
      for (dm in demos){
        for(tp in times[!times %in% c("B",paste0("Delta",timepoints[length(timepoints)],"over",timepoints[1]))]) {
          
          tpLabel <- gsub("ay ", "", labels.time[tp])
          dmLabel <- demoLabels[dm]
          
          res = knitr::knit_child(c(here::here('immuno_graphical', 'report_rcdf_demographic.Rmd')), quiet = TRUE)
          cat(res, sep = '\n')
          cat("\\clearpage", sep = '\n')
        }
      }
    }
  }
}
    
```

## Boxplots of antibody markers by demographics for per-protocol cohort

```{r, echo=FALSE, results='asis'}

if_no_minority = attr(config,"config") %in% c("janssen_la_partA","janssen_sa_partA",
                                       "janssen_la_partAsenior","janssen_la_partAnonsenior",
                                       "janssen_sa_partAnonsenior")
demos <- c("age_group","risk_group","age_x_risk_group","sex","age_x_sex_group","ethnicity","race",if(!if_no_minority)c("minority_group","age_x_minority"),if(study_name=="ENSEMBLE")"country", if(study_name=="ENSEMBLE")"hiv_group")

demoLabels <- c("age groups","high-risk condition","age and high-risk condition","sex assigned at birth","age and sex assgined at birth","ethnicity","race",if(!if_no_minority)c("dichotomous classification of
race and ethnic group","age and dichotomous classification of
race and ethnic group"),if(study_name=="ENSEMBLE")"country of residence", if(study_name=="ENSEMBLE")"HIV
positivity")
names(demoLabels) <- demos

if (study_name!="VAT08") {
  for (bsero in c("BaselineNeg", if (if.pos.exist==1) "BaselinePos")){
    
    for (trt in c("Vaccine", "Placebo")){
      bseroLabel <- ifelse(bsero=="BaselineNeg", "negative", "positive")
      trtLabel=tolower(trt)
      
      if (trt=="Placebo" && bsero=="BaselineNeg") next # do not report Negative Placebo Arm
    
      for (dm in demos){
        for(tp in times[!times %in% c("B",paste0("Delta",timepoints[length(timepoints)],"over",timepoints[1]))]) {
          
          tpLabel <- gsub("ay ", "", labels.time[tp])
          dmLabel <- demoLabels[dm]
          
          res = knitr::knit_child(c(here::here('immuno_graphical', 'report_box_demographic.Rmd')), quiet = TRUE)
          cat(res, sep = '\n')
          cat("\\clearpage", sep = '\n')
        }
      }
    }
  }
}

    
```
-->

## Spaghetti plots of antibody markers over time for overall per-protocol cohort
```{r, echo=FALSE, results='asis'}
if (attr(config,"config")=="janssen_partA_VL"){
  for (ind in c(1:4)){
    
    res = knitr::knit_child(c(here::here('immuno_graphical', 'report_spaghetti.Rmd')), quiet = TRUE)
    cat(res, sep = '\n')
    cat("\\clearpage", sep = '\n')
  }
}
```

## Spider plot of antibody markers for overall per-protocol cohort
```{r, echo=FALSE, results='asis'}
if(study_name=="VAT08" | attr(config,"config")=="janssen_partA_VL"){
  for (tp in if(study_name=="VAT08") {c("day1day22day43", "delta")} else {"day"}) {
  
    for (asy in c("bAb" ,"nAb")){
      
      for (reg in if(attr(config,"config")=="janssen_partA_VL") {c("LATAM_","ZA_")} else {""}){
      
        tpLabel <- case_when(tp=="day1day22day43" ~ "Day 1, Day 22, Day 43", 
                             tp=="delta" ~"fold-rise (D01 to D22, D1 to D43)", 
                             TRUE ~ paste0("Day", timepoints_))
        
        regLabel <- case_when(reg=="LATAM_" ~ "Latin America",
                                reg=="ZA_" ~ "Southern Africa",
                                TRUE ~ "")
  
        res = knitr::knit_child(c(here::here('immuno_graphical', 'report_spider.Rmd')), quiet = TRUE)
        cat(res, sep = '\n')
        cat("\\clearpage", sep = '\n')
      }
    }
  }
}
```

<!-- 
\clearpage
## Set 1 plots: D01, D22, D43 Ab distributions
```{r, echo=FALSE, results='asis', eval=study_name=="VAT08"}

for (a in c("bindSpike","pseudoneutid50")){
  
  for (tp in tps_no_delta_over_tinterm){
    
    tpLabel = ifelse(tp=="B", "Day1", tp)
    res = knitr::knit_child(c(here::here('immuno_graphical', 'report_set1.Rmd')), quiet = TRUE)
    cat(res, sep = '\n')
    cat("\\clearpage", sep = '\n')
  }
}

```

\clearpage
## Set 2 plots: Longitudinal plots D01, D22, D43
```{r, echo=FALSE, results='asis', eval=study_name=="VAT08"}

for (assay_grp in c("bAb","nAb")){
    
    res = knitr::knit_child(c(here::here('immuno_graphical', 'report_set2.Rmd')), quiet = TRUE)
    cat(res, sep = '\n')
    cat("\\clearpage", sep = '\n')
  
}

```

\clearpage
## Set 3 plots: Correlation plots across the markers at a given time point
```{r, echo=FALSE, results='asis', eval=study_name=="VAT08"}

for (bsero in c("non_naive")){
  
  for (trt in c("vac_pla")){
  
    for (tp in tps_no_fold_change){
    
    tpLabel = ifelse(tp=="B", "Day1", tp)
    assay_n = length(assays)
    res = knitr::knit_child(c(here::here('immuno_graphical', 'report_set3.Rmd')), quiet = TRUE)
    cat(res, sep = '\n')
    cat("\\clearpage", sep = '\n')
    }
  }
}

for (bsero in c("naive")){
  
  for (trt in c("vac")){
  
    for (tp in tps_no_B_and_fold_change){
    
    tpLabel = ifelse(tp=="B", "Day1", tp)
    res = knitr::knit_child(c(here::here('immuno_graphical', 'report_set3.Rmd')), quiet = TRUE)
    cat(res, sep = '\n')
    cat("\\clearpage", sep = '\n')
    }
  }
}

```

\clearpage
## Set 4 plots: Correlation plots for a given marker across time points
```{r, echo=FALSE, results='asis', eval=study_name=="VAT08"}

for (a in assays){
    
    res = knitr::knit_child(c(here::here('immuno_graphical', 'report_set4.Rmd')), quiet = TRUE)
    cat(res, sep = '\n')
    cat("\\clearpage", sep = '\n')
  
}

```
-->