---
title: "AMP Trial Threshold Correlate Analysis"
output:
  pdf_document:
    toc: yes
  html_document:
    toc: yes
    toc_float: yes
---

```{r, include = F, warning = F, message = F}
knitr::opts_chunk$set(echo = FALSE, warning = F, message = F, cache = T)

set.seed(10)

# devtools::install_github("jpspeng/npthreshold")
library(npthreshold)
library(SuperLearner)
library(plyr)
library(dplyr)
library(ggplot2)
library(sl3)
library(DT)
library(knitr)
library(msm)
library(data.table)

analysis_data_files <- c(
  HVTN703 = "dt703new.csv",
  HVTN704 = "dt704new.csv",
  pooled_marks = "amp_sieve_pooled_marks_final_v9.csv"
)
```

```{r}
df_v703 <- read.csv(analysis_data_files[["HVTN703"]])
df_v704 <- read.csv(analysis_data_files[["HVTN704"]])

df_amp_marks <- read.csv(analysis_data_files[["pooled_marks"]])

df_v703 <- df_v703 %>% 
  merge(df_amp_marks %>% 
          select(pub_id, pred.ic80.mf),
        by = "pub_id", all.x = T) 

df_v704 <- df_v704 %>% 
  merge(df_amp_marks %>% 
          select(pub_id, pred.ic80.mf),
        by = "pub_id", all.x = T) 

```

```{r}
graphthresh <- function(res,
                        type = "raw",
                        ylabel = "Estimate",
                        xlabel = "Thresholds",
                        cutoffs = NULL,
                        exp10 = FALSE,
                        plot_density = FALSE,
                        plot_endpoints = FALSE,
                        data = NA,
                        weights = NA,
                        marker = NA,
                        annotate = NA,
                        event = NA,
                        time_var = NA,
                        tf = NA,
                        ylimit = NULL,
                        xlimit = NULL,
                        yright_endpoint = "min",
                        pt_flag = FALSE) {

  res <- data.frame(res)

  if (type == "monotone") {
    y_var <- "estimate_monotone"
    ci_lo_var <- "ci_lo_monotone"
    ci_hi_var <- "ci_hi_monotone"
  } else if (type == "raw") {
    y_var <- "estimate"
    ci_lo_var <- "ci_lo"
    ci_hi_var <- "ci_hi"
  } else if (type == "ve") {
    y_var <- "ve_monotone"
    ci_lo_var <- "ve_monotone_ci_lo"
    ci_hi_var <- "ve_monotone_ci_hi"
  } else {
    stop("type must be one of 'raw', 'monotone', or 've'")
  }

  if (!is.null(cutoffs)) {
    res[, ci_lo_var] <- pmax(res[, ci_lo_var], cutoffs[1])
    res[, ci_hi_var] <- pmin(res[, ci_hi_var], cutoffs[2])
  }

  shift_coef <- 0

  if (type == "ve") {
    if (!is.null(ylimit)) {
      scale_coef <- ylimit[2]
    } else {
      scale_coef <- max(res[[ci_hi_var]], na.rm = TRUE)
    }
  } else {
    if (is.null(ylimit)) {
      scale_coef <- max(res[[ci_hi_var]], na.rm = TRUE)
    } else {
      scale_coef <- ylimit[2]
    }
  }

  if (yright_endpoint == "min") {
    yright <- min(res[[y_var]], na.rm = TRUE)
  } else {
    yright <- max(res[[y_var]], na.rm = TRUE)
  }

  ggthresh <- ggplot(res, aes(x = threshold, y = !!rlang::sym(y_var))) +
    geom_point(size = 0.7) +
    geom_line() +
    geom_ribbon(aes(ymin = !!rlang::sym(ci_lo_var),
                    ymax = !!rlang::sym(ci_hi_var)),
                alpha = 0.3, color = NA) +
    labs(x = xlabel, y = ylabel) +
    theme_minimal() +
    theme(plot.title = element_text(hjust = 0.5))

  if (plot_density) {

    if (all(is.na(data)) || all(is.na(weights)) || all(is.na(marker))) {
      stop("When plot_density = TRUE, data, weights, and marker must be supplied.")
    }

    data <- data[!is.na(data[[marker]]) & !is.na(data[[weights]]), , drop = FALSE]

    RCDF <- function(a) {
      (sum(data[[weights]] * (data[[marker]] >= a), na.rm = TRUE) /
         sum(data[[weights]], na.rm = TRUE)) * scale_coef
    }

    RCDF_pt_0.5 <- function(a) {
      (sum(data[[weights]] * ((data[[marker]] / 0.5) >= a), na.rm = TRUE) /
         sum(data[[weights]], na.rm = TRUE)) * scale_coef
    }

    RCDF_pt_3.0 <- function(a) {
      (sum(data[[weights]] * ((data[[marker]] / 3.0) >= a), na.rm = TRUE) /
         sum(data[[weights]], na.rm = TRUE)) * scale_coef
    }

    RCDF <- Vectorize(RCDF)
    RCDF_pt_0.5 <- Vectorize(RCDF_pt_0.5)
    RCDF_pt_3.0 <- Vectorize(RCDF_pt_3.0)

    col_main <- grDevices::rgb(grDevices::col2rgb("olivedrab3")[1],
                               grDevices::col2rgb("olivedrab3")[2],
                               grDevices::col2rgb("olivedrab3")[3],
                               alpha = 255, maxColorValue = 255)

    col_pt1 <- grDevices::rgb(grDevices::col2rgb("steelblue3")[1],
                              grDevices::col2rgb("steelblue3")[2],
                              grDevices::col2rgb("steelblue3")[3],
                              alpha = 255, maxColorValue = 255)

    col_pt2 <- grDevices::rgb(grDevices::col2rgb("firebrick3")[1],
                              grDevices::col2rgb("firebrick3")[2],
                              grDevices::col2rgb("firebrick3")[3],
                              alpha = 255, maxColorValue = 255)

    if (!pt_flag) {
      ggthresh <- ggthresh +
        stat_function(fun = RCDF, color = col_main, geom = "line")
    } else {
      ggthresh <- ggthresh +
        stat_function(aes(color = "IC80 = 0.5 mcg/mL"),
                      fun = RCDF_pt_0.5,
                      geom = "line",
                      linetype = "dashed") +
        stat_function(aes(color = "IC80 = 3.0 mcg/mL"),
                      fun = RCDF_pt_3.0,
                      geom = "line",
                      linetype = "dotdash")    }
  }

  right_breaks <- seq(0, 1, by = 0.25)

  if (!is.null(ylimit)) {
ggthresh <- ggthresh +
  scale_y_continuous(
    breaks = seq(ylimit[1], ylimit[2], by = ylimit[3]),
    sec.axis = sec_axis(~ (. - shift_coef) / scale_coef,
                        name = "Reverse CDF",
                        breaks = right_breaks,
                        labels = sprintf("%.2f", right_breaks))
  ) +
  coord_cartesian(
    ylim = c(ylimit[1], ylimit[2]),
    clip = "on"
  ) +
  theme(axis.text.x = element_text(angle = 0, hjust = 1),
        axis.text.y = element_text(angle = 0, hjust = 1))  } else {
    ggthresh <- ggthresh +
      scale_y_continuous(
        n.breaks = 10,
        sec.axis = sec_axis(~ . / scale_coef,
                            name = "Reverse CDF",
                            breaks = right_breaks,
                            labels = sprintf("%.2f", right_breaks))
      ) +
      theme(axis.text.x = element_text(angle = 0, hjust = 1),
            axis.text.y = element_text(angle = 0, hjust = 1))
  }

  if (plot_endpoints) {

    if (all(is.na(data)) || all(is.na(event)) || all(is.na(time_var)) || all(is.na(tf))) {
      stop("When plot_endpoints = TRUE, data, event, time_var, tf, and marker must be supplied.")
    }

    threshold_min <- min(res$threshold, na.rm = TRUE)
    threshold_max <- max(res$threshold, na.rm = TRUE)

    data_event <- data %>%
      dplyr::filter(
        .data[[event]] == 1,
        .data[[time_var]] <= tf,
        !is.na(.data[[marker]]),
        .data[[marker]] >= threshold_min,
        .data[[marker]] <= threshold_max
      )

    data_event$y_inter <- approx(res$threshold, res[[y_var]],
                                 xout = data_event[[marker]],
                                 yright = yright)$y

    ggthresh <- ggthresh +
      geom_point(aes_string(x = marker, y = "y_inter"),
                 data = data_event,
                 color = "blue")
    }

  min_value <- min(data[, marker], na.rm = TRUE)
max_value <- max(data[, marker], na.rm = TRUE)

if (exp10) {
  if (ceiling(min_value) == floor(max_value) || (max_value - min_value) < 1) {
    breaks <- seq(ceiling(min_value * 10) / 10,
                  floor(max_value * 10) / 10,
                  by = 0.1)
  } else {
    breaks <- seq(ceiling(min_value), floor(max_value), by = 1)
  }

  if (!is.null(xlimit)) {
    xlims <- c(xlimit[1], xlimit[2])
    xbreaks <- breaks
  } else {
    xlims <- c(min_value, max_value)
    xbreaks <- breaks
  }

  if (pt_flag) {
    ggthresh <- ggthresh +
      scale_x_continuous(
        limits = xlims,
        breaks = xbreaks,
        labels = parse(text = paste0("10^", xbreaks)),
        sec.axis = dup_axis(
          name = "VRC01 PT80 against viruses with IC80 = 0.5 or 3.0 mcg/mL"
        )
      )
  } else {
    ggthresh <- ggthresh +
      scale_x_continuous(
        limits = xlims,
        breaks = xbreaks,
        labels = parse(text = paste0("10^", xbreaks))
      )
  }

} else {
  if (!is.null(xlimit)) {
    if (pt_flag) {
      ggthresh <- ggthresh +
        scale_x_continuous(
          limits = c(xlimit[1], xlimit[2]),
          breaks = seq(xlimit[1], xlimit[2], xlimit[3]),
          sec.axis = dup_axis(
            name = "VRC01 PT80 against viruses with IC80 = 0.5 or 3.0 mcg/mL"
          )
        )
    } else {
      ggthresh <- ggthresh +
        scale_x_continuous(
          limits = c(xlimit[1], xlimit[2]),
          breaks = seq(xlimit[1], xlimit[2], xlimit[3])
        )
    }
  } else if (pt_flag) {
    ggthresh <- ggthresh +
      scale_x_continuous(
        sec.axis = dup_axis(
          name = "VRC01 PT80 against viruses with IC80 = 0.5 or 3.0 mcg/mL"
        )
      )
  }
}

  if (!is.na(annotate)[1]) {
    x_annotate_loc <- max(data[, marker], na.rm = TRUE) * 0.85

    ggthresh <- ggthresh +
      annotate("text",
               x = x_annotate_loc,
               y = max(res[, ci_hi_var], na.rm = TRUE) * 0.95,
               label = annotate)
  }
  
  if (pt_flag){
  ggthresh <- ggthresh +
  scale_color_manual(
    name = "Neutralization Titer (PT80)",
    values = c(
      "IC80 = 0.5 mcg/mL" = "steelblue3",
      "IC80 = 3.0 mcg/mL" = "firebrick3"
    )
  ) +
  theme(
    legend.position = "bottom",
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 9)
  )
  }

  ggthresh
}
```


# Overview 

* **Covariates**: Body weight (weight) and trial  (only for pooled 703 and 704 analyses)
* **Time variable**: fudays61towk80
* **Event variable**: status61towk80
* **Marker variables**: Day61conc
* **Phase 2 (sampling) filter**: ph2ind == 1
* **Weight variable**: IPSweight
* **Timeframe**: 534 days 
* Performed analysis for six groups: 1) 703 trial arms (T1 and T2 pooled), 2) 
704 trial arms (T1 and T2 pooled), 3) Pooled 703 and 704 trials arms (T1 and T2 pooled), 4) 703 trial arms 
(All arms pooled), 5) 704 trial arms (All arms pooled), 6) Pooled 703 and 704 trials arms (All arms pooled)
* All learners: GLM

# 703 trial arms (T1 and T2 pooled) {.tabset .tabset-fade}

```{r}
# helper functions to select quantiles
select_quants <- function(df, event_var, marker_var){
  
  max_thresh <- df %>% 
    filter(.data[[event_var]] == 1) %>% 
    arrange(desc(.data[[marker_var]])) %>% 
    slice(3) %>% 
    pull(.data[[marker_var]]) 
  
  quants <- c(seq(min(df[,marker_var], na.rm = T), max_thresh, 10),
                     max_thresh)
  quants <- unique(round(quants))
  
  quants
}

```

```{r}
gen_res <- function(df, 
                    covariates, 
                    time_var, 
                    tf, 
                    event_var, 
                    marker_var, 
                    weight_var, 
                    trt_filter = c("T1+T2"),
                    learner.treatment = Lrnr_glm$new(), 
                    learner.event_type = Lrnr_glm$new(), 
                    learner.failure_time = Lrnr_glm$new(), 
                    learner.censoring_time = Lrnr_glm$new(), 
                    pt_flag = T){
  
  df_analysis <- df %>% filter(rx_pool %in% trt_filter)
  df_placebo <- df %>% filter(rx_pool == "C3")

  quants <- select_quants(df, event_var, marker_var)

  res_placebo_overall <- thresholdSurv(data = df_placebo , 
                                       covariates = covariates,
                                       failure_time = time_var, 
                                       tf = tf, 
                                       event_type = event_var, 
                                       marker = "rx_pool",
                                       learner.treatment = learner.treatment, 
                                       learner.event_type = learner.event_type,
                                       learner.failure_time = learner.failure_time, 
                                       learner.censoring_time = learner.censoring_time, 
                                       verbose = F)
  
  if ("C3" %in% trt_filter){
    risk_placebo <- NULL
    se_placebo <- NULL
  }
  else{
    risk_placebo <- res_placebo_overall$estimate
    se_placebo <- res_placebo_overall$se
  }
  
  res <- thresholdSurv(data = df_analysis , 
                            covariates = covariates,
                            failure_time = time_var, 
                            tf = tf, 
                            event_type = event_var, 
                            marker = marker_var,
                            weights = weight_var,
                            threshold_list = quants, 
                            learner.treatment = learner.treatment,
                            learner.event_type = learner.event_type, 
                            learner.failure_time = learner.failure_time, 
                            learner.censoring_time = learner.censoring_time,
                            placebo_risk = risk_placebo,
                           placebo_se = se_placebo, 
                            verbose = F)
  
  g1 <- graphthresh(data.frame(res), 
                  type = "monotone",
                  ylabel = sprintf("Probability of HIV diagnosis by %s days", tf),
                  xlabel = "VRC01 serum concentration (ucg/ml) Thresholds",
                  plot_density = T,
                  plot_endpoints = T, 
                  data = df_analysis,
                  weights = weight_var,
                  marker = marker_var,
                  event = event_var,
                  time_var = time_var,
                  tf = tf, 
                  exp10 = F, 
                  cutoffs = c(0, 0.1), 
                  xlimit = c(0, 200, 50), 
                  pt_flag = pt_flag) 
  
  g2 <- graphthresh(data.frame(res), 
                  type = "raw",
                  ylabel = sprintf("Probability of HIV diagnosis by %s days", tf),
                  xlabel = "VRC01 serum concentration (ucg/ml) Thresholds",
                  plot_density = T,
                  plot_endpoints = T, 
                  data = df_analysis,
                  weights = weight_var,
                  marker = marker_var,
                  event = event_var,
                  time_var = time_var,
                  tf = tf, 
                  cutoffs = c(0, 0.1),
                  exp10 = F, 
                  xlimit = c(0, 200, 50), 
                  pt_flag = pt_flag) 

    g3 <- graphthresh(data.frame(res), 
                  type = "monotone",
                  ylabel = sprintf("Probability of HIV diagnosis by %s days", tf),
                  xlabel = "VRC01 serum concentration (ucg/ml) Thresholds",
                  plot_density = T,
                  plot_endpoints = T, 
                  data = df_analysis,
                  weights = weight_var,
                  marker = marker_var,
                  event = event_var,
                  time_var = time_var,
                  tf = tf, 
                  exp10 = F, 
                  cutoffs = c(0, 0.1), 
                  ylimit = c(0, 0.07, 0.01), 
                  xlimit = c(0, 200, 50), 
                  pt_flag = pt_flag) 
  
  cat("\n\n## Monotone {.tabset .tabset-fade} \n")

  g1 %>% 
    print()
  
  data.frame(res) %>%
      mutate(ifelse(ci_hi_monotone > 1, 1, ci_hi_monotone)) %>% 
      rename(Threshold = threshold, 
             Estimate = estimate_monotone, 
             SE = se, 
             `Lower CI` = ci_lo_monotone, 
             `Upper CI` = ci_hi_monotone) %>% 
      select(Threshold, rcdf, Estimate, SE, 
             `Lower CI`, `Upper CI`) %>%
      mutate(across(where(is.numeric), ~ signif(.x, 3))) %>% kable() %>% print()

  
  cat("\n\n## Not Monotone {.tabset .tabset-fade} \n")

  g2 %>% 
    print()
  
  data.frame(res) %>%
      rename(Threshold = threshold,
             Estimate = estimate, 
             SE = se, 
             `Lower CI` = ci_lo, 
             `Upper CI` = ci_hi) %>% 
      select(Threshold, rcdf, Estimate, SE, 
             `Lower CI`, `Upper CI`) %>%
      mutate(across(where(is.numeric), ~ signif(.x, 3))) %>% kable() %>% print()
  
  cat("\n\n## Monotone Harmonized Y-Axes {.tabset .tabset-fade} \n")

  g3 %>% 
    print()
  
    if (!("C3" %in% trt_filter)){
    g4 <- graphthresh(data.frame(res), 
                  type = "ve",
                  ylabel ="Prevention efficacy",
                  xlabel = "VRC01 serum concentration (ucg/ml) Thresholds",
                  plot_density = T,
                  plot_endpoints = T, 
                  data = df_analysis,
                  weights = weight_var,
                  marker = marker_var,
                  event = event_var,
                  time_var = time_var,
                  tf = tf, 
                  exp10 = F, 
                  cutoffs = c(-10, 1),
                  ylimit = c(-0.5, 1, 0.25),
                  xlimit = c(0, 200, 50), 
                  pt_flag = pt_flag) 
  cat("\n\n## Prevention efficacy {.tabset .tabset-fade} \n")

  g4 %>% 
    print()

  data.frame(res) %>%
      rename(Threshold = threshold, 
             Estimate = ve_monotone, 
             SE = ve_se, 
             `Lower CI` = ve_monotone_ci_lo, 
             `Upper CI` = ve_monotone_ci_hi) %>% 
      select(Threshold, rcdf, Estimate, SE, `Lower CI`, `Upper CI`) %>%
      mutate(across(where(is.numeric), ~ signif(.x, 3))) %>% kable() %>% print()
    }
}
```


```{r, results = "asis", fig.align='center'}
df <- df_v703 %>% 
  filter(ph2ind == 1)
covariates <- c("weight")
time_var <- "fudays61towk80"
tf <- 533
event_var <- "status61towk80"
marker_var <- "Day61conc"
weight_var <- "IPSweight"

gen_res(df, 
        covariates, 
        time_var, 
        tf, 
        event_var, 
        marker_var, 
        weight_var, 
        trt_filter = c("T1+T2"),
        learner.treatment = Lrnr_glm$new(), 
        learner.event_type = Lrnr_glm$new(), 
        learner.failure_time = Lrnr_glm$new(), 
        learner.censoring_time = Lrnr_glm$new())


```

# 704 trial arms (T1 and T2 pooled) {.tabset .tabset-fade}

```{r, results = "asis", fig.align='center'}
df <- df_v704 %>% 
  filter(ph2ind == 1) 
covariates <- c("weight")
time_var <- "fudays61towk80"
tf <- 533
event_var <- "status61towk80"
marker_var <- "Day61conc"
weight_var <- "IPSweight"

gen_res(df, 
        covariates, 
        time_var, 
        tf, 
        event_var, 
        marker_var, 
        weight_var, 
        trt_filter = c("T1+T2"),
        learner.treatment = Lrnr_glm$new(), 
        learner.event_type = Lrnr_glm$new(), 
        learner.failure_time = Lrnr_glm$new(), 
        learner.censoring_time = Lrnr_glm$new())


```

# Pooled 703 and 704 trials arms (T1 and T2 pooled) {.tabset .tabset-fade}

```{r, results = "asis", fig.align='center'}
df <- df_v703 %>%
  mutate(trial = 0) %>% 
  rbind.fill(df_v704 %>% 
               mutate(trial = 1)) %>% 
  filter(ph2ind == 1) %>% 
  mutate(trial = factor(trial))
covariates <- c("weight", "trial")
time_var <- "fudays61towk80"
tf <- 533
event_var <- "status61towk80"
marker_var <- "Day61conc"
weight_var <- "IPSweight"

gen_res(df, 
        covariates, 
        time_var, 
        tf, 
        event_var, 
        marker_var, 
        weight_var, 
        trt_filter = c("T1+T2"),
        learner.treatment = Lrnr_glm$new(), 
        learner.event_type = Lrnr_glm$new(), 
        learner.failure_time = Lrnr_glm$new(), 
        learner.censoring_time = Lrnr_glm$new())


```

# Pooled 703 and 704 trials arms (T1 and T2 pooled, IC80 < 3) {.tabset .tabset-fade}

```{r, results = "asis", fig.align='center'}
df <- df_v703 %>%
  mutate(trial = 0) %>% 
  rbind.fill(df_v704 %>% 
               mutate(trial = 1)) %>% 
  filter(ph2ind == 1) %>% 
  mutate(trial = factor(trial)) %>% 
  mutate(event_new = ifelse(!is.na(pred.ic80.mf) & 
                              pred.ic80.mf < 3 & 
                              status61towk80 == 1, 1, 0))


covariates <- c("weight", "trial")
time_var <- "fudays61towk80"
tf <- 533
event_var <- "event_new"
marker_var <- "Day61conc"
weight_var <- "IPSweight"

gen_res(df, 
        covariates, 
        time_var, 
        tf, 
        event_var, 
        marker_var, 
        weight_var, 
        trt_filter = c("T1+T2"),
        learner.treatment = Lrnr_glm$new(), 
        learner.event_type = Lrnr_glm$new(), 
        learner.failure_time = Lrnr_glm$new(), 
        learner.censoring_time = Lrnr_glm$new(), 
        pt_flag = F)


```


# Pooled 703 and 704 trials arms (T1 and T2 pooled, IC80 >= 3) {.tabset .tabset-fade}

```{r, results = "asis", fig.align='center'}
df <- df_v703 %>%
  mutate(trial = 0) %>% 
  rbind.fill(df_v704 %>% 
               mutate(trial = 1)) %>% 
  filter(ph2ind == 1) %>% 
  mutate(trial = factor(trial)) %>% 
  mutate(event_new = ifelse(!is.na(pred.ic80.mf) & 
                              pred.ic80.mf >= 3 & 
                              status61towk80 == 1, 1, 0))


covariates <- c("weight", "trial")
time_var <- "fudays61towk80"
tf <- 533
event_var <- "event_new"
marker_var <- "Day61conc"
weight_var <- "IPSweight"

gen_res(df, 
        covariates, 
        time_var, 
        tf, 
        event_var, 
        marker_var, 
        weight_var, 
        trt_filter = c("T1+T2"),
        learner.treatment = Lrnr_glm$new(), 
        learner.event_type = Lrnr_glm$new(), 
        learner.failure_time = Lrnr_glm$new(), 
        learner.censoring_time = Lrnr_glm$new(), 
        pt_flag = F)


```

# 703 trial arms (All arms pooled) {.tabset .tabset-fade}

```{r, results = "asis", fig.align='center'}
df <- df_v703 %>% 
  filter(ph2ind == 1)
covariates <- c("weight")
time_var <- "fudays61towk80"
tf <- 533
event_var <- "status61towk80"
marker_var <- "Day61conc"
weight_var <- "IPSweight"

gen_res(df, 
        covariates, 
        time_var, 
        tf, 
        event_var, 
        marker_var, 
        weight_var, 
        trt_filter = c("T1+T2", "C3"),
        learner.treatment = Lrnr_glm$new(), 
        learner.event_type = Lrnr_glm$new(), 
        learner.failure_time = Lrnr_glm$new(), 
        learner.censoring_time = Lrnr_glm$new())


```

# 704 trial arms (All arms pooled) {.tabset .tabset-fade}


```{r, results = "asis", fig.align='center'}
df <- df_v704 %>% 
  filter(ph2ind == 1) 
covariates <- c("weight")
time_var <- "fudays61towk80"
tf <- 533
event_var <- "status61towk80"
marker_var <- "Day61conc"
weight_var <- "IPSweight"

gen_res(df, 
        covariates, 
        time_var, 
        tf, 
        event_var, 
        marker_var, 
        weight_var, 
        trt_filter = c("T1+T2", "C3"),
        learner.treatment = Lrnr_glm$new(), 
        learner.event_type = Lrnr_glm$new(), 
        learner.failure_time = Lrnr_glm$new(), 
        learner.censoring_time = Lrnr_glm$new())


```

# Pooled 703 and 704 trials arms (All arms pooled) {.tabset .tabset-fade}

```{r, results = "asis", fig.align='center'}
df <- df_v703 %>%
  mutate(trial = 0) %>% 
  rbind.fill(df_v704 %>% 
               mutate(trial = 1)) %>% 
  filter(ph2ind == 1) %>% 
  mutate(trial = factor(trial))
covariates <- c("weight", "trial")
time_var <- "fudays61towk80"
tf <- 533
event_var <- "status61towk80"
marker_var <- "Day61conc"
weight_var <- "IPSweight"

gen_res(df, 
        covariates, 
        time_var, 
        tf, 
        event_var, 
        marker_var, 
        weight_var, 
        trt_filter = c("T1+T2", "C3"),
        learner.treatment = Lrnr_glm$new(), 
        learner.event_type = Lrnr_glm$new(), 
        learner.failure_time = Lrnr_glm$new(), 
        learner.censoring_time = Lrnr_glm$new())


```

# Reproducibility Information

```{r, echo = FALSE, message = FALSE, warning = FALSE, results = "asis"}
commit_hash <- system("git rev-parse HEAD", intern = TRUE)
data_paths <- normalizePath(analysis_data_files, mustWork = TRUE)

cat(sprintf("- **Code commit:** `%s`\n", commit_hash))
for (i in seq_along(data_paths)) {
  cat(sprintf("- **%s data:** `%s`\n", names(data_paths)[[i]], data_paths[[i]]))
}
```
