---
header-includes:
   - \usepackage{float}
output:
  pdf_document: default
  html_document: default
  citation_package: natbib
  number_sections: true
  extra_dependencies: ["caption", "subcaption", "graphicx"]
  toc: true
---

```{r, echo=FALSE, message=FALSE}
message("~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ running cor_threshold report ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~")
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# hack
folder_var <- paste0("cor_threshold/output/",TRIAL,"/BD29naive")
library(here)
library(dplyr)
print(here::here())
TRIAL <- Sys.getenv("TRIAL")
config <- config::get(config = TRIAL)
for(opt in names(config)){
  eval(parse(text = paste0(names(config[opt])," <- config[[opt]]")))
}
DayPrefix = ifelse (TRIAL == 'moderna_boost', "BD", "Day")


```

# Univariate CoR: Nonparametric Threshold Modeling (>=s)

An extension of the unadjusted nonparametric threshold-searching approach
developed in @Donovan, the covariate-adjusted TMLE-based approach developed by
van der Laan, Zhang, Gilbert (submitted) is used to estimate the so-called
threshold-response function $E_X[ E[Y \mid S \geq s, X, A = 1] \mid A=1]$ for a
range of thresholds $s$. Here, $X$ is a set of baseline characteristics, $A=1$
represents the vaccine group, $S$ is the biomarker/immune-response/correlate of
interest, and $Y$ is the indicator of infection diagnosis before the reference time point
$t_f$, which is defined as the final observed time of an event. This parameter can be viewed as a causal/covariate-adjusted version of
the parameter $P(Y=1 \mid S \geq s, A=1)$. Intuitively, the threshold-response
at a given threshold is the expected probability of obtaining of acquiring HIV-1 infection diagnosis if
one experiences a marker/immune-response value above that threshold. The variables adjusted for are: age, whether country is South Africa, BMI and baseline behavioral risk score. A
number of plots and tables are reported:
\begin{enumerate}
\item A plot and table with risk estimates and point-wise 95\% confidence intervals
\item A plot and table with risk estimates and simultaneous 95\% confidence bands
\item Monotone-corrected versions of 1 and 2.
\end{enumerate}

A reverse cumulative distribution function curve estimated by the IPW NPMLE of
the marker values is superimposed on the threshold-response plots and a dashed
red line is added to mark the threshold value after which no more events are
observed.

The blue dots on the plots represent the risk predictions at marker values where there was an observed case.



\newpage

```{r, echo = F, include = F}

ci <- "pointwise"
above = TRUE
monotone <- FALSE

```

```{r, echo = F, include = F}

if(TRIAL %in% c("janssen_pooled_mock", "janssen_pooled_EUA", "janssen_na_mock", "janssen_na_EUA", "janssen_la_mock", "janssen_la_EUA", "janssen_sa_mock", 'janssen_sa_EUA', "janssen_trial_EUA")) {
  
  ENSEMBLE <- TRUE
  CORs <-  c("D29", "D29start1") 
  
} else if(TRIAL %in% c("janssen_pooled_partA", "janssen_la_partA")) {
  
  ENSEMBLE <- TRUE
  CORs <-  c("D29IncludeNotMolecConfirmed", "D29SevereIncludeNotMolecConfirmed", "D29ModerateIncludeNotMolecConfirmed")
  
} else if(TRIAL %in% c("janssen_na_partA", "janssen_sa_partA")) {
  
  ENSEMBLE <- TRUE
  CORs <-  c("D29IncludeNotMolecConfirmed", "D29ModerateIncludeNotMolecConfirmed")
  
} else if(TRIAL %in% c("hvtn705second")) {
  
  ENSEMBLE <- FALSE
  CORs <- c("D210") 
  
} else if(TRIAL %in% c("moderna_mock", "moderna_real")) {
  
  ENSEMBLE <- FALSE
  CORs <- c("D29", "D57") 
  
} else if(TRIAL %in% c("moderna_boost")) {
  
  ENSEMBLE <- FALSE
  CORs <- c("BD29naive", "BD29nnaive") 
  
} else stop("TRIAL not supported")

```


```{r, results="asis", echo = F }

if (TRIAL=='moderna_boost') {
  # assays=c("bindSpike_BA.1", "pseudoneutid50_BA.1", "bindSpike", "pseudoneutid50")
  assays=c("bindSpike_BA.1")
} else {
  assays <- config$assays
}


for(COR in CORs){
  config.cor <- config::get(config = COR)
  day <- config.cor$tpeak
  tpeak <- config.cor$tpeak
  countAfter1 <- COR == "D29start1"
  
  time <- paste0(DayPrefix, tpeak)
  markers <- paste0(DayPrefix, tpeak, assays)
  
  if (TRIAL=='moderna_boost') markers = c(markers, paste0("DeltaBD29overBD1", assays))

  
  ## non-monotone
  if (!config$threshold_monotone_only) {
    title0 <- paste0(COR, " Plots and Tables with estimates and ", ci, " confidence intervals"," for day ", day, " markers")
    if(monotone) {
      title <- paste0(title0, " (monotone-corrected)")
    }
    if(countAfter1) {
      title <- paste0(title0, " (events after 1 day post dose)")
    } else {
      title = title0
    }
    cat("##", title, "\n")
  
    for(marker in markers) {
      key <- paste0(marker)
      assay <- gsub(time, "" , marker)
      if(!(assay %in% assays)) {
        assay <- assays[stringr::str_detect(marker, assays)]
      }
  
      message(key)
      message(assay)
  
      res = knitr::knit_child(c(here::here(folder_var, 'sub_report.Rmd')), quiet = TRUE)
      #res = knitr::knit_child(c(here::here( 'sub_report.Rmd')), quiet = TRUE)
  
      cat(res, sep = '\n')
      cat("\\clearpage", sep = '\n')
    }
  }
  
  
  # monotone
  monotone <- TRUE

  title0 <- paste0(COR, " Plots and Tables with estimates and ", ci, " confidence intervals"," for day ", day, " markers")
  if(monotone) {
    title <- paste0(title0, " (monotone-corrected)")
  }
  if(countAfter1) {
    title <- paste0(title0, " (events after 1 day post dose)")
  } else {
    title = title0
  }
  cat("##", title, "\n")
  
  for(marker in markers) {
    key <- paste0(marker)
    #assay <- assays[stringr::str_detect(marker, assays)]
    assay <- gsub(time, "" , marker)
    

    res = knitr::knit_child(c(here::here('cor_threshold', 'sub_report.Rmd')), quiet = TRUE)
    
    cat(res, sep = '\n')
    cat("\\clearpage", sep = '\n')
  }
}


```



```{r, echo = F , results = "asis" }
ci <- "simultaneous"

for(COR in CORs){
  config.cor <- config::get(config = COR)
  day <- config.cor$tpeak
  tpeak <- config.cor$tpeak
  countAfter1 <- COR == "D29start1"
  
  time <- paste0(DayPrefix, tpeak)
  markers <- paste0(DayPrefix, tpeak, assays)
  
  
  ## non-monotone
  if (!config$threshold_monotone_only) {
    title0 <- paste0(COR, " Plots and Tables with estimates and ", ci, " confidence intervals"," for day ", day, " markers")
    if(monotone) {
      title <- paste0(title0, " (monotone-corrected)")
    }
    if(countAfter1) {
      title <- paste0(title0, " (events after 1 day post dose)")
    } else {
      title = title0
    }
    cat("##", title, "\n")
    
    for(marker in markers) {
      key <- paste0(marker)
      #assay <- assays[stringr::str_detect(marker, assays)]
      assay <- gsub(time, "" , marker)
      res = knitr::knit_child(c(here::here('sub_report.Rmd')), quiet = TRUE)
    
      cat(res, sep = '\n')
      cat("\\clearpage", sep = '\n')
    }
  }
  
  
  ## monotone
  monotone <- TRUE

  title0 <- paste0(COR, " Plots and Tables with estimates and ", ci, " confidence intervals"," for day ", day, " markers")
  if(monotone) {
    title <- paste0(title0, " (monotone-corrected)")
  }
  if(countAfter1) {
    title <- paste0(title0, " (events after 1 day post dose)")
  } else {
    title = title0
  }
  cat("##", title, "\n")
  
  for(marker in markers) {
    key <- paste0(marker)
    #assay <- assays[stringr::str_detect(marker, assays)]
    assay <- gsub(time, "" , marker)
    
    res = knitr::knit_child(c(here::here('cor_threshold', 'sub_report.Rmd')), quiet = TRUE)
    
    cat(res, sep = '\n')
    cat("\\clearpage", sep = '\n')
  }
  
  
}



```





