---
header-includes:
   - \usepackage{float}
output:
  pdf_document: default
  html_document: default
  citation_package: natbib
  number_sections: true
  extra_dependencies: ["caption", "subcaption", "graphicx"]
  toc: true
---

```{r, echo = F, include = F}
if(above) {
  dir_term <- ""
} else {
  dir_term  <- "_below"
}
if(above) {
  dashed_line <- "The dashed red line marks the threshold after which no more COVID events are observed."
  if(tolower(TRIAL) %in% c("hvtn705")) {
    dashed_line <- "The dashed red line marks the threshold after which no more HIV events are observed."
  }
} else {
  dashed_line <- ""
}
if(monotone) {
  key0 <- "monotone_"
  add_line <- "The estimates and confidence intervals are adjusted using the assumption that the true threshold-response is nonincreasing."
  add_term <- "monotone-corrected "
} else{
  key0 <- ""
  add_line <- ""
  add_term <- ""
}
if(ci == "simultaneous") {
  ci_key <- "simult"
} else{
  ci_key <- ci
}

ci_label <- paste0(ci, " ")
 

 addsss <- ""
if(countAfter1) {
  addsss <- "(counting events after 1 day post dose)"
}
```

 
\clearpage
### Day `r day` `r assay` `r addsss`

\begin{figure}
\centering
\includegraphics[width=0.75\textwidth]{`r here::here(folder_var, "figs", paste0(ci,"_CI"), paste0("PLOT_",key0,   key, "_", ci_key, "CI", dir_term, ".pdf"))`}
\caption{Adjusted threshold-response function for a range of thresholds of the
  Day `r day` `r gsub("_", "\\\\_", assay)` levels with `r ci` 95\% confidence intervals. `r dashed_line` `r add_line` The blue dots correspond with marker values where an event is observed. }
\end{figure}

 
```{r, output = "asis", echo = FALSE, eval = TRUE}
 file <- (here::here(folder_var,   "figs", paste0(ci,"_CI"), paste0("TABLE_", dir_term, key0,   key, "_", ci_key, "CI", dir_term, ".rds")))
if(!file.exists(file)) {
  stop(key)
  stop(file)
}

ptwise_tab_guts <- readRDS(here::here(folder_var,   "figs", paste0(ci,"_CI"), paste0("TABLE_", dir_term, key0,   key, "_", ci_key, "CI", dir_term, ".rds")))
knitr::kable(ptwise_tab_guts, format = "latex", row.names = F, booktabs = TRUE, escape = FALSE,
            caption = paste0("Table of ", add_term,"risk estimates for a range of thresholds with ", ci_label,"95\\% confidence intervals."),
              linesep = "") %>%
    kableExtra::kable_styling(latex_options = c("scaled_down", "striped","hold_position") )
```

\clearpage
