---
title: "Threshold Analysis on Sanofi P3005 Data"
output:
  html_document:
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
---

```{r, include = F, warning = F, message = F}
knitr::opts_chunk$set(echo = FALSE, warning = F, message = F)

library(npthreshold)
library(SuperLearner)
library(dplyr)
library(ggplot2)
library(sl3)
library(DT)
library(knitr)
library(msm)
```

```{r old_graphthresh}
# old version of npthreshold code, used for this report 
graphthresh <- function(res,
                        monotone = F,
                        ylabel = "Probability of COVID-19 by 85 Days Post Day 43 Visit",
                        xlabel = "Threshold", 
                        exp10 = F, 
                        graph_ve = F, 
                        title = "", 
                        lod_limit = 2.4, 
                        lod_label = "LLOQ/2",
                        include_lod = T, 
                        ylim = NULL){
  
  res_graph <- res %>% 
    mutate(ci_lo = ifelse(ci_lo < 0, 0, ci_lo), 
           ci_lo_monotone = ifelse(ci_lo_monotone < 0, 0, ci_lo_monotone)
           )
  
  res_graph <- data.frame(res_graph)
  
  if (monotone){
    y_var <- "estimate_monotone"
    ci_lo_var <- "ci_lo_monotone"
    ci_hi_var <- "ci_hi_monotone"
  }
  else{
    y_var <- "estimate"
    ci_lo_var <- "ci_lo"
    ci_hi_var <- "ci_hi"
  }
  if (graph_ve){
    res_graph <- res_graph %>% 
      mutate(ve_monotone_ci_hi = ifelse(ve_monotone_ci_hi > 1, 1, ve_monotone_ci_hi))
    
    y_var <- "ve_monotone"
    ci_lo_var <- "ve_monotone_ci_lo"
    ci_hi_var <- "ve_monotone_ci_hi"
    ylabel <- "Vaccine efficacy"
  }
  
  if (!is.null(ylim)){
    res_graph[,ci_lo_var] <- pmax(res_graph[, ci_lo_var], ylim[1])
    res_graph[,ci_hi_var] <- pmin(res_graph[, ci_hi_var], ylim[2])
  }
  
  plt <- ggplot2::ggplot(res_graph, ggplot2::aes(x = threshold, y = !!sym(y_var))) +
    geom_point(size = 0.2) + 
    geom_line() +
    geom_ribbon(aes(ymin = !!sym(ci_lo_var), ymax = !!sym(ci_hi_var)), alpha = 0.3, color = NA) +
    labs(x = "Thresholds", y = "Estimates (CI)") +
    theme_minimal() +
    scale_y_continuous(n.breaks = 10) +
    scale_x_continuous(
      limits = c(min(res$threshold), max(res$threshold))) +
    xlab(xlabel) +
    ylab(ylabel) + 
    ggtitle(title) + 
    theme(plot.title = element_text(hjust = 0.5)) 
  
  if (!is.null(ylim)){
    plt <- plt + scale_y_continuous(n.breaks = 10, limits = c(ylim[1], ylim[2]))
  }
  else{
    plt <- plt + scale_y_continuous(n.breaks = 10)
  }
}


custom_labels <- function(breaks) {
      labels <- ifelse(breaks == lod_limit, lod_label, sprintf("10^%s  ", round(breaks,1)))
      return(labels)
    }

add_rcdf <- function(ggthresh,
                     data,
                     weights,
                     marker, 
                     event, 
                     time_var,
                     tf, 
                     monotone = F,
                     exp10 = F,
                     annotate = "", 
                     lod_limit = 2.4, 
                     lod_label = "LLOQ/2", 
                     graph_ve = F, 
                     ylim = NULL){
  
  
  data_event <- data %>% 
    filter(.data[[event]] == 1 & .data[[time_var]] <= tf) 
  
  shift_coef <- 0 
  
  if (graph_ve){
    estimate_var <- "ve_monotone"

    if (is.null(ylim)){
      scale_coef <- 1
    }
    else{
      scale_coef <- ylim[2] - ylim[1]
      shift_coef <- ylim[1]
    }

    yright <- max(ggthresh$data[[estimate_var]])
  }
  else {
    
    if (is.null(ylim)){
      scale_coef <- max(ggthresh$data$ci_hi, na.rm = T)
    }
    else{
      scale_coef <- ylim[2]
    }

  if (monotone){
    estimate_var <- "estimate_monotone"
   }
  else{
    estimate_var <- "estimate"
  }
  yright <- min(ggthresh$data[[estimate_var]])
  }
  
  data_event$y_inter <- approx(ggthresh$data$threshold, ggthresh$data[[estimate_var]],
                               xout = data_event[,marker], 
                               yright = yright)$y
  
  RCDF <- function(a) {
    (sum(data[[weights]] * (data[[marker]] >= a)) /
       sum(data[[weights]]) * scale_coef) + shift_coef
  }
  
  RCDF <- Vectorize(RCDF)

  col <- c(col2rgb("olivedrab3")) # orange, darkgoldenrod2
  col <- rgb(col[1], col[2], col[3], alpha = 255 * 0.4, maxColorValue = 255)

  if (is.null(ylim)){
    plt <- ggthresh +
      geom_point(aes_string(x = marker, y = "y_inter"), data = data_event, color = "blue") + 
      stat_function(fun = RCDF, color = col,
                    geom = "area", fill = col, alpha = 0.2) +
        scale_y_continuous(
          sec.axis = sec_axis(~ (. - shift_coef) / scale_coef,
                              name = "Reverse CDF",
                              breaks = c(0, 0.2, 0.4, 0.6, 0.8, 1)))  +
      theme(plot.title = element_text(hjust = 0.5),
            axis.text.x = element_text(angle = 0, hjust = 1),
            axis.text.y = element_text(angle = 0, hjust = 1)) + 
      geom_vline(xintercept = max(data_event[,marker]), 
                 linetype = "dotted", 
                 color = "red")
  }
  else{
    plt <- ggthresh +
      geom_point(aes_string(x = marker, y = "y_inter"), data = data_event, color = "blue") + 
        stat_function(fun = RCDF, color = col, geom = "line") +
        scale_y_continuous(
          breaks = seq(ylim[1], ylim[2], by = ylim[3]),
          sec.axis = sec_axis(~ (. - shift_coef) / scale_coef,
                              name = "Reverse CDF",
                              breaks = c(0, 0.2, 0.4, 0.6, 0.8, 1)))  +
      theme(plot.title = element_text(hjust = 0.5),
            axis.text.x = element_text(angle = 0, hjust = 1),
            axis.text.y = element_text(angle = 0, hjust = 1)) + 
      geom_vline(xintercept = max(data_event[,marker]), 
                 linetype = "dotted", 
                 color = "red")
  }
  
  
  if (exp10){
    # Find the minimum value from the data
    min_value <- min(data[, marker], na.rm = TRUE)
    
    
    if (min_value < ceiling(min(data[, marker], na.rm = TRUE)) - 0.1){
    breaks <- c(min_value, 
                ceiling(min_value):floor((max(data[, marker], na.rm = TRUE))))
    }
    else{
    breaks <- c(min_value, 
                (ceiling(min_value) + 1):floor((max(data[, marker], na.rm = TRUE))))
    }

    # Adjust scale_x_log10 to include custom limits and labels
    plt <- plt + 
      scale_x_continuous(
        limits = c(min_value, 
                   max(data[, marker], na.rm = TRUE)), 
        breaks = breaks, 
        labels = label_parsed(custom_labels(breaks))
      ) 

  }
  else{
    # Find the minimum value from the data
    min_value <- min(data[, marker], na.rm = TRUE)

    breaks <- (ceiling(min_value)):floor((max(data[, marker], na.rm = TRUE)))

    plt <- plt +
      scale_x_continuous(limits = c(min(data[,marker]), max(data[,marker])), 
                         breaks = breaks,
                         labels = label_parsed(custom_labels(breaks))
)
  }
  
  x_annotate_loc <- max(data[,marker]) * 0.85
    
  plt  + 
    annotate("text", 
             x = x_annotate_loc,  
             y = ylim[2] * 0.95,  
             label = annotate)
  
}

```

```{r read_data, cache = T}
# read data 
# df <- read.csv("vat08_combined_data_processed_20250321.csv")
df <- read.csv("/trials/covpn/p3005/analysis/correlates/Part_A_Blinded_Phase_Data/adata/vat08_combined_data_processed_20250417.csv")
```

```{r pull_last_event_times}
# find last timepoint of event 

# # stage 1, spike
# df %>%
#   filter(Trialstage==1 & Bserostatus==1 & ph2.D43.bAb) %>%
#   filter(Trt == 1) %>%
#   filter(EventIndOmicronD43M6hotdeck10 == 1) %>%
#   arrange(desc(EventTimeOmicronD43M6hotdeck10)) %>%
#   slice(1) %>%
#   pull(EventTimeOmicronD43M6hotdeck10)
# 
# df %>%
#   filter(Trialstage==1 & Bserostatus==1 & ph2.D43.bAb) %>%
#   filter(Trt == 0) %>%
#   filter(EventIndOmicronD43M6hotdeck10 == 1) %>%
#   arrange(desc(EventTimeOmicronD43M6hotdeck10)) %>%
#   slice(1) %>%
#   pull(EventTimeOmicronD43M6hotdeck10)
# 
# 
# # stage 1, nab
# df %>%
#   filter(Trialstage==1 & Bserostatus==1 & ph2.D43.st1.nAb.batch0and1) %>%
#   filter(EventIndOmicronD43M6hotdeck10 == 1) %>%
#   filter(Trt == 1) %>%
#   arrange(desc(EventTimeOmicronD43M6hotdeck10)) %>%
#   slice(1) %>%
#   pull(EventTimeOmicronD43M6hotdeck10)
# 
# df %>%
#   filter(Trialstage==1 & Bserostatus==1 & ph2.D43.st1.nAb.batch0and1) %>%
#   filter(EventIndOmicronD43M6hotdeck10 == 1) %>%
#   filter(Trt == 0) %>%
#   arrange(desc(EventTimeOmicronD43M6hotdeck10)) %>%
#   slice(1) %>%
#   pull(EventTimeOmicronD43M6hotdeck10)
# 
# # stage 2, spike
# df %>%
#   filter(Trialstage==2 & Bserostatus==1 & ph2.D43.bAb) %>%
#   filter(Trt == 1) %>%
#   filter(EventIndOmicronD43M5hotdeck10 == 1) %>%
#   arrange(desc(EventTimeOmicronD43M5hotdeck10)) %>%
#   slice(1) %>%
#   pull(EventTimeOmicronD43M5hotdeck10)
# 
# df %>%
#   filter(Trialstage==2 & Bserostatus==1 & ph2.D43.bAb) %>%
#   filter(Trt == 0) %>%
#   filter(EventIndOmicronD43M5hotdeck10 == 1) %>%
#   arrange(desc(EventTimeOmicronD43M5hotdeck10)) %>%
#   slice(1) %>%
#   pull(EventTimeOmicronD43M5hotdeck10)
# 
# 
# # stage 2, nab
# df %>%
#   filter(Trialstage==2 & Bserostatus==1 & ph2.D43.nAb) %>%
#   filter(EventIndOmicronD43M5hotdeck10 == 1) %>%
#   filter(Trt == 1) %>%
#   arrange(desc(EventTimeOmicronD43M5hotdeck10)) %>%
#   slice(1) %>%
#   pull(EventTimeOmicronD43M5hotdeck10)
# 
# 
# df %>%
#   filter(Trialstage==2 & Bserostatus==1 & ph2.D43.nAb) %>%
#   filter(EventIndOmicronD43M5hotdeck10 == 1) %>%
#   filter(Trt == 0) %>%
#   arrange(desc(EventTimeOmicronD43M5hotdeck10)) %>%
#   slice(1) %>%
#   pull(EventTimeOmicronD43M5hotdeck10)
```

```{r process_data}
# process data 
df <- df %>% 
  mutate(Sex = factor(Sex), 
         Region3 = factor(Region3))
```

```{r spike_marker_list}
spike_marker_list <- list(
  Day43bindSpike = list(
    readable = "IgG Spike Index Concentration (AU/ml)", 
    shortname = "IgG Spike Index",
    change_var = "Delta43overBbindSpike"
  ), 
  Day43bindSpike_beta = list(
    readable = "IgG Beta Spike Concentration (AU/ml)", 
    shortname = "IgG Spike Beta",
    change_var = "Delta43overBbindSpike_beta"
  ), 
  Day43bindSpike_alpha = list(
    readable = "IgG Alpha Spike Concentration (AU/ml)", 
    shortname = "IgG Spike Alpha",
    change_var = "Delta43overBbindSpike_alpha"
  ),
  Day43bindSpike_gamma = list(
    readable = "IgG Gamma Spike Concentration (AU/ml)", 
    shortname = "IgG Spike Gamma",
    change_var = "Delta43overBbindSpike_gamma"
  ),
  Day43bindSpike_delta1 = list(
    readable = "IgG Delta1 Spike Concentration (AU/ml)", 
    shortname = "IgG Spike Delta1",
    change_var = "Delta43overBbindSpike_delta1"
  ),
  Day43bindSpike_delta2 = list(
    readable = "IgG Delta2 Spike Concentration (AU/ml)", 
    shortname = "IgG Spike Delta2",
    change_var = "Delta43overBbindSpike_delta2"
  ),
  Day43bindSpike_delta3 = list(
    readable = "IgG Delta3 Spike Concentration (AU/ml)", 
    shortname = "IgG Spike Delta3",
    change_var = "Delta43overBbindSpike_delta3"
  ),
  Day43bindSpike_omicron = list(
    readable = "IgG Omicron Spike Concentration (AU/ml)", 
    shortname = "IgG Spike Omicron",
    change_var = "Delta43overBbindSpike_omicron"
  ),
  Day43bindSpike_mdw = list(
    readable = "IgG Spike Cross-reactivity Score (weighted average AU/ml)", 
    shortname = "IgG Spike Cross-Reactivity Score",
    change_var = "Delta43overBbindSpike_mdw"
  )
)
```

```{r neut_marker_list}
neut_marker_list <- list(
  Day43pseudoneutid50 = list(
    readable = "nAb ID50 reference titer (AU/ml)", 
    shortname = "nAb ID50 Reference", 
    change_var = "Delta43overBpseudoneutid50"
  ), 
  Day43pseudoneutid50_B.1.351 = list(
    readable = "nAb ID50 titer for B.1.351 (AU/ml)", 
    shortname = "nAb ID50 B.1.351", 
    change_var = "Delta43overBpseudoneutid50_B.1.351"
  ), 
  Day43pseudoneutid50_BA.1 = list(
    readable = "nAb ID50 titer for BA.1 (AU/ml)", 
    shortname = "nAb ID50 BA.1", 
    change_var = "Delta43overBpseudoneutid50_BA.1"
  ),
  Day43pseudoneutid50_BA.2 = list(
    readable = "nAb ID50 titer for BA.2 (AU/ml)", 
    shortname = "nAb ID50 BA.2", 
    change_var = "Delta43overBpseudoneutid50_BA.2"
  ),
  Day43pseudoneutid50_BA.4.5 = list(
    readable = "nAb ID50 titer for BA.4/5 (AU/ml)", 
    shortname = "nAb ID50 BA.4/5", 
    change_var = "Delta43overBpseudoneutid50_BA.4.5"
  ),
  Day43pseudoneutid50_mdw = list(
    readable = "nAb ID50 Titer Breadth Score (weighted average AU/ml)", 
    shortname = "nAb ID50 Breadth Score", 
    change_var = "Delta43overBpseudoneutid50_mdw"
  )
)
```

```{r helper_list}
stage_dict <- list(
  Stage1 = list(
    spike_filter = "Trialstage==1 & Bserostatus==1 & ph2.D43.bAb", 
    neut_filter = "Trialstage==1 & Bserostatus==1 & ph2.D43.st1.nAb.batch0and1",
    marginal_filter = "Trialstage==1 & Bserostatus==1 & ph1.D43",
    spike_weight = "wt.D43.bAb", 
    neut_weight = "wt.D43.st1.nAb.batch0and1", 
    time_var = "EventTimeOmicronD43M6hotdeck10",
    event_var = "EventIndOmicronD43M6hotdeck10", 
    tf = 158
  ), 
  
  Stage2 = list(
    spike_filter = "Trialstage==2 & Bserostatus==1 & ph2.D43.bAb", 
    neut_filter = "Trialstage==2 & Bserostatus==1 & ph2.D43.nAb",
    marginal_filter = "Trialstage==2 & Bserostatus==1 & ph1.D43",
    spike_weight = "wt.D43.bAb", 
    neut_weight = "wt.D43.nAb", 
    time_var = "EventTimeOmicronD43M5hotdeck10",
    event_var = "EventIndOmicronD43M5hotdeck10",
    tf = 124
  )
)
```

```{r delta_method_func}
calc_delta_method <- function(row, placebo_incidence, placebo_se) {
  # Extract values from the row
  estimate_monotone <- row['estimate_monotone']
  estimate_se  <- row['se']

  # Variance-covariance matrix (assuming no covariance)
  cov_matrix <- matrix(c(estimate_se^2, 0, 0, placebo_se^2), nrow = 2)
  
  # Calculate the standard error using the delta method
  se_ratio <- deltamethod(~ x1 / x2, mean = c(estimate_monotone, placebo_incidence), 
                          cov = cov_matrix)
  
  return(se_ratio)
}

```

```{r rcdf_func}
RCDF <- function(a, data, weights, marker) {
  w <- data[[weights]]
  x <- data[[marker]]
  sapply(a, function(thresh) {
    sum(w * (x >= thresh)) / sum(w)
  })
}
```


```{r analysis_helper}
run_analysis_helper <- function(data,
                                time_var, 
                                event_var, 
                                marker_var,
                                weight_var = NULL, 
                                covariates = c("standardized_risk_score"),
                                xlabel = "Thresholds",
                                tf = 128, 
                                exp10 = F, 
                                overall = F, 
                                annotate = F, 
                                placebo_incidence = NULL, 
                                placebo_se = NULL, 
                                title = "",
                                lod_limit = 2.4, 
                                lod_label = "LLOQ/2", 
                                modify_left_point = F, 
                                left_estimate = NULL, 
                                left_se = NULL, 
                                max_thresh = NULL){
  
  t0 <- data %>% 
    filter(.data[[event_var]] == 1) %>% 
    arrange(desc(time_var)) %>% 
    slice(3) %>% 
    pull(.data[[time_var]])
  
  
  if (overall){
    quants <- NULL
  }
  else{
    if (is.null(max_thresh)){
      max_thresh <- data %>% 
        filter(.data[[event_var]] == 1) %>% 
        arrange(desc(.data[[marker_var]])) %>% 
        slice(3) %>% 
        pull(.data[[marker_var]]) 
    }
  
    quants <- seq(min(data[,marker_var]), max_thresh, 0.1)
  }
  
  res <- thresholdSurv(data = data, 
                       covariates = covariates,
                       failure_time = time_var, 
                       tf = tf, 
                       event_type = event_var, 
                       marker = marker_var,
                       weights = weight_var,
                       threshold_list = quants, 
                       learner.treatment = Lrnr_glm$new(),
                       learner.event_type = Lrnr_glm$new(),
                       learner.failure_time = Lrnr_glm$new(),
                       learner.censoring_time = Lrnr_glm$new(),
                       verbose = F)
  
  if (modify_left_point){
    res[1,"estimate"] <- left_estimate
    res[1, "se"] <- left_se
    res[1, "ci_lo"] <- left_estimate - (1.96 * left_se)
    res[1, "ci_hi"] <- left_estimate + (1.96 * left_se)
    
    n_event_cutoff <- 10
  
    weights_for_iso <- sqrt(res$n_in_bin)
    weights_for_iso[res$n_events_in_bin < n_event_cutoff] <- 0.01
    weights_for_iso <- weights_for_iso / sum(weights_for_iso)
    
    res$estimate_monotone <- -isotone::gpava(res$threshold,
                                             -res$estimate,
                                             weights = weights_for_iso)$x
    res$ci_lo_monotone <- res$estimate_monotone - (1.96 * res$se)
    res$ci_hi_monotone <- res$estimate_monotone + (1.96 * res$se)

  }
  
  if (!overall){
  g1_monotone <- graphthresh(res, monotone = T, 
                    ylabel = sprintf("Probability of COVID-19 by %s Days Post Day 43 Visit", 
                                     tf), 
                    xlabel = xlabel, 
                    exp10 = exp10, 
                    title = title, 
                    ylim = c(0, 0.015, 0.003))
  
  g1 <- graphthresh(res, monotone = F, 
                    ylabel = sprintf("Probability of COVID-19 by %s Days Post Day 43 Visit", 
                                     tf), 
                    xlabel = xlabel, 
                    exp10 = exp10, 
                    title = title, 
                    ylim = c(0, 0.015, 0.003))
  
  if (annotate){
    annotate_text <- sprintf("Placebo risk: %s", round(placebo_incidence, 3))
  }
  else{
    annotate_text <- ""
  }
  
  g2_monotone <- add_rcdf(g1_monotone, data = data, weights = weight_var, 
                 marker = marker_var, 
                 exp10 = exp10, 
                 event = event_var, 
                 time_var = time_var, 
                 tf = tf, 
                 monotone = T,
                 annotate = annotate_text, 
                 lod_limit = lod_limit, 
                 lod_label = lod_label,
                ylim = c(0, 0.015, 0.003))
  
  g2 <- add_rcdf(g1, data = data, weights = weight_var, 
                 marker = marker_var, 
                 exp10 = exp10, 
                 event = event_var, 
                 time_var = time_var, 
                 tf = tf, 
                 annotate = annotate_text, 
                 lod_limit = lod_limit, 
                 lod_label = lod_label, 
                ylim = c(0, 0.015, 0.003))
  }
  else{
    g2 <- NULL
    g2_monotone <- NULL
  }
  
  if (!is.null(placebo_incidence)){
  res <- res %>% 
    mutate(ve_monotone = 1 - (estimate_monotone / placebo_incidence))
  
  res$ve_se <- apply(res, 1, calc_delta_method, 
                     placebo_incidence = placebo_incidence, 
                     placebo_se = placebo_se)
  
  res <- res %>% 
    mutate(ve_monotone_ci_lo = ve_monotone - (1.96 * ve_se), 
           ve_monotone_ci_hi = ve_monotone + (1.96 * ve_se))

  g_ve <- graphthresh(res, monotone = T, 
                      xlabel = xlabel, 
                      exp10 = exp10, 
                      graph_ve = T, 
                      title = title,
                      include_lod = exp10, 
                      ylim = c(-0.2, 1, 0.2))
  
  g_ve_rcdf <- add_rcdf(g_ve,
                        data = data, 
                        weights = weight_var, 
                        marker = marker_var, 
                        exp10 = exp10, 
                        event = event_var, 
                        time_var = time_var, 
                        tf = tf, 
                        annotate = "", 
                        lod_limit = lod_limit, 
                        lod_label = lod_label, 
                        graph_ve = T, 
                      ylim = c(-0.2, 1, 0.2))
  }
  else{
    g_ve <- NULL
    g_ve_rcdf <- NULL
    res$ve_monotone <- NA 
    res$ve_se <- NA 
    res$ve_monotone_ci_lo <- NA 
    res$ve_monotone_ci_hi <- NA 
  }
  
  if (is.null(weight_var)){
    weight_var <- "temp_weight"
    data$temp_weight <- 1
  }
  
  rcdf_vals <- RCDF(res$threshold, data, 
                    weight_var, 
                    marker_var)

  list(
    graph = g2, 
    
    graph_monotone = g2_monotone,
    
    graph_ve = g_ve_rcdf,
    
    table_monotone = res %>%
      rename(Thresholdlog10 = threshold, 
             Estimate = estimate_monotone, 
             SE = se, 
             `Lower CI` = ci_lo_monotone, 
             `Upper CI` = ci_hi_monotone) %>% 
      mutate(Threshold = 10^Thresholdlog10, 
             RCDF = 1 - rcdf_vals) %>% 
      rename(`Threshold (log10)` = Thresholdlog10) %>% 
      select(`Threshold (log10)`, Threshold, RCDF, Estimate, SE, 
             `Lower CI`, `Upper CI`) %>%
      mutate(across(where(is.numeric), ~ signif(.x, 3))),
    
    table = res %>%
      rename(Thresholdlog10 = threshold, 
             Estimate = estimate, 
             SE = se, 
             `Lower CI` = ci_lo, 
             `Upper CI` = ci_hi) %>% 
      mutate(Threshold = 10^Thresholdlog10) %>% 
      rename(`Threshold (log10)` = Thresholdlog10) %>% 
      select(`Threshold (log10)`, Threshold, Estimate, SE, 
             `Lower CI`, `Upper CI`) %>%
      mutate(across(where(is.numeric), ~ signif(.x, 3))), 
    
    table_ve = res %>%
      rename(Thresholdlog10 = threshold, 
             Estimate = ve_monotone, 
             SE = ve_se, 
             `Lower CI` = ve_monotone_ci_lo, 
             `Upper CI` = ve_monotone_ci_hi) %>% 
      mutate(Threshold = 10^Thresholdlog10) %>% 
      rename(`Threshold (log10)` = Thresholdlog10) %>% 
      select(`Threshold (log10)`, Threshold, Estimate, SE, 
             `Lower CI`, `Upper CI`) %>%
      mutate(across(where(is.numeric), ~ signif(.x, 3))), 
    
    raw_table = res
  )
}
```

# Analysis notes 

- **Updated 4/23 with new weights, only included Stage 2 results, and harmonized y-axis**
- Reference timepoint is fixed at 158 days for Stage 1, 
and 124 days for Stage 2, which is the 
minimum timepoint for the latest COVID-19 endpoint across both vaccine and placebo arms. 
- Adjusted for standardized_risk_score.
- Showing estimates with pointwise confidence intervals. Both raw results and results
assuming monotonicity are shown. For the VE scaled graphs, only included graphs 
assuming monotonicity.
- CIs for risk in graphs are bounded between 0 and 1. CIs for VE in graphs are bounded
above by 1. 

```{r run_analysis, results = "asis", fig.align='center', cache = T}
for (stage in c(2)){
  
  cat(sprintf("\n\n# Stage %s \n", stage))
  
  stage_str <- sprintf("Stage%s", stage)
  
  neut_antibody_vars <- stage_dict[[stage_str]]$neut_antibody_vars
  neut_antibody_change_vars <- stage_dict[[stage_str]]$neut_antibody_change_vars
  spike_filter <- stage_dict[[stage_str]]$spike_filter
  neut_filter <- stage_dict[[stage_str]]$neut_filter
  spike_weight <- stage_dict[[stage_str]]$spike_weight
  neut_weight <- stage_dict[[stage_str]]$neut_weight
  time_var <- stage_dict[[stage_str]]$time_var
  event_var <- stage_dict[[stage_str]]$event_var
  tf <- stage_dict[[stage_str]]$tf
  marginal_filter <- stage_dict[[stage_str]]$marginal_filter

  # spike variables 
  for (marker in names(spike_marker_list)){
    
    
    placebo_max_thresh <- NULL
    vaccine_max_thresh <- NULL
    change_max_thresh <- NULL 

    if (stage == 1 & marker == "Day43bindSpike"){
      placebo_max_thresh <- 5.1 
      vaccine_max_thresh <- 5.7
    }
    else if (stage == 1 & marker == "Day43bindSpike_beta"){
      placebo_max_thresh <- 4.8 
      vaccine_max_thresh <- 5.48
    }
    else if (stage == 1 & marker == "Day43bindSpike_omicron"){
      placebo_max_thresh <- 4.3 
      vaccine_max_thresh <- 5.1
    }
    else if (stage == 1 & marker == "Day43bindSpike_mdw"){
      placebo_max_thresh <- 4.9 
      vaccine_max_thresh <- 5.5
    }
    else if (stage == 2 & marker == "Day43bindSpike_mdw"){
      change_max_thresh <- 2.06
    }
    lod_limit <- 2.4
    lod_label <- "LLOQ/2"
    
    df_temp <- df %>% filter_(spike_filter)
    df_marginal <- df %>% filter_(marginal_filter)
    
    xlabel <- sprintf("%s Threshold", spike_marker_list[[marker]]$readable)
    xlabel_change <- sprintf("Fold-rise (D43/D01) %s Threshold",
                             spike_marker_list[[marker]]$readable)
    
    df_vaccine <- df_temp %>% filter(Trt == 1)
    df_placebo <- df_temp %>% filter(Trt == 0) 

    # find placebo + vaccine incidence
    res_placebo_overall <- run_analysis_helper(df_marginal %>% filter(Trt == 0),
                                               time_var = time_var, 
                                               event_var = event_var,
                                               marker_var = "Trt", 
                                               xlabel = xlabel, 
                                               tf = tf, 
                                               exp10 = T, 
                                               overall = T)

    res_vaccine_overall <- run_analysis_helper(df_marginal %>% filter(Trt == 1),
                                               time_var = time_var, 
                                               event_var = event_var,
                                               marker_var = "Trt", 
                                               xlabel = xlabel, 
                                               tf = tf, 
                                               exp10 = T, 
                                               overall = T)
    
    incidence_placebo <- res_placebo_overall$raw_table$estimate
    se_placebo <- res_placebo_overall$raw_table$se
    incidence_vaccine <- res_vaccine_overall$raw_table$estimate
    se_vaccine <- res_vaccine_overall$raw_table$se
    
    # create marker header
    cat(sprintf("\n\n## %s {.tabset .tabset-fade} \n", spike_marker_list[[marker]]$shortname))
    
    # run vaccine analysis, output graph 
    cat("\n\n### Vaccine {.tabset .tabset-fade} \n")
    vaccine_title <- sprintf("Vaccine D43 %s", spike_marker_list[[marker]]$shortname)
    placebo_title <- sprintf("Placebo D43 %s", spike_marker_list[[marker]]$shortname)
    vaccine_change_title <- sprintf("Vaccine D43/D01 Fold-rise %s",
                                    spike_marker_list[[marker]]$shortname)
    
    res <- run_analysis_helper(df_vaccine,
                        time_var = time_var, 
                        event_var = event_var,
                        marker_var = marker, 
                        weight_var = spike_weight, 
                        xlabel = xlabel, 
                        tf = tf, 
                        exp10 = T, 
                        annotate = T, 
                        placebo_incidence = incidence_placebo, 
                        placebo_se = se_placebo, 
                        title = vaccine_title, 
                        lod_limit = lod_limit, 
                        lod_label = lod_label,
                        modify_left_point = T, 
                        left_estimate = incidence_vaccine, 
                        left_se = se_vaccine, 
                        max_thresh = vaccine_max_thresh)
    
    cat("\n\n#### Unscaled (not monotone) \n \n")

    res$graph %>% print() 
    
    res$table %>% kable() %>% print()
    
    # write.csv(res$raw_table, 
    #           file = sprintf("raw_res_only_standardized/Stage %s %s vaccine raw results.csv", stage, marker), 
    #           row.names = F)
    # 
    
    cat("\n\n#### Unscaled (monotone) \n \n")

    res$graph_monotone %>% print() 
    
    res$table_monotone %>% kable() %>% print()
    
    cat("\n\n#### VE scale (1 minus risk / placebo risk) (monotone) \n")
    
    res$graph_ve %>% print() 
    
    res$table_ve %>% kable() %>% print()

    
    # run placebo analysis, output graph 
    cat("\n\n### Placebo {.tabset .tabset-fade} \n")
    
    res <- run_analysis_helper(df_placebo,
                        time_var = time_var, 
                        event_var = event_var,
                        marker_var = marker, 
                        weight_var = spike_weight, 
                        xlabel = xlabel, 
                        tf = tf,
                        exp10 = T, 
                        title = placebo_title, 
                        lod_limit = lod_limit, 
                        lod_label = lod_label,
                        modify_left_point = T, 
                        left_estimate = incidence_placebo, 
                        left_se = se_placebo, 
                        max_thresh = placebo_max_thresh)
    
    cat("\n\n#### Not monotone \n")

    res$graph %>% print() 
    
    res$table %>% kable() %>% print()
    
    # write.csv(res$raw_table, 
    #           file = sprintf("raw_res_only_standardized/Stage %s %s placebo raw results.csv", stage, marker), 
    #           row.names = F)

    cat("\n\n#### Monotone \n")

    res$graph_monotone %>% print() 
    
    res$table_monotone %>% kable() %>% print()

    # run change analysis on vaccine only, output graph 
    cat("\n\n### Vaccine (change) {.tabset .tabset-fade}  \n")
    res <- run_analysis_helper(df_vaccine,
                        time_var = time_var, 
                        event_var = event_var,
                        marker_var = spike_marker_list[[marker]]$change_var, 
                        weight_var = spike_weight, 
                        tf = tf,
                        xlabel = xlabel_change, 
                        annotate = T, 
                        placebo_incidence = incidence_placebo, 
                        title = vaccine_change_title, 
                        left_estimate = incidence_vaccine, 
                        left_se = se_vaccine, 
                        max_thresh = change_max_thresh)
    
    cat("\n\n#### Unscaled (not monotone) \n")

    res$graph %>% print() 
    
    res$table %>% kable() %>% print()
    
    # write.csv(res$raw_table, 
    #           file = sprintf("raw_res_only_standardized/Stage %s %s vaccine change raw results.csv", stage, marker), 
    #           row.names = F)
    
    cat("\n\n#### Unscaled (monotone) \n")

    res$graph_monotone %>% print() 
    
    res$table_monotone %>% kable() %>% print()
    
    cat("\n\n#### VE scale (1 minus risk / placebo risk) (monotone) \n")
    
    res$graph_ve %>% print() 
    
    res$table_ve %>% kable() %>% print()

  }
  
  # neutralizing antibody variables
  for (marker in names(neut_marker_list)){
    lod_limit <- 1.3 
    lod_label <- "LOD/2"

    xlabel <- sprintf("%s Threshold", neut_marker_list[[marker]]$readable)
    xlabel_change <- sprintf("Fold-rise (D43/D01) %s", neut_marker_list[[marker]]$readable)

    df_temp <- df %>% filter_(neut_filter)
    df_marginal <- df %>% filter_(marginal_filter)

    df_vaccine <- df_temp %>% filter(Trt == 1)
    df_placebo <- df_temp %>% filter(Trt == 0)

    if (stage == 1){
      marker_new <- sprintf("%s_10", marker)
      marker_change <- sprintf("%s_10", neut_marker_list[[marker]]$change_var)
    }
    else{
      marker_new <- marker
      marker_change <- neut_marker_list[[marker]]$change_var
    }

    # find placebo + vaccine incidence
    res_placebo_overall <- run_analysis_helper(df_marginal %>% filter(Trt == 0),
                        time_var = time_var,
                        event_var = event_var,
                        marker_var = "Trt",
                        xlabel = xlabel,
                        tf = tf,
                        exp10 = T,
                        overall = T)

    res_vaccine_overall <- run_analysis_helper(df_marginal %>% filter(Trt == 1),
                        time_var = time_var,
                        event_var = event_var,
                        marker_var = "Trt",
                        xlabel = xlabel,
                        tf = tf,
                        exp10 = T,
                        overall = T)

    incidence_placebo <- res_placebo_overall$raw_table$estimate
    se_placebo <- res_placebo_overall$raw_table$se
    incidence_vaccine <- res_vaccine_overall$raw_table$estimate
    se_vaccine <- res_vaccine_overall$raw_table$se

    # create marker header
    cat(sprintf("\n\n## %s {.tabset .tabset-fade} \n", neut_marker_list[[marker]]$shortname))

    vaccine_title <- sprintf("Vaccine D43 %s", neut_marker_list[[marker]]$shortname)
    placebo_title <- sprintf("Placebo D43 %s", neut_marker_list[[marker]]$shortname)
    vaccine_change_title <- sprintf("Vaccine D43/D01 Fold-rise %s", neut_marker_list[[marker]]$shortname)

    # run vaccine analysis, output graph
    cat("\n\n### Vaccine {.tabset .tabset-fade} \n")

    res <- run_analysis_helper(df_vaccine,
                        time_var = time_var,
                        event_var = event_var,
                        marker_var = marker_new,
                        weight_var = neut_weight,
                        xlabel = xlabel,
                        tf = tf,
                        exp10 = T,
                        annotate = T,
                        placebo_incidence = incidence_placebo,
                        title = vaccine_title, 
                        lod_limit = lod_limit, 
                        lod_label = lod_label,
                        modify_left_point = T, 
                        left_estimate = incidence_vaccine, 
                        left_se = se_vaccine)

    cat("\n\n#### Unscaled (not monotone) \n")

    res$graph %>% print()

    res$table %>% kable() %>% print()

    write.csv(res$raw_table,
              file = sprintf("raw_res_only_standardized/Stage %s %s vaccine raw results.csv", stage, marker),
              row.names = F)

    cat("\n\n#### Unscaled (monotone) \n")

    res$graph_monotone %>% print()

    res$table_monotone %>% kable() %>% print()

    cat("\n\n#### VE scale (1 minus risk / placebo risk) (monotone) \n")

    res$graph_ve %>% print()

    res$table_ve %>% kable() %>% print()

    # run placebo analysis, output graph
    cat("\n\n### Placebo {.tabset .tabset-fade} \n")

    res <- run_analysis_helper(df_placebo,
                        time_var = time_var,
                        event_var = event_var,
                        marker_var = marker_new,
                        weight_var = neut_weight,
                        xlabel = xlabel,
                        tf = tf,
                        exp10 = T,
                        title = placebo_title, 
                        lod_limit = lod_limit, 
                        lod_label = lod_label,
                        modify_left_point = T, 
                        left_estimate = incidence_placebo, 
                        left_se = se_placebo)

    cat("\n\n#### Not monotone \n")

    res$graph %>% print()
    res$table %>% kable() %>% print()

    write.csv(res$raw_table,
              file = sprintf("raw_res_only_standardized/Stage %s %s placebo raw results.csv", stage, marker),
              row.names = F)

    cat("\n\n#### Monotone \n")

    res$graph_monotone %>% print()

    res$table_monotone %>% kable() %>% print()


    # run change analysis on vaccine only, output graph
    cat("\n\n### Vaccine (change) {.tabset .tabset-fade} \n")
    res <- run_analysis_helper(df_vaccine,
                        time_var = time_var,
                        event_var = event_var,
                        marker_var = marker_change,
                        weight_var = neut_weight,
                        tf = tf,
                        xlabel = xlabel_change,
                        annotate = T,
                        placebo_incidence = incidence_placebo,
                        title = vaccine_change_title,
                        modify_left_point = T, 
                        left_estimate = incidence_vaccine, 
                        left_se = se_vaccine)

    cat("\n\n#### Unscaled (not monotone) \n")

    res$graph %>% print()

    res$table %>% kable() %>% print()

    # write.csv(res$raw_table,
    #           file = sprintf("raw_res_only_standardized/Stage %s %s vaccine change raw results.csv", stage, marker),
    #           row.names = F)

    cat("\n\n#### Unscaled (monotone) \n")

    res$graph_monotone %>% print()

    res$table_monotone %>% kable() %>% print()

    cat("\n\n#### VE scale (1 minus risk / placebo risk) (monotone) \n")

    res$graph_ve %>% print()

    res$table_ve %>% kable() %>% print()

  }
}
```


