---
header-includes:
   - \usepackage{float}
   
# title: "COVID-19 Optimal Surrogate Analysis Report"
title: "HVTN-705 Optimal Surrogate Analysis Report"
subtitle: "`r Sys.Date()`"

output:
  pdf_document: default
  html_document: default
  citation_package: natbib   
  number_sections: true
  extra_dependencies: ["caption", "subcaption", "graphicx"]
  toc: true
---

```{r, include = FALSE}
library(here)
here::i_am("cor_surrogates/report.Rmd")
```

\tableofcontents

\clearpage
\section{Overview}

This report summarizes the results of the Month 7 multivariable marker Super Learner modeling and variable importance analysis of vaccine recipients for the HVTN-705 HIV vaccine efficacy trial. This report will be updated once the ELISpot Any Env and ADCP Mosaic markers are available.

The analysis presented in this report was performed on data from all vaccine recipients included in the case-control cohort. 

Table 1 shows the 13 learner-screen combinations fed into the Super Learner. The variable sets that were used as input feature sets in the Super Learner are shown in Table 2. The first variable set, baseline risk factors, is taken to be the same baseline factors adjusted for in the other correlates objectives of the SAP (RSA, Age, BMI and baseline risk score). For each set of Month 7 markers, both primary and exploratory markers are included. This is done given the objective of this machine learning analysis is to be maximally inclusive and unbiased, including all of the primary and exploratory Month 7 immune markers. In addition, all Month 7 individual markers that are constituents for defining one or more of the 12 markers are included; for  example the antigen-specific breadth score variables aggregate over readouts to a set of antigens. Therefore, for example, the variable set “6_M7_IgG3gp140” in Table 2 includes all individual antigen IgG3 gp140 markers as well as the IgG3 gp140 breadth score marker.

For each variable set, a point and 95% confidence interval estimate of CV-AUC from the Super Learner model fit is used to summarize classification accuracy (Table 3 and Figure 1).    

The Appendix section of the report shows the results (forest plots, ROC curves and predicted probability plots) for each of the 15 variable sets in order of their performance CV-AUC.   

The importance of variable sets is summarized by the estimated gain in population prediction potential (also referred to as the intrinsic importance) when comparing each variable set plus baseline risk factors to baseline risk factors alone. We measure prediction potential using CV-AUC. Our approach to inference on the intrinsic importance requires sample splitting; thus, we report both the estimated variable importance (Table 4 and Figure 2) and the estimated CV-AUC of each variable set when evaluated on independent data (predictiveness) from the data used to evaluate the CV-AUC of the baseline risk factors (Table 5 and Figure 3). There may be some discrepancy between the latter estimates of CV-AUC and the estimates provided in Table 3 and Figure 1; these are explained by the sample splitting, and would be expected to diminish as the sample size grows. Note that the class-balancing learners, "SL.xgboost.2.yes" and "SL.xgboost.4.yes", were dropped from the Super Learner library in the variable importance computation as the regression carried out to account for the two-phase sampling is based on a continuous outcome (so there shouldn’t be any imbalance). 


```{r, child=here("cor_surrogates", 'report_sub_HVTN705.Rmd')}
```

