---
title: "Controlled VE Curves based on Cox Models with Quantitatve Markers"
shorttitle: "Coxph CVE"
author:
header-includes:
   - \usepackage{float}
date: "`r Sys.Date()`"
output:
  bookdown::pdf_document2:
    citation_package: natbib
    number_sections: true
    extra_dependencies: ["caption", "subcaption", "graphicx"]
    toc: false
linkcolor: blue
bibliography: ref.bib
---

```{r, include=FALSE}
renv::activate(project = here::here(".."))    
```


\counterwithin{table}{section}
\counterwithin{figure}{section}

\clearpage


# COVE + ENSEMBLE + AZ
\clearpage

```{r, echo=FALSE, results='asis'}
for (a in c("pseudoneutid50","bindSpike","bindRBD")) {
  res = knitr::knit_child(c(here::here('meta_collate_sub1.Rmd')), quiet = TRUE)
  cat(res, sep = '\n')
}
```

# COVE + ENSEMBLE regions
\clearpage

```{r, echo=FALSE, results='asis'}
for (a in c("pseudoneutid50","bindSpike","bindRBD")) {
  res = knitr::knit_child(c(here::here('meta_collate_sub2.Rmd')), quiet = TRUE)
  cat(res, sep = '\n')
}
```

# ENSEMBLE regions
\clearpage

```{r, echo=FALSE, results='asis'}
for (a in c("pseudoneutid50","bindSpike","bindRBD","ADCP")) {
  res = knitr::knit_child(c(here::here('meta_collate_sub3.Rmd')), quiet = TRUE)
  cat(res, sep = '\n')
}
```

# COVE + ENSEMBLE/US + AZ
\clearpage

```{r, echo=FALSE, results='asis'}
for (a in c("pseudoneutid50","bindSpike","bindRBD")) {
  res = knitr::knit_child(c(here::here('meta_collate_sub4.Rmd')), quiet = TRUE)
  cat(res, sep = '\n')
}
```

# COVE + ENSEMBLE/US
\clearpage

```{r, echo=FALSE, results='asis'}
for (a in c("pseudoneutid50","bindSpike","bindRBD")) {
  res = knitr::knit_child(c(here::here('meta_collate_sub5.Rmd')), quiet = TRUE)
  cat(res, sep = '\n')
}
```



# Controlled VE based on Cox Models with Discretized Markers

\begin{table}[H]
\caption{Controlled VE for discretized Pseudovirus nAb ID50. COVE: starting 7 days and ending 100 days post Day 57. ENSEMBLE: starting 1 days post Day 29; pooled: ending 66 days; NA: ending 66 days; LA: ending 48 days; SA: ending 26 days.}
\begin{center}
    \input{output/meta/id50_ve.tex}\\
\end{center}
\end{table}


