<!-- ```{r, echo=FALSE} -->
<!-- here::i_am("cor_coxph/report.Rmd") -->
<!-- ``` -->



```{r, echo=FALSE, message=FALSE}
message("~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ running cor_coxph report ~~~~~~~~~~~~~~~~~~~~~~~~~")
```


`r 
tt=timepoints
do.fold.change= attr(config::get(config = Sys.getenv("TRIAL")), "config") %in% c("vat08m_nonnaive")
`

# Graphical Descriptions of Time to Event Data {#cor-graphical-time-to-event}

`r 
if (two_marker_timepoints & is_ows_trial ) { 
  paste0("
\\begin{figure}[H]
    \\centering
    \\includegraphics[width=1\\textwidth]{", paste0("cor_coxph/output/", attr(config,"config"), "/D", tt[1], "D", tt[2]), "/barplot_mixed}
    \\caption{Distribution of the number of days to COVID endpoints, vaccine arm, baseline negative.}
\\end{figure}
")} else {
  paste0("This page is empty.")
}
`


<!-- latex variables that may be used in report_sub -->
<!-- \newif\ifCOVE -->
<!-- \newif\ifENSEMBLE -->



```{r, echo=FALSE, results='asis'}

covariates_adjusted = covariates_riskscore
covariates_adjusted = sub("\\~\\.\\+","",covariates_adjusted)
covariates_adjusted = sub("_","",covariates_adjusted)

if(file.exists(here::here('cor_coxph', paste0('report_', tolower(study_name), '.Rmd')))
   & attr(config,"config")!="profiscov_lvmn" # profiscov uses special template but lvmn does not because it does not have D43start48
) {
  # trial-specific report, which also calls report_by_COR.Rmd
  
  message ("trial-specific report rmd found")
  res = knitr::knit_child(c(here::here('cor_coxph', paste0('report_', tolower(study_name), '.Rmd'))), quiet = TRUE)
  cat(res, sep = '\n')

} else {
  # generic report
  
  for (tpeak in tt) {
    COR <- paste0("D", tpeak)
    config.cor <- config::get(config = COR)
    for(opt in names(config.cor)) eval(parse(text = paste0(names(config.cor[opt])," <- config.cor[[opt]]")))
    special.note = ""
    pathCoRoutput <- paste0("cor_coxph/output/", attr(config,"config"), "/", COR)
    
    all.markers=paste0("Day", tpeak, assays)
    if (do.fold.change) all.markers=c(all.markers, paste0("Delta", tpeak, "overB", assays))
    names(all.markers)=all.markers

    res = knitr::knit_child(c(here::here('cor_coxph', 'report_by_COR.Rmd')), quiet = TRUE)
    cat(res, sep = '\n')
  }

}
```
