
\scriptsize
\input{`r paste0(pathCoRoutput, "/CoR_univariable_svycoxph_cat_pretty_", fname.suffix)`}
\normalsize
\vspace{-15pt}

<!-- $\ast$Baseline covariates adjusted for: `r covariates_adjusted`.  -->

```{r, echo=FALSE, results='asis'}
# cat("Cutpoints (on the log10 scale): ", concatList(paste0("\\input{", pathCoRoutput, "/cutpoints_", all.markers, ".txt}"), sep=","))
```
$\ast\ast$ No. at-risk/no. cases = estimated population size and case number in the group. Both are ph1 numbers.


$\ast\ast$$\ast$Generalized Wald-test p-value of the null hypothesis that the hazard rate is constant across the Lower, Middle, and Upper tertile groups.

`r if (!show.q) '<!--'`
`r tmp = paste0(sub("^[^/]+/", "", pathCoRoutput), "/pvals.perm.", fname.suffix, ".Rdata")`
$\dagger$ q-value and FWER (family-wide error rate) are computed over the set of p-values both for quantitative markers and categorical markers using the `r ifelse(file.exists(tmp), "Westfall and Young permutation", "Holm and FDR")` method`r ifelse(file.exists(tmp), " (\\protect\\input\\{" %.%tmp%.% "\\} replicates)", "")`.
`r if (!show.q)'-->'`

```{r, echo=FALSE, results='asis'}
if (show.tertile.curves) {
  cat("\\newpage")
  res = knitr::knit_child(c(here::here('.', 'report_by_COR_tertilecurves.Rmd')), quiet = TRUE)
  cat(res, sep = '\n')
}
```


