<!-- ```{r, echo=FALSE} -->
<!-- here::i_am("cor_coxph/report.Rmd") -->
<!-- ``` -->



```{r, echo=FALSE, message=FALSE}
message("~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ running cor_coxph report ~~~~~~~~~~~~~~~~~~~~~~~~~")
```


`r 
tt=timepoints
`


`r 
if (two_marker_timepoints & is_ows_trial ) { 
  paste0("# Graphical Descriptions of Time to Event Data {#cor-graphical-time-to-event}
\\begin{figure}[H]
    \\centering
    \\includegraphics[width=1\\textwidth]{", paste0("cor_coxph/output/", attr(config,"config"), "/D", tt[1], "D", tt[2]), "/barplot_mixed}
    \\caption{Distribution of the number of days to COVID endpoints, vaccine arm, baseline negative.}
\\end{figure}
")} 

`


<!-- latex variables that may be used in report_sub -->
<!-- \newif\ifCOVE -->
<!-- \newif\ifENSEMBLE -->



```{r, echo=FALSE, results='asis'}

covariates_adjusted = covariates
covariates_adjusted = sub("\\~\\.\\+","",covariates_adjusted)
covariates_adjusted = sub("_","",covariates_adjusted)


if (TRIAL=="vat08_combined") {
  
  if (Sys.getenv("stage")=="1") {
    message ("vat08_combined stage 1")
    res = knitr::knit_child(c(here::here('cor_coxph', paste0('report_vat08_combined_1.Rmd'))), quiet = TRUE)
    cat(res, sep = '\n')
  } else if (Sys.getenv("stage")=="2") {
    message ("vat08_combined stage 2")
    res = knitr::knit_child(c(here::here('cor_coxph', paste0('report_vat08_combined_2.Rmd'))), quiet = TRUE)
    cat(res, sep = '\n')
  } else {
    stop("Please export stage=1 or 2 .....................")
  }
  
  
} else if(file.exists(here::here('cor_coxph', paste0('report_', TRIAL, '.Rmd')))
   & attr(config,"config")!="profiscov_lvmn" # profiscov uses special template but lvmn does not because it does not have D43start48
) {
  
  message ("trial-specific report rmd found")
  res = knitr::knit_child(c(here::here('cor_coxph', paste0('report_', TRIAL, '.Rmd'))), quiet = TRUE)
  cat(res, sep = '\n')

} else if(file.exists(here::here('cor_coxph', paste0('report_', tolower(study_name), '.Rmd')))
   & attr(config,"config")!="profiscov_lvmn" # profiscov uses special template but lvmn does not because it does not have D43start48
) {

  message ("study name-specific report rmd found")
  res = knitr::knit_child(c(here::here('cor_coxph', paste0('report_', tolower(study_name), '.Rmd'))), quiet = TRUE)
  cat(res, sep = '\n')

} else {
  # generic report
  
  level=1; show.q=T

  for (tpeak in tt) {
    COR <- paste0("D", tpeak)
    config.cor <- config::get(config = COR)
    for(opt in names(config.cor)) eval(parse(text = paste0(names(config.cor[opt])," <- config.cor[[opt]]")))
    special.note = ""
    pathCoRoutput <- paste0("cor_coxph/output/", attr(config,"config"), "/", COR)
    
    all.markers=paste0("Day", tpeak, assays)
    if (do.fold.change.overB) all.markers=c(all.markers, paste0("Delta", tpeak, "overB", assays))
    names(all.markers)=all.markers

    res = knitr::knit_child(c(here::here('cor_coxph', 'report_by_COR.Rmd')), quiet = TRUE)
    cat(res, sep = '\n')
  }

}
```
