```{r, echo=FALSE, results='asis'}
if(is.null(fname.suffix)) fname.suffix = ''
```


## `r COR` `r fname.suffix`  Univariate CoR: Cox Models of Risk

The main regression model is the Cox proportional hazards model. Each row represents results from one model. All plots are made with Cox models fit unless specified otherwise. 

<!-- Hazard ratios -->
\setlength{\tabcolsep}{.5ex}
  \input{`r pathCoRoutput`/CoR_univariable_svycoxph_pretty_`r fname.suffix`}
$\ast$Baseline covariates adjusted for: `r covariates_adjusted`.

$\ast$`r txt.coxph.note2`

`r if (!show.q) '<!--'`
$\ast\ast\ast$q-value and FWER (family-wide error rate) are computed over the set of p-values both for quantitative markers and categorical markers `r if(TRIAL=="PREVENT19") "(not including categorical bindSpike due to there being no case in the upper tertile)"` using the Westfall and Young permutation method (\protect\input{`r pathCoRoutput`/permutation_replicates_`r fname.suffix`} replicates).
`r if (!show.q)'-->'`

`r special.note`

\vspace{10pt}

\setlength{\tabcolsep}{.5ex}
  \input{`r pathCoRoutput`/CoR_univariable_svycoxph_pretty_scaled_`r fname.suffix`}
$\ast$Baseline covariates adjusted for: `r covariates_adjusted`.

$\ast$$\ast$`r txt.coxph.note2`

`r if (!show.q) '<!--'`
$\ast$$\ast$$\ast$q-value and FWER (family-wide error rate) are computed over the set of p-values both for quantitative markers and categorical markers using the Westfall and Young permutation method (\protect\input{`r pathCoRoutput`/permutation_replicates_`r fname.suffix`} replicates).
`r if (!show.q)'-->'`

`r special.note`


\clearpage
\scriptsize
\input{`r paste0(pathCoRoutput, "/CoR_univariable_svycoxph_cat_pretty_", fname.suffix)`}
\normalsize
\vspace{-15pt}
$\ast$Baseline covariates adjusted for: `r covariates_adjusted`. Cutpoints (on the log10 scale): `r concatList(paste0("\\input{", pathCoRoutput, "/cutpoints_", all.markers, "}"), sep=",")`

$\ast\ast$`r txt.coxph.note2`

$\ast\ast$$\ast$Generalized Wald-test p-value of the null hypothesis that the hazard rate is constant across the Lower, Middle, and Upper tertile groups.

`r if (!show.q) '<!--'`
$\dagger$ q-value and FWER (family-wide error rate) are computed over the set of p-values both for quantitative markers and categorical markers using the Westfall and Young permutation method (\protect\input{`r pathCoRoutput`/permutation_replicates_`r fname.suffix`} replicates).
`r if (!show.q)'-->'`

`r special.note`

\vspace{30pt}


<!-- only for two TRIALs -->
`r if (!attr(config,"config") %in% c("moderna_real", "janssen_pooled_EUA")) '<!--'`
\begin{table}[H]
\caption{The ratio of sample sizes required to power a future trial for the column marker compared to the row marker (Follmann 2018). Confidence intervals are based on $10^3$ bootstrap replicates. }
\begin{center}
    \input{`r pathCoRoutput`/follmann2018_samplesizeratio}\\
    (lb, ub)\\
    \input{`r pathCoRoutput`/follmann2018_samplesizeratio_lbub}\\
\end{center}
`r special.note`
    %\label{tab:follmann2018_samplesizeratio}
\end{table}
\vspace{10pt}
`r if (!attr(config,"config") %in% c("moderna_real", "janssen_pooled_EUA"))'-->'`


<!-- Table 1, commented out for covail -->
`r if (attr(config,"config") %in% c("covail")) '<!--'`
\begin{table}[H]
\caption{Number of cases and non-cases in ph2 or not}
\begin{center}
  \input{`r pathCoRoutput`/tab1_`r fname.suffix`}\\
\end{center}
\end{table}
`r if (attr(config,"config") %in% c("covail"))'-->'`


<!-- additional counts tables if existed -->
`r if (!TRIAL %in% c("janssen_partA_VL")) '<!--'`

\begin{table}[H]
\caption{Number of cases and non-cases in ph2 (with ancestral Abs measured) or not. The previous table is for ph2 subjects with variants Abs measured}
\begin{center}
  \input{`r pathCoRoutput`/tab1_`r fname.suffix`_ancestral}\\
\end{center}
\end{table}


\begin{table}[H]
\caption{Number of competing cases in ph2 or not}
\begin{center}
  \input{`r pathCoRoutput`/tab1_competing_`r fname.suffix`}\\
\end{center}
\end{table}

`r if (!TRIAL %in% c("janssen_partA_VL"))'-->'`


\clearpage



<!-- Forest plots -->

```{r, echo=FALSE, results='asis'}

if (TRIAL=="janssen_partA_VL") {
  
} else if(!contain(attr(config,"config"),"senior") & file.exists(here::here('cor_coxph', paste0('forestplots_', tolower(study_name), '.Rmd')))) {
  message ("forest plots")
  res = knitr::knit_child(c(here::here('cor_coxph', paste0('forestplots_', tolower(study_name), '.Rmd'))), quiet = TRUE)
  cat(res, sep = '\n')
  cat("\\clearpage\n")
  
} else if(file.exists(paste0("../", pathCoRoutput, "/hr_forest_",fname.suffix,".pdf"))) {
  # ../ is necessary because pathCoRoutput starts at corcoxph
  cat("
\\begin{figure}
\\center
\\includegraphics[width=.8\\textwidth,keepaspectratio]{", pathCoRoutput, "/hr_forest_", fname.suffix, ".pdf}
\\caption{Forest plot.}
\\end{figure}
\\clearpage", sep="")
}
```


<!-- ## Marginalized risk and controlled vaccine efficacy plots -->

<!-- \setlength{\tabcolsep}{.5ex} -->

<!-- \begin{longtable}{lcccccc} -->
<!-- \caption{Analysis of Day `r tpeak` markers (upper vs. lower tertile) as a CoR and a controlled risk CoP.}\\ -->
<!-- \hline -->
<!--   \multicolumn{1}{c}{} & \multicolumn{2}{c}{marginalized risk} & \multicolumn{2}{c}{controlled risk}     &  \multicolumn{1}{c}{}  & \multicolumn{1}{c}{} \\ -->
<!--   \multicolumn{1}{c}{} & \multicolumn{2}{c}{ratio $RR_M(0,1)$} & \multicolumn{2}{c}{ratio $RR_C(0,1)^1$} &  \multicolumn{2}{c}{e(0,1)$^2$} \\ -->
<!--   \multicolumn{1}{c}{} & Point Est. & 95\% CI                  & Point Est. & 95\% CI                    &   Point Est.  & 95\% CI UL \\ -->
<!-- \hline -->

<!--   \input{`r pathCoRoutput`/marginalized_risks_cat_`r fname.suffix`}\\ -->
<!--   \hline -->
<!-- \end{longtable} -->


<!-- $^1$Conservative (upper bound) estimate assuming unmeasured confounding at level $RR_{UD}(0,1)=RR_{EU}(0,1) = 2$ and thus $B(0,1)=4/3$.  -->

<!-- $^2$E-values are computed for upper tertile ($s=1$) vs. lower tertile ($s=0$) biomarker subgroups after controlling for `r covariates_adjusted`; UL = upper limit. -->

<!-- `r special.note` -->



<!-- \clearpage -->


<!-- ```{r, echo=FALSE, results='asis'} -->
<!--   for (a in all.markers) { -->
<!--     assay=marker.name.to.assay(a) -->
<!--     res = knitr::knit_child(c(here::here('cor_coxph', 'risk_plots_by_assays.Rmd')), quiet = TRUE) -->
<!--     cat(res, sep = '\n') -->
<!--   } -->
<!-- ``` -->



```{r, echo=FALSE, results='asis'}

  tmp = config$multivariate_assays
  if (!is.null(multivariate_assays)) {
    tmp = multivariate_assays
  } 
  if (!is.null(tmp)) {
    cat("## Multivariate Cox Models of Risk\n\n")
    for (i in 1:length(tmp)) {
      res = knitr::knit_child(c(here::here('cor_coxph', 'multiple_regression.Rmd')), quiet = TRUE)
      cat(res, sep = '\n')
    }
  }

```



<!-- ```{r, echo=FALSE, results='asis'} -->
<!--   if (!is.null(config$additional_models)) { -->
<!--   cat("## Additional posthoc Cox Models of Risk") -->
<!--     for (i in 1:length(config$additional_models)) { -->
<!--       res = knitr::knit_child(c(here::here('cor_coxph', 'additional_model.Rmd')), quiet = TRUE) -->
<!--       cat(res, sep = '\n') -->
<!--     } -->
<!--   } -->
<!-- ``` -->


<!-- `r if (is.null(config$interaction)) '<!--'` -->
<!-- ## Interaction Cox Models of Risk -->

<!-- \begin{table}[H] -->
<!-- \centering -->
<!-- \input{`r pathCoRoutput`/CoR_itxn_multitesting} -->
<!-- \caption{ Inference for Day `r tpeak` antibody marker covariate-adjusted correlates of risk by Day \protect\input{`r pathCoRoutput`/timepoints_cum_risk_`r fname.suffix`} in the vaccine arm. Interaction P values. `r special.note`} -->
<!-- \end{table} -->

<!-- \clearpage -->
<!-- `r if (is.null(config$interaction)) '  <!--'` -->


<!-- ```{r, echo=FALSE, results='asis'} -->
<!-- if (!is.null(config$interaction)) { -->
<!--   for (ab in config$interaction) { -->
<!--       tmp=trim(strsplit(ab, " *\\* *")[[1]]) -->
<!--       a=tmp[1] -->
<!--       b=tmp[2] -->
<!--       res = knitr::knit_child(c(here::here('cor_coxph', 'itxn_by_assays.Rmd')), quiet = TRUE) -->
<!--       cat(res, sep = '\n') -->
<!--   } -->
<!-- } -->
<!-- ``` -->
