# `r COR` Univariate CoR: Cox Models of Risk {#cor-coxph-Day`r COR`}

The main regression model is the Cox proportional hazards model. All plots are made with Cox models fit unless specified otherwise.

## Hazard ratios


```{r, echo=FALSE, results='asis'}

variants=list(US=c("Ancestral.Lineage"),
              LatAme=c("Ancestral.Lineage", "Gamma", "Lambda", "Mu", "Zeta"),
              RSA=c("Beta"))

regions=c("US","LatAm","RSA")

```



```{r, echo=FALSE, results='asis'}

for (iRegion in 1:3) {
  region=regions[iRegion]
  for (variant in variants[[iRegion]]) {
    fname.suffix = paste0(region, "_", variant)
    
    cat(paste0("
\\subsection{",region,", ",variant,"}    
    
\\setlength{\\tabcolsep}{.5ex}
  \\input{", pathCoRoutput, "/CoR_univariable_svycoxph_pretty_", fname.suffix, "}
\\vspace{-20pt}
$\\ast$Baseline covariates adjusted for: ", covariates_adjusted, ".

", special.note, "

$\\dagger$ Results are based on analyses of ten imputed data sets combined through Robin's rule.

\\vspace{10pt}



\\setlength{\\tabcolsep}{.5ex}
  \\input{", pathCoRoutput, "/CoR_univariable_svycoxph_pretty_scaled_", fname.suffix, "}
\\vspace{-20pt}
$\\ast$Baseline covariates adjusted for: ", covariates_adjusted, ". 

", special.note, "

$\\dagger$ Results are based on analyses of ten imputed data sets combined through Robin's rule.

\\vspace{10pt}



\\scriptsize
\\input{", paste0(pathCoRoutput, "/CoR_univariable_svycoxph_cat_pretty_", fname.suffix), "}
\\normalsize
\\vspace{-20pt}
$\\ast$Baseline covariates adjusted for: ", covariates_adjusted, ". Cutpoints (on the log10 scale): ", concatList(paste0("\\input{", pathCoRoutput, "/cutpoints_", all.markers, "_", study_name, "}"), sep=","), "

$\\ast\\ast$$\\ast$Generalized Wald-test p-value of the null hypothesis that the hazard rate is constant across the Lower, Middle, and Upper tertile groups.

", special.note, "

$\\dagger$ Results are based on analyses of ten imputed data sets combined through Robin's rule.

\\vspace{10pt}


\\begin{table}[H]
\\caption{Number of ", variant, " cases and non-cases (latter includes other variant cases) in the ",region," in the un-imputed dataset.}
\\begin{center}
  \\input{", pathCoRoutput, "/tab1_nonimputed_",fname.suffix,"}
\\end{center}
\\end{table}


\\begin{table}[H]
\\caption{Average number of ", variant, " cases and non-cases (latter includes other variant cases) in the ",region," across ten hotdeck imputed datasets.}
\\begin{center}
  \\input{", pathCoRoutput, "/tab1_",fname.suffix,"}
\\end{center}
\\end{table}


\\begin{table}[H]
\\caption{Average number of cases non-", variant, " cases in the ",region," across ten hotdeck imputed datasets.}
\\begin{center}
  \\input{", pathCoRoutput, "/tab1_competing_",fname.suffix,"}
\\end{center}
\\end{table}


\\clearpage
"))

  }
}

```


### Forest plots

\begin{figure}[H]
    \includegraphics[width=1\textwidth]{`r pathCoRoutput`/hr_forest_bindSpike}
    \caption{Forest plots of hazard ratios per 10-fold increase. `r special.note`}
\end{figure}
\clearpage

\begin{figure}[H]
    \includegraphics[width=1\textwidth]{`r pathCoRoutput`/hr_forest_bindRBD}
    \caption{Forest plots of hazard ratios per 10-fold increase. `r special.note`}
\end{figure}
\clearpage

\begin{figure}[H]
    \includegraphics[width=1\textwidth]{`r pathCoRoutput`/hr_forest_pseudoneutid50}
    \caption{Forest plots of hazard ratios per 10-fold increase. `r special.note`}
\end{figure}
\clearpage


## Marginalized risk and controlled vaccine efficacy plots

```{r, echo=FALSE, results='asis'}
for (iRegion in 1:3) {
  region=regions[iRegion]
  for (variant in variants[[iRegion]]) {
    fname.suffix = paste0(region, "_", variant)
    
    cat(paste0("
\\subsection{",region,", ",variant,"}
"))
  
    for (a in all.markers) {
      assay=get.assay.from.name(a)
      res = knitr::knit_child(c(here::here('cor_coxph', 'risk_plots_by_assays.Rmd')), quiet = TRUE)
      cat(res, sep = '\n')
    }

  }
}


```





## Multivariate Cox Models of Risk

```{r, echo=FALSE, results='asis'}
for (iRegion in 1:3) {
  region=regions[iRegion]
  for (variant in variants[[iRegion]]) {
    fname.suffix = paste0(region, "_", variant)
    txt.endpoint = paste0(variant, " COVID, ", region)

    cat(paste0("
\\subsection{",region,", ",variant,"}
"))

  if (!is.null(config$multivariate_assays)) {
    for (i in 1:length(config$multivariate_assays)) {
      res = knitr::knit_child(c(here::here('cor_coxph', 'multiple_regression.Rmd')), quiet = TRUE)
      cat(res, sep = '\n')
    }
  }
    
    
  }
}
```

