<!-- There are two subsections, one for continuous markers, including forest plots, and one for trichotomized markers, including tertile incidence plots. -->

`r paste(concatList(rep('#',level)), fname.suffix, COR)`  Univariate


`r paste(concatList(rep('#',level+1)))`  Continuous markers

Each row represents results from one model. 

`r if (exists("COR_page_notes")) if(COR_page_notes!="") COR_page_notes`


<!-- Hazard ratios -->
\setlength{\tabcolsep}{.5ex}
  \input{`r pathCoRoutput`/CoR_univariable_svycoxph_pretty_`r fname.suffix`}
  \input{`r pathCoRoutput`/CoR_univariable_svycoxph_pretty_scaled_`r fname.suffix`}
\vspace{-15pt}

$\ast$Baseline covariates adjusted for: `r covariates_adjusted`.

$\ast$`r txt.coxph.note2` Case counting starts `r tpeaklag` days post Day `r tpeak`.

`r if (!show.q) '<!--'`
$\ast\ast\ast$q-value and FWER (family-wide error rate) are computed over the set of p-values both for quantitative markers and categorical markers `r if(TRIAL=="PREVENT19") "(not including categorical bindSpike due to there being no case in the upper tertile)"` using the Westfall and Young permutation method (\protect\input{`r pathCoRoutput`/permutation_replicates_`r fname.suffix`} replicates).
`r if (!show.q)'-->'`




<!-- Follmann sample size ratio. Only for two TRIALs -->
`r if (!attr(config,"config") %in% c("moderna_real", "janssen_pooled_EUA")) '<!--'`
\begin{table}[H]
\caption{The ratio of sample sizes required to power a future trial for the column marker compared to the row marker (Follmann 2018). Confidence intervals are based on $10^3$ bootstrap replicates. }
\begin{center}
    \input{`r pathCoRoutput`/follmann2018_samplesizeratio}\\
    (lb, ub)\\
    \input{`r pathCoRoutput`/follmann2018_samplesizeratio_lbub}\\
\end{center}
    %\label{tab:follmann2018_samplesizeratio}
\end{table}
\vspace{10pt}
`r if (!attr(config,"config") %in% c("moderna_real", "janssen_pooled_EUA"))'-->'`


<!-- Table 1, commented out for covail -->
`r if (attr(config,"config") %in% c("covail")) '<!--'`
\begin{table}[H]
\caption{Number of cases and non-cases by ph2}
\begin{center}
  \input{`r pathCoRoutput`/tab1_`r fname.suffix`}\\
\end{center}
\end{table}
`r if (attr(config,"config") %in% c("covail"))'-->'`


<!-- additional counts tables if existed -->
`r if (!TRIAL %in% c("janssen_partA_VL")) '<!--'`

\begin{table}[H]
\caption{Number of cases and non-cases by ph2 (with ancestral Abs measured). There are more non-cases in ph2 than the previous table, which is for ph2 subjects with variants Abs measured.}
\begin{center}
  \input{`r pathCoRoutput`/tab1_`r fname.suffix`_ancestral}\\
\end{center}
\end{table}


\begin{table}[H]
\caption{Number of competing cases by ph2}
\begin{center}
  \input{`r pathCoRoutput`/tab1_competing_`r fname.suffix`}\\
\end{center}
\end{table}

`r if (!TRIAL %in% c("janssen_partA_VL"))'-->'`




<!-- Forest plots -->

```{r, echo=FALSE, results='asis'}

# cat(concatList(rep('#',level+1)), " Forest plots\n\n")

if(TRIAL %in% c("azd1222")) {
  message ("forest plots")
  res = knitr::knit_child(c(here::here('cor_coxph', paste0('forestplots_', tolower(study_name), '.Rmd'))), quiet = TRUE)
  cat(res, sep = '\n')

} else if(file.exists(paste0("../", pathCoRoutput, "/hr_forest_",fname.suffix,".pdf"))) {
  # ../ is necessary because pathCoRoutput starts at corcoxph
  
  cat("
\\begin{figure}
\\center
\\includegraphics[width=.8\\textwidth,keepaspectratio]{", pathCoRoutput, "/hr_forest_", fname.suffix, ".pdf}
\\includegraphics[width=.8\\textwidth,keepaspectratio]{", pathCoRoutput, "/hr_forest_log_", fname.suffix, ".pdf}
\\caption{Forest plots depicting hazard ratios per 10-fold change in marker, presented on both an antilog scale and a log scale.}
\\end{figure}
", sep="")
  
  cat("
\\begin{figure}
\\center
\\includegraphics[width=.8\\textwidth,keepaspectratio]{", pathCoRoutput, "/hr_forest_scaled_", fname.suffix, ".pdf}
\\includegraphics[width=.8\\textwidth,keepaspectratio]{", pathCoRoutput, "/hr_forest_log_scaled_", fname.suffix, ".pdf}
\\caption{Forest plots depicting hazard ratios per SD change in marker, presented on both an antilog scale and a log scale.}
\\end{figure}
", sep="")
  
  
  # additional plots
  if (TRIAL=="vat08_combined" & fname.suffix=="D" %.% tpeak) {
    # add more forest plots: baseline and fold rise
    cat("
\\begin{figure}
\\center
\\includegraphics[width=.8\\textwidth,keepaspectratio]{", pathCoRoutput, "/hr_forest_", fname.suffix, "2.pdf}
\\includegraphics[width=.8\\textwidth,keepaspectratio]{", pathCoRoutput, "/hr_forest_log_", fname.suffix, "2.pdf}
\\caption{Forest plots depicting hazard ratios per 10-fold change in baseline marker, presented on both an antilog scale and a log scale.}
\\end{figure}
", sep="")
  
    cat("
\\begin{figure}
\\center
\\includegraphics[width=.8\\textwidth,keepaspectratio]{", pathCoRoutput, "/hr_forest_scaled_", fname.suffix, "2.pdf}
\\includegraphics[width=.8\\textwidth,keepaspectratio]{", pathCoRoutput, "/hr_forest_log_scaled_", fname.suffix, "2.pdf}
\\caption{Forest plots depicting hazard ratios per SD change in baseline marker, presented on both an antilog scale and a log scale.}
\\end{figure}
", sep="")

    cat("
\\begin{figure}
\\center
\\includegraphics[width=.8\\textwidth,keepaspectratio]{", pathCoRoutput, "/hr_forest_", fname.suffix, "3.pdf}
\\includegraphics[width=.8\\textwidth,keepaspectratio]{", pathCoRoutput, "/hr_forest_log_", fname.suffix, "3.pdf}
\\caption{Forest plots depicting hazard ratios per 10-fold change in fold increases, presented on both an antilog scale and a log scale.}
\\end{figure}
", sep="")
  
    cat("
\\begin{figure}
\\center
\\includegraphics[width=.8\\textwidth,keepaspectratio]{", pathCoRoutput, "/hr_forest_scaled_", fname.suffix, "3.pdf}
\\includegraphics[width=.8\\textwidth,keepaspectratio]{", pathCoRoutput, "/hr_forest_log_scaled_", fname.suffix, "3.pdf}
\\caption{Forest plots depicting hazard ratios per SD change in fold increases, presented on both an antilog scale and a log scale.}
\\end{figure}

\\clearpage
", sep="")    
  }

}
```


\clearpage



`r paste(concatList(rep('#',level+1)))`  Trichotomized markers


\scriptsize
\input{`r paste0(pathCoRoutput, "/CoR_univariable_svycoxph_cat_pretty_", fname.suffix)`}
\normalsize
\vspace{-15pt}
$\ast$Baseline covariates adjusted for: `r covariates_adjusted`. Cutpoints (on the log10 scale): `r concatList(paste0("\\input{", pathCoRoutput, "/cutpoints_", all.markers, ".txt}"), sep=",")`

$\ast\ast$`r txt.coxph.note2` Case counting starts `r tpeaklag` days post Day `r tpeak`.

$\ast\ast$$\ast$Generalized Wald-test p-value of the null hypothesis that the hazard rate is constant across the Lower, Middle, and Upper tertile groups.

`r if (!show.q) '<!--'`
$\dagger$ q-value and FWER (family-wide error rate) are computed over the set of p-values both for quantitative markers and categorical markers using the Westfall and Young permutation method (\protect\input{`r pathCoRoutput`/permutation_replicates_`r fname.suffix`} replicates).
`r if (!show.q)'-->'`


<!-- `r paste(concatList(rep('#',level+2)))` Tertiles cumulative incidence plots -->
\vspace{100pt}


In the following figures, the tertiled incidence curves are estimated by marginalizing over a Cox model. The comparison arm incidence curve is estimated based on a null Cox model. The comparison arm curve may not go all the way to tfinal.tpeak because the last point shown is the last event time in the comparison arm.


The data ribbon is estimated based on survfit separately within each tertile using ph2 data only, without any covariates. Thus, blanks occur when a strata is depleted after a time point.


`r if (exists("tertilecurves_page_notes")) if(tertilecurves_page_notes!="") tertilecurves_page_notes`

\clearpage

<!-- markers may be a subset of all.markers, depending on fname.suffix -->
`r 
if (TRIAL=="vat08_combined" & fname.suffix=="D" %.% tpeak) {
  all.markers.tri = all.markers[1:(length(all.markers)/3*2)]
} else if (TRIAL=="vat08_combined" & fname.suffix=="D" %.% tpeak %.% "_plac_alt2") {
  all.markers.tri = c()
} else {
  all.markers.tri = all.markers
}

res=""
for (a in all.markers.tri) {

  res = paste0(res, concatList(rep('#',level+2)), " ", a, "\n\n")

  res = paste0(res, '
\\begin{figure}
\\center
\\includegraphics[width=.75\\textwidth,keepaspectratio]{', pathCoRoutput, '/', a, '_', 'marginalized_risks_cat_',  fname.suffix, '.pdf} 
\\caption{Marginalized cumulative incidence rate curves for trichotomized Day ', tpeak, ' markers. The gray line, if present, is the overall cumulative incidence rate curve in the comparison arm. Final incidences in the tertiled groups and in the comparison arm, if present: \\protect\\input{',  pathCoRoutput, '/', a, '_tertile_incidences_',  fname.suffix, '.txt}. }
\\end{figure}
\\clearpage
')

}

res 
`




<!-- multiple_regression -->

```{r, echo=FALSE, results='asis'}

  tmp = config$multivariate_assays
  if (exists("multivariate_assays")) {
    tmp = multivariate_assays
  } 
  if (!is.null(tmp)) {
    cat("## Multivariate Cox Models of Risk\n\n")
    for (i in 1:length(tmp)) {
      res = knitr::knit_child(c(here::here('cor_coxph', 'multiple_regression.Rmd')), quiet = TRUE)
      cat(res, sep = '\n')
    }
  }

```





<!-- ## Additional content -->

<!-- \setlength{\tabcolsep}{.5ex} -->

<!-- \begin{longtable}{lcccccc} -->
<!-- \caption{Analysis of Day `r tpeak` markers (upper vs. lower tertile) as a CoR and a controlled risk CoP.}\\ -->
<!-- \hline -->
<!--   \multicolumn{1}{c}{} & \multicolumn{2}{c}{marginalized risk} & \multicolumn{2}{c}{controlled risk}     &  \multicolumn{1}{c}{}  & \multicolumn{1}{c}{} \\ -->
<!--   \multicolumn{1}{c}{} & \multicolumn{2}{c}{ratio $RR_M(0,1)$} & \multicolumn{2}{c}{ratio $RR_C(0,1)^1$} &  \multicolumn{2}{c}{e(0,1)$^2$} \\ -->
<!--   \multicolumn{1}{c}{} & Point Est. & 95\% CI                  & Point Est. & 95\% CI                    &   Point Est.  & 95\% CI UL \\ -->
<!-- \hline -->

<!--   \input{`r pathCoRoutput`/marginalized_risks_cat_`r fname.suffix`}\\ -->
<!--   \hline -->
<!-- \end{longtable} -->


<!-- $^1$Conservative (upper bound) estimate assuming unmeasured confounding at level $RR_{UD}(0,1)=RR_{EU}(0,1) = 2$ and thus $B(0,1)=4/3$.  -->

<!-- $^2$E-values are computed for upper tertile ($s=1$) vs. lower tertile ($s=0$) biomarker subgroups after controlling for `r covariates_adjusted`; UL = upper limit. -->




<!-- ```{r, echo=FALSE, results='asis'} -->
<!--   if (!is.null(config$additional_models)) { -->
<!--   cat("## Additional posthoc Cox Models of Risk") -->
<!--     for (i in 1:length(config$additional_models)) { -->
<!--       res = knitr::knit_child(c(here::here('cor_coxph', 'additional_model.Rmd')), quiet = TRUE) -->
<!--       cat(res, sep = '\n') -->
<!--     } -->
<!--   } -->
<!-- ``` -->


<!-- `r if (is.null(config$interaction)) '<!--'` -->
<!-- ## Interaction Cox Models of Risk -->

<!-- \begin{table}[H] -->
<!-- \centering -->
<!-- \input{`r pathCoRoutput`/CoR_itxn_multitesting} -->
<!-- \caption{ Inference for Day `r tpeak` antibody marker covariate-adjusted correlates of risk by Day \protect\input{`r pathCoRoutput`/timepoints_cum_risk_`r fname.suffix`} in the vaccine arm. Interaction P values. } -->
<!-- \end{table} -->

<!-- \clearpage -->
<!-- `r if (is.null(config$interaction)) '  <!--'` -->


<!-- ```{r, echo=FALSE, results='asis'} -->
<!-- if (!is.null(config$interaction)) { -->
<!--   for (ab in config$interaction) { -->
<!--       tmp=trim(strsplit(ab, " *\\* *")[[1]]) -->
<!--       a=tmp[1] -->
<!--       b=tmp[2] -->
<!--       res = knitr::knit_child(c(here::here('cor_coxph', 'itxn_by_assays.Rmd')), quiet = TRUE) -->
<!--       cat(res, sep = '\n') -->
<!--   } -->
<!-- } -->
<!-- ``` -->
