```{r, echo=FALSE, results='asis'}
if(is.null(fname.suffix)) fname.suffix = ''
```


## `r COR` `r fname.suffix`  Univariate CoR: Cox Models of Risk

The main regression model is the Cox proportional hazards model. All plots are made with Cox models fit unless specified otherwise. One model per row.

<!-- ### Hazard ratios -->

\setlength{\tabcolsep}{.5ex}
  \input{`r pathCoRoutput`/CoR_univariable_svycoxph_pretty_`r fname.suffix`}
$\ast$Baseline covariates adjusted for: `r covariates_adjusted`.

$\ast$`r txt.coxph.note2`

`r if (!show.q) '<!--'`
$\ast\ast\ast$q-value and FWER (family-wide error rate) are computed over the set of p-values both for quantitative markers and categorical markers `r if(TRIAL=="PREVENT19") "(not including categorical bindSpike due to there being no case in the upper tertile)"` using the Westfall and Young permutation method (\protect\input{`r pathCoRoutput`/permutation_replicates_`r fname.suffix`} replicates).
`r if (!show.q)'-->'`

`r special.note`

\vspace{10pt}

\setlength{\tabcolsep}{.5ex}
  \input{`r pathCoRoutput`/CoR_univariable_svycoxph_pretty_scaled_`r fname.suffix`}
$\ast$Baseline covariates adjusted for: `r covariates_adjusted`.

$\ast$$\ast$`r txt.coxph.note2`

`r if (!show.q) '<!--'`
$\ast$$\ast$$\ast$q-value and FWER (family-wide error rate) are computed over the set of p-values both for quantitative markers and categorical markers using the Westfall and Young permutation method (\protect\input{`r pathCoRoutput`/permutation_replicates_`r fname.suffix`} replicates).
`r if (!show.q)'-->'`

`r special.note`


\clearpage
\scriptsize
\input{`r paste0(pathCoRoutput, "/CoR_univariable_svycoxph_cat_pretty_", fname.suffix)`}
\normalsize
\vspace{-15pt}
$\ast$Baseline covariates adjusted for: `r covariates_adjusted`. Cutpoints (on the log10 scale): `r concatList(paste0("\\input{", pathCoRoutput, "/cutpoints_", all.markers, "}"), sep=",")`

$\ast\ast$`r txt.coxph.note2`

$\ast\ast$$\ast$Generalized Wald-test p-value of the null hypothesis that the hazard rate is constant across the Lower, Middle, and Upper tertile groups.

`r if (!show.q) '<!--'`
$\dagger$ q-value and FWER (family-wide error rate) are computed over the set of p-values both for quantitative markers and categorical markers using the Westfall and Young permutation method (\protect\input{`r pathCoRoutput`/permutation_replicates_`r fname.suffix`} replicates).
`r if (!show.q)'-->'`

`r special.note`

\vspace{30pt}


<!-- only for two TRIALs -->
`r if (!attr(config,"config") %in% c("moderna_real", "janssen_pooled_EUA")) '<!--'`
\begin{table}[H]
\caption{The ratio of sample sizes required to power a future trial for the column marker compared to the row marker (Follmann 2018). Confidence intervals are based on $10^3$ bootstrap replicates. }
\begin{center}
    \input{`r pathCoRoutput`/follmann2018_samplesizeratio}\\
    (lb, ub)\\
    \input{`r pathCoRoutput`/follmann2018_samplesizeratio_lbub}\\
\end{center}
`r special.note`
    %\label{tab:follmann2018_samplesizeratio}
\end{table}
\vspace{10pt}
`r if (!attr(config,"config") %in% c("moderna_real", "janssen_pooled_EUA"))'-->'`


<!-- comment out for covail -->
`r if (attr(config,"config") %in% c("covail")) '<!--'`
\begin{table}[H]
\caption{Number of cases and non-cases in ph2 or not}
\begin{center}
  \input{`r pathCoRoutput`/tab1}\\
\end{center}
\end{table}
`r if (attr(config,"config") %in% c("covail"))'-->'`


\clearpage



<!-- Forest plots -->

```{r, echo=FALSE, results='asis'}

if(!contain(attr(config,"config"),"senior") & file.exists(here::here('cor_coxph', paste0('forestplots_', tolower(study_name), '.Rmd')))) {
  message ("forest plots")
  res = knitr::knit_child(c(here::here('cor_coxph', paste0('forestplots_', tolower(study_name), '.Rmd'))), quiet = TRUE)
  cat(res, sep = '\n')
  cat("\\clearpage\n")
}
```


<!-- ## Marginalized risk and controlled vaccine efficacy plots -->

<!-- \setlength{\tabcolsep}{.5ex} -->

<!-- \begin{longtable}{lcccccc} -->
<!-- \caption{Analysis of Day `r tpeak` markers (upper vs. lower tertile) as a CoR and a controlled risk CoP.}\\ -->
<!-- \hline -->
<!--   \multicolumn{1}{c}{} & \multicolumn{2}{c}{marginalized risk} & \multicolumn{2}{c}{controlled risk}     &  \multicolumn{1}{c}{}  & \multicolumn{1}{c}{} \\ -->
<!--   \multicolumn{1}{c}{} & \multicolumn{2}{c}{ratio $RR_M(0,1)$} & \multicolumn{2}{c}{ratio $RR_C(0,1)^1$} &  \multicolumn{2}{c}{e(0,1)$^2$} \\ -->
<!--   \multicolumn{1}{c}{} & Point Est. & 95\% CI                  & Point Est. & 95\% CI                    &   Point Est.  & 95\% CI UL \\ -->
<!-- \hline -->

<!--   \input{`r pathCoRoutput`/marginalized_risks_cat_`r fname.suffix`}\\ -->
<!--   \hline -->
<!-- \end{longtable} -->


<!-- $^1$Conservative (upper bound) estimate assuming unmeasured confounding at level $RR_{UD}(0,1)=RR_{EU}(0,1) = 2$ and thus $B(0,1)=4/3$.  -->

<!-- $^2$E-values are computed for upper tertile ($s=1$) vs. lower tertile ($s=0$) biomarker subgroups after controlling for `r covariates_adjusted`; UL = upper limit. -->

<!-- `r special.note` -->



<!-- \clearpage -->


<!-- ```{r, echo=FALSE, results='asis'} -->
<!--   for (a in all.markers) { -->
<!--     assay=marker.name.to.assay(a) -->
<!--     res = knitr::knit_child(c(here::here('cor_coxph', 'risk_plots_by_assays.Rmd')), quiet = TRUE) -->
<!--     cat(res, sep = '\n') -->
<!--   } -->
<!-- ``` -->


<!-- ## Multivariate Cox Models of Risk -->

<!-- ```{r, echo=FALSE, results='asis'} -->
<!--   if (!is.null(config$multivariate_assays)) { -->
<!--     for (i in 1:length(config$multivariate_assays)) { -->
<!--       res = knitr::knit_child(c(here::here('cor_coxph', 'multiple_regression.Rmd')), quiet = TRUE) -->
<!--       cat(res, sep = '\n') -->
<!--     } -->
<!--   } -->
<!-- ``` -->



<!-- ```{r, echo=FALSE, results='asis'} -->
<!--   if (!is.null(config$additional_models)) { -->
<!--   cat("## Additional posthoc Cox Models of Risk") -->
<!--     for (i in 1:length(config$additional_models)) { -->
<!--       res = knitr::knit_child(c(here::here('cor_coxph', 'additional_model.Rmd')), quiet = TRUE) -->
<!--       cat(res, sep = '\n') -->
<!--     } -->
<!--   } -->
<!-- ``` -->


<!-- `r if (is.null(config$interaction)) '<!--'` -->
<!-- ## Interaction Cox Models of Risk -->

<!-- \begin{table}[H] -->
<!-- \centering -->
<!-- \input{`r pathCoRoutput`/CoR_itxn_multitesting} -->
<!-- \caption{ Inference for Day `r tpeak` antibody marker covariate-adjusted correlates of risk by Day \protect\input{`r pathCoRoutput`/timepoints_cum_risk_`r fname.suffix`} in the vaccine arm. Interaction P values. `r special.note`} -->
<!-- \end{table} -->

<!-- \clearpage -->
<!-- `r if (is.null(config$interaction)) '  <!--'` -->


<!-- ```{r, echo=FALSE, results='asis'} -->
<!-- if (!is.null(config$interaction)) { -->
<!--   for (ab in config$interaction) { -->
<!--       tmp=trim(strsplit(ab, " *\\* *")[[1]]) -->
<!--       a=tmp[1] -->
<!--       b=tmp[2] -->
<!--       res = knitr::knit_child(c(here::here('cor_coxph', 'itxn_by_assays.Rmd')), quiet = TRUE) -->
<!--       cat(res, sep = '\n') -->
<!--   } -->
<!-- } -->
<!-- ``` -->
