# Summary for mRNA vaccines

Most analyses are repeated six times for D15to181, D15to91, D92to181, D15to181BA45, D15to91BA45, and D92to181BA45. If a chapter/section title ends with BA45, cases other than BA4/BA5 are censored.

Objective 1 are main effects models, including B, D15, fold change, B + D15/B, B + D15 + D15^2, etc. Objectives 2, 3 and 4 are interaction models
 
Some analyses are repeated separately within naive and non-naive. Some analyses are repeated separately within baseline L/M/H groups.
 
When a model has more than one marker covariate, e.g. B + D15^2, both baseline and D15 markers are centered (not scaled) so that the coefficients do not explode.  

 
\vspace{0.5cm} 
**Peak Obj 1. Models without interaction terms: baseline, D15, D15/B, baseline + D15**

* D22to181

  - Both baseline and D15 markers are overall inverse correlates of risk. For example, baseline MDW HR 0.65, D15 MDW HR 0.69. 
  
  - The risks in the low and medium groups are similar but the risk in the high group is smaller.
  
  - Effect sizes are larger for both Moderna (D15 MDW HR 0.58) and Pfizer (D15 MDW HR 0.54).

  - Effect sizes are smaller for prototype (D15 MDW HR 0.78).

  - Effect sizes are larger for monovalent (D15 MDW HR 0.38).


An interesting observation is that for MDW and BA4BA5 markers, but not for Delta markers, low and medium markers have similar risks, underscoring the nonlinearity of the correlates and raising the possibility that Delta markers and Omicron markers may be complementary in prediction.


* D22to91

  - Results are similar to D22to181, with less cases and less significant P values.
  
  - Prototype vs Omicron inserts
    * Prototype D15 MDW HR 0.74 (30 cases)
    * Omicron   D15 MDW HR 0.66 (101 cases)
    * Prototype baseline MDW HR 0.58
    * Omicron   baseline MDW HR 0.63

* D92to181

  - Results are similar to D22to181, but there are some subtleties 
  
  - Effect size is larger for Pfizer, D15 MDW HR 0.33

  - Prototype vs Omicron inserts
    * Prototype D15 MDW HR 0.90 (only 13 cases)
    * Omicron   D15 MDW HR 0.57 (51 cases)
    * Prototype baseline MDW HR 1.44
    * Omicron   baseline MDW HR 0.49 

For mRNA prototype-insert vaccines and mRNA omicron-containing insert vaccines, D15 markers were inverse correlates of risk for COVID-19 occurring proximal to vaccination D22-D91. However, for COVID-19 occurring distal to vaccination D92-D181, the D15 correlate of risk result was totally flat for prototype-insert vaccines whereas the D15 inverse correlate of risk was retained for omicron-containing insert vaccines. This result suggests that immunity from ancestral strain vaccines against omicron strains is weak or absent beyond 3 months post-booster whereas the immunity of omicron-matched vaccines persists through 6 months. These results are consistent with literature on short-lived booster efficacy of ancestral-strain mRNA vaccines against omicron COVID-19.



\vspace{.5cm}
**Peak Obj 2 Naive x D15 or D15/B**

Interaction is much stronger for Early D22-D91 COVID-19 endpoints than for Late D92-D181 COVID-19 endpoints, which is evidence for the interaction being real.

* D22to181: Significant interaction between naive and D15 markers. 
    - D15 MDW HR 0.30 (0.09-0.99) among non-naive
    - D15 MDW HR 0.61 (0.42-0.90) among naive
    - Ratio of HRs 1.96 (P value 0.025)

* D22to91: Significant interaction between naive and D15 markers. 
    - D15 MDW HR 0.33 (0.19-0.56) among non-naive
    - D15 MDW HR 0.91 (0.63-1.30) among naive
    - Ratio of HRs 2.74 (P value 0.002)
  
* D92to181: Not significant interaction between naive and D15 markers.  
    - D15 MDW HR 0.83 (0.21-3.27) among non-naive
    - D15 MDW HR 0.59 (0.36-0.94) among naive
    - Ratio of HRs 0.70 (P value 0.632)


\vspace{.5cm}
**Peak Obj 3 Baseline (continuous or discrete) x D15 or D15/B**

Significant interaction between baseline (continuous) and D15 markers

* D22to181: Significant interaction between baseline and D15 markers. MDW ratio of HRs 0.44

  - Larger interaction for Pfizer (MDW ratio of HRs 0.16) than for Moderna (MDW ratio of HRs 0.52)
  
  - Similar interaction between Prototype (MDW ratio of HRs 0.35) and Omicron (MDW ratio of HRs 0.49)
  
  - Larger interaction for Monovalent (MDW ratio of HRs 0.26) than for Bivalent (MDW ratio of HRs 0.59)

* D22to91: Significant interaction between baseline and D15 markers. MDW ratio of HRs 0.44

* D92to181: Significant interaction between baseline and D15 markers. MDW ratio of HRs 0.44


\vspace{.25cm}
Non-significant interaction between baseline (continuous) and D15/Baseline fold change markers overall, but significant for D22to91 Moderna (Table 13.2)


\vspace{.25cm}
Significant interaction between baseline (trichotomized) and D15 markers

Consistent with naive x D15 interaction model results, these results show that the effect of D15 marker is more pronounced among subjects with higher baseline marker level. However, we need to keep in mind that it is harder to get the same fold rise if the baseline marker is already high. In addition, interaction is much stronger for Early D22-D91 COVID-19 endpoints than for Late D92-D181 COVID-19 endpoints, which is evidence for the interaction being real.

* D22to181: Significant interaction between baseline H/M/L and D15 markers. Generalized Wald P value 0.002

* D22to91: Significant interaction between baseline H/M/L and D15 markers. Generalized Wald P value 0.003

* D92to181: Non-significant interaction between baseline H/M/L and D15 markers. Generalized Wald P value 0.535


\vspace{.25cm}
Non-significant interaction between baseline (trichotomized) and D15/B fold change markers overall, but significant for D22to91 Moderna (Table 16.3)



\vspace{.5cm}
**Peak Obj 4 TrtA(B|C) x D15**

Not significant anywhere


\vspace{.5cm}
**Peak Obj 1 Separately within Naive and Non-Naive**

In models including for both baseline and D15/B markers, D15/B markers show no significance, baseline markers have larger effect sizes (HR 0.34 vs 0.73) and are more significant (in spite of having only 1/6 of the cases) in the non-naive subpopulation compared to the naive subpopulation.


\vspace{.5cm}
**Modeling results**

To check whether the markers behave differently for naive and non-naive, we fit an interaction model with naive * 9-category. Even though there are some two fold ratios of HRs, none are significant.

We also fit a model with interaction between naive and D15 and a model with interaction between naive and baseline. There is significant interaction between naive and baseline in the 3rd column. This analysis suggests that naive and non-naive do not differ in their relationship between D15 markers and risk, but do differ in their relationship between baseline markers and risk. Roughly speaking, a 10-fold increase in baseline marker in a non-naive is worth 100-fold increase baseline marker in a non-naive. 


# Summary of Sanofi vaccines

\vspace{.5cm}
**Peak Obj 1 Sanofi**

Focusing on MDW: D15 marker is significant (HR 0.47), baseline and fold change are not, when studied alone. When both baseline and D15 markers are included, both are significant. This is true for both D22to181 and D22to91, but no signals in D92to181.


<!-- Set up -->
```{r, echo=FALSE, results='asis'}
show.q=F
multivariate_assays=NULL
show.risk.curves=F
has.plac=F # controls whether to show placebo prevalence

special.note = paste0("$\\ddagger$ Count cases starting 7 days post Day 15.")

assays = c("pseudoneutid50_D614G", "pseudoneutid50_Delta", "pseudoneutid50_Beta", "pseudoneutid50_BA.1", "pseudoneutid50_BA.4.BA.5", "pseudoneutid50_MDW")
all.markers = c("B"%.%assays, "Day15"%.%assays, "Delta15overB"%.%assays) # use to get list of cutpoints
names(all.markers)=all.markers

config <- config::get(config = "covail")
dat_proc=read.csv(config$data_cleaned)
dat = subset(dat_proc, ph1.D15 & TrtonedosemRNA==1) 
dat.n=subset(dat, naive==1)
dat.nn=subset(dat, naive==0)

```


<!-- Objective 1, 2 and 3 -->
```{r, echo=FALSE, results='asis'}

# tables made in iObj 21 is part of the 2
for (iObj in c(1,11,12,2,3,31)) { 
  
  for (COR in c("D15to181", "D15to91", "D92to181", "D15to181BA45", "D15to91BA45", "D92to181BA45")) {
    
    pathCoRoutput <- paste0("cor_coxph/output/", TRIAL, "/", COR)
    config.cor <- config::get(config = COR)
    for(opt in names(config.cor)) eval(parse(text = paste0(names(config.cor[opt])," <- config.cor[[opt]]")))
    
    # shift by 7 days to start counting from D15
    COR = sub("D15to", "D22to", COR) 
    # COR = sub("to181", "to188", COR) 
    
    cat("# Objective Peak ", 
        switch(iObj%.%"", 
               "1"=1, 
               "2"=2, 
               "3"=3, 
               "31"="3 discrete baseline", 
               "11"="1 baseline+D15/B", 
               "12"="1 baseline+D15+D15^2"), 
        ", ", COR, sep="")
    
    for (iPop in 1:7) {
      fname.suffix = switch (iPop,
        '1' = 'mRNA_onedose',
        '2' = 'mRNA_Moderna',
        '3' = 'mRNA_Pfizer',
        '4' = 'mRNA_Prototype',
        '5' = 'mRNA_Omicron-Containing',
        '6' = 'mRNA_Bivalent',
        '7' = 'mRNA_Monovalent'
      )  
      
      if (iObj==1) {
        has.alt = F
        show.ve.curves = F
        res = knitr::knit_child(c(here::here('cor_coxph', 'report_by_COR.Rmd')), quiet = TRUE)
        
      } else if (iObj==11) {
        fname.suffix = fname.suffix %.% "_B+D15"
        has.alt = F
        res = knitr::knit_child(c(here::here('cor_coxph', 'report_by_COR_coef.Rmd')), quiet = TRUE)
        
      } else if (iObj==12) {
        fname.suffix = fname.suffix %.% "_B+D15^2"
        has.alt = F
        res = knitr::knit_child(c(here::here('cor_coxph', 'report_by_COR_coef.Rmd')), quiet = TRUE)
        
      } else if (iObj==2) {
        fname.suffix = fname.suffix %.% "_NxD15"
        has.alt = T
        res = knitr::knit_child(c(here::here('cor_coxph', 'report_by_COR_coef.Rmd')), quiet = TRUE)
        
      } else if (iObj==3) {
        fname.suffix = fname.suffix %.% "_BxD15"
        has.alt = F
        res = knitr::knit_child(c(here::here('cor_coxph', 'report_by_COR_coef.Rmd')), quiet = TRUE)
        
      } else if (iObj==31) {
        fname.suffix = fname.suffix %.% "_BxD15_cat"
        has.alt = T
        res = knitr::knit_child(c(here::here('cor_coxph', 'report_by_COR_coef.Rmd')), quiet = TRUE)
        
      }
      cat(res, sep = '\n')
      
      # select risk curves
      if (iObj==1 & COR=="D22to181BA45" & iPop==1) {
        show.ve.curves=F
        for (a in "Day15"%.%assays) {
          assay=marker.name.to.assay(a)
          res = knitr::knit_child(c(here::here('cor_coxph', 'risk_plots_by_assays.Rmd')), quiet = TRUE)
          cat(res, sep = '\n')
        }
      }

    }
    
  }
  
}
```


<!-- Objective 4 -->
```{r, echo=FALSE, results='asis'}


for (COR in c("D15to181", "D15to91", "D92to181", "D15to181BA45", "D15to91BA45", "D92to181BA45")) {
  
  pathCoRoutput <- paste0("cor_coxph/output/", TRIAL, "/", COR)
  config.cor <- config::get(config = COR)
  for(opt in names(config.cor)) eval(parse(text = paste0(names(config.cor[opt])," <- config.cor[[opt]]")))
  
  # shift by 7 days to start counting from D15
  COR = sub("D15to", "D22to", COR) 
  # COR = sub("to181", "to188", COR) 
  
  cat("# Objective Peak ", 4, ", ", sub("D15", "D22", COR), sep="")

  for (iPop in 1:3) {
    fname.suffix = switch (iPop,
      '1' = 'mRNA_Mod_Pfi',
      '2' = 'mRNA_Pro_Omi',
      '3' = 'mRNA_Bi_Mono'
    )  
    has.alt = F
    res = knitr::knit_child(c(here::here('cor_coxph', 'report_by_COR_coef.Rmd')), quiet = TRUE)
    cat(res, sep = '\n')
  }
}
```


<!-- Separate analyses within naive and non-naive -->
```{r, echo=FALSE, results='asis'}

# Obj 1 in naive and non-naive
for (iObj in c(1,11,12)) { 
  
  for (iPop in 1:2) {
    cat("# Objective Peak ", 
        switch(iPop%.%"", 
               "1"="1 naive", 
               "2"="1 nnaive"), 
        switch(iObj%.%"", 
               "1"="", 
               "11"=", baseline+D15/B", 
               "12"=", baseline+D15^2"), 
        sep="")
  
    for (COR in c("D15to181", "D15to91", "D92to181", "D15to181BA45", "D15to91BA45", "D92to181BA45")) {
      
      pathCoRoutput <- paste0("cor_coxph/output/", TRIAL, "/", COR)
      config.cor <- config::get(config = COR)
      for(opt in names(config.cor)) eval(parse(text = paste0(names(config.cor[opt])," <- config.cor[[opt]]")))
      
      # shift by 7 days to start counting from D15
      COR = sub("D15to", "D22to", COR) 
      # COR = sub("to181", "to188", COR) 
      
      fname.suffix = switch (iPop%.%"",
        '1' = 'mRNA_naive',
        '2' = 'mRNA_nnaive'
      )  
    
      if (iObj==1) {
        has.alt = F
        res = knitr::knit_child(c(here::here('cor_coxph', 'report_by_COR.Rmd')), quiet = TRUE)
        
      } else if (iObj==11) {
        fname.suffix = fname.suffix %.% "_B+D15"
        has.alt = F
        res = knitr::knit_child(c(here::here('cor_coxph', 'report_by_COR_coef.Rmd')), quiet = TRUE)
        
      } else if (iObj==12) {
        fname.suffix = fname.suffix %.% "_B+D15^2"
        has.alt = F
        res = knitr::knit_child(c(here::here('cor_coxph', 'report_by_COR_coef.Rmd')), quiet = TRUE)
      }
      cat(res, sep = '\n')
    }
  }
}
```


<!-- Separate analyses within baseline L/M/H -->
```{r, echo=FALSE, results='asis'}
cat("# Objective Peak 1, separately by baseline L/M/H\n\n")
for (COR in c("D15to181", "D15to91", "D92to181")) {
  
  pathCoRoutput <- paste0("cor_coxph/output/", TRIAL, "/", COR)
  config.cor <- config::get(config = COR)
  for(opt in names(config.cor)) eval(parse(text = paste0(names(config.cor[opt])," <- config.cor[[opt]]")))
  
  # shift by 7 days to start counting from D15
  COR = sub("D15to", "D22to", COR) 
  # COR = sub("to181", "to188", COR) 
  
  cat("## ", COR, "\n", sep="")
  
  cat("\\input{", pathCoRoutput, "/CoR_univariable_svycoxph_pretty_Bmarkercat.tex}", sep="")

}

cat("\\clearpage")

for (COR in c("D15to181BA45", "D15to91BA45", "D92to181BA45")) {
  
  pathCoRoutput <- paste0("cor_coxph/output/", TRIAL, "/", COR)
  config.cor <- config::get(config = COR)
  for(opt in names(config.cor)) eval(parse(text = paste0(names(config.cor[opt])," <- config.cor[[opt]]")))
  
  # shift by 7 days to start counting from D15
  COR = sub("D15to", "D22to", COR) 
  # COR = sub("to181", "to188", COR) 
  
  cat("## ", COR, "\n", sep="")
  
  cat("\\input{", pathCoRoutput, "/CoR_univariable_svycoxph_pretty_Bmarkercat.tex}", sep="")

}
```


<!-- Sanofi -->
```{r, echo=FALSE, results='asis'}
for (iObj in c(1,11)) { 
  
  cat("# Objective Peak ", 
      switch(iObj%.%"", 
             "1"="1 Sanofi", 
             "11"="1 Sanofi, baseline+D15/B"), 
      sep="")
  
  for (COR in c("D15to181", "D15to91", "D92to181")) {
    
    pathCoRoutput <- paste0("cor_coxph/output/", TRIAL, "/", COR)
    config.cor <- config::get(config = COR)
    for(opt in names(config.cor)) eval(parse(text = paste0(names(config.cor[opt])," <- config.cor[[opt]]")))
    
    # shift by 7 days to start counting from D15
    COR = sub("D15to", "D22to", COR) 
    # COR = sub("to181", "to188", COR) 
    
    for (iPop in 1:1) {
      fname.suffix = switch (iPop%.%"",
        '1' = 'sanofi'
      )  
      
      if (iObj==1) {
        has.alt = F
        res = knitr::knit_child(c(here::here('cor_coxph', 'report_by_COR.Rmd')), quiet = TRUE)
        
      } else if (iObj==11) {
        fname.suffix = fname.suffix %.% "_B+D15"
        has.alt = F
        res = knitr::knit_child(c(here::here('cor_coxph', 'report_by_COR_coef.Rmd')), quiet = TRUE)
      }
      cat(res, sep = '\n')
    }
  }
}
```



<!-- Modeling for all COVID -->
# Modeling for all COVID

```{r, echo=FALSE, results='asis'}
for (COR in c("D15to181", "D15to91", "D92to181")) {
  
  pathCoRoutput <- paste0("cor_coxph/output/", TRIAL, "/", COR)
  config.cor <- config::get(config = COR)
  for(opt in names(config.cor)) eval(parse(text = paste0(names(config.cor[opt])," <- config.cor[[opt]]")))
  
  # shift by 7 days to start counting from D15
  COR = sub("D15to", "D22to", COR) 
  # COR = sub("to181", "to188", COR) 
  
  cat("## ",COR,  "\n\n", sep="")
  
  cat("**Model likelihood and Cox PH test**\n\n")
  
  cat("In the following tables, each number comes from a model. Each row represents one population; N: naive, NN: non-naive. The Bcat*D15cat model is the saturated model. \n\n")
  
  cat("Log likelihood\n\n")
  cat("\\input{", pathCoRoutput, "/mdw_llik.tex}\n\n", sep="")
  
  cat("Cox.zph global P value\n\n")
  cat("\\input{", pathCoRoutput, "/mdw_zphglobal.tex}\n\n", sep="")
  
  cat("Cox.zph marker P value\n\n")
  cat("\\input{", pathCoRoutput, "/mdw_zphmarker.tex}\n\n", sep="")
  
  if (COR=="D15to181") {
    cat("B*D15 and B+D15^2 have similar log likelhoods and are the best among . There are trends in cox.zph P values.")
  }


  cat("\\clearpage\n\n")
  cat("**Model coefficients (p values)**\n\n")
  cat("In the following tables, each column represents one formula. B: baseline MDW, D15: Day 15 MDW. Markers are centered but not scaled to make the coef more interpretable because quadratic modeles are included. \n\n")
  
  cat("N+NN (dat.onedosemRNA)\n\n")
  cat("\\scriptsize \\input{", pathCoRoutput, "/mdw_models_N+NN.tex} \\normalsize \n\n", sep="")
  cat("Naive\n\n")
  cat("\\scriptsize \\input{", pathCoRoutput, "/mdw_models_N.tex} \\normalsize \n\n", sep="")
  cat("Non-naive\n\n")
  cat("\\scriptsize \\input{", pathCoRoutput, "/mdw_models_NN.tex} \\normalsize \n\n", sep="")
  
  cat("\\clearpage\n\n")
  cat("**Models with discrete baseline and Day15 markers**\n\n")
  cat("Instead of fitting the fully saturated model, which has 8 dof for the two L/M/H markers together, we choose to fit a model with 6 dof by merging L/M and L/H and merging M/L and M/H so that we don't have cells with 10 or less subjects in the 3x3 table among the naive subpopulation.\n\n")
  
  cat("N+NN (dat.onedosemRNA)\n\n")
  cat("\\input{", pathCoRoutput, "/mdw_discrete_discrete_itxn_model_N+NN.tex}\n\n", sep="")
  cat("Naive\n\n")
  cat("\\input{", pathCoRoutput, "/mdw_discrete_discrete_itxn_model_N.tex}\n\n", sep="")
  cat("Non-naive\n\n")
  cat("\\input{", pathCoRoutput, "/mdw_discrete_discrete_itxn_model_NN.tex}\n\n", sep="")
  cat("Naive * LMH\n\n")
  cat("\\input{", pathCoRoutput, "/mdw_discrete_discrete_itxn_model_N*LMH.tex}\n\n", sep="")

  cat("\\clearpage\n\n")
  cat("**Models with naive * markers interaction**\n\n")
  cat("\\input{", pathCoRoutput, "/mdw_discrete_discrete_itxn_model_N*marker.tex}\n\n", sep="")
  
  cat("\\clearpage")
}

```


## Relationship between baseline and Day 15 titers

```{r fig.width=4, fig.asp=1.5}
par(mfrow=c(2,1), mar=c(3,4,2,2))
  lim=range(c(dat$Bpseudoneutid50_MDW, dat$Day15pseudoneutid50_MDW))
  corplot(Day15pseudoneutid50_MDW~Bpseudoneutid50_MDW, dat.n, add.deming.fit = T, xlim=lim, ylim=lim, xlab="", main="Naive", method="pearson", ylab="Day 15 ID50 MDW")
  corplot(Day15pseudoneutid50_MDW~Bpseudoneutid50_MDW, dat.nn, add.deming.fit = T, xlim=lim, ylim=lim, main="Non-naive", method="pearson", ylab="Day 15 ID50 MDW")
  title(xlab="Baseline ID50 MDW", line=2)
  
```

\clearpage
**Demming regression results:**

Naive
```{r}
fit.n =  Deming(dat.n$Bpseudoneutid50_MDW,  dat.n$Day15pseudoneutid50_MDW,  boot = TRUE)
summary(fit.n)[1:2,]
```

Non-naive
```{r}
fit.nn = Deming(dat.nn$Bpseudoneutid50_MDW, dat.nn$Day15pseudoneutid50_MDW, boot = TRUE)
summary(fit.nn)[1:2,]
```

\clearpage
## Delta marker and Omicron markers

Delta and BA4BA5 markers are least closely correlated.

```{r}
mypairs(dat[,"Day15"%.%assays])
```
